### 2018-05-31 paper/paper.tex
added title page to the thesis

\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\author{ANDREI-ALIN CORODESCU}
\title{Prover pentru logica separatoare relațională în Maude}
\begin{document}
\begin{titlepage}
\begin{center}
\textbf{
UNIVERSITATEA "ALEXANDRU IOAN CUZA" DIN IAȘI
}
\\
\textbf{FACULTATEA DE INFORMATICĂ}
\end{center}
   \vspace{50mm}
\begin{center}
	\Large\textbf {TITLU PROVIZORIU}\\
	\vspace{30mm}
	\large\textit {ANDREI-ALIN CORODESCU}
	\\
	\vspace{20mm}
	\textbf{Sesiunea: }\textit{iulie, 2018}\\
	\vspace{30mm}
	\textbf{Coordonator științific}\\
	\textbf{\textit{Conf. Dr. Ciobâcă Ștefan}}
	\vspace{30mm}
\end{center}

\end{titlepage}
\end{document}

### 2018-06-02 paper/paper.tex
added first draft of the ToC to the paper

@@
 \usepackage{amssymb}
+\usepackage[romanian]{babel}
 \author{ANDREI-ALIN CORODESCU}
@@
 \end{center}
+\end{titlepage}
+\tableofcontents
 
-\end{titlepage}
+\section{Introducere}
+De ce am ales aceasta tema?
+\section{Fundamente Teoretice}
+În acest capitol voi prezenta pe scurt fundamentele teoretice ale prezentei lucrări.
+\subsection{Logica Hoare}
+\subsection{Logica Separatoare}
+\subsection{Logica Separatoare Relațională}
+\subsection{Logica Rescrierii}
+\section{Prover Logică Separatoare Relațională}
+Ordinea subsectiunilor mai poate fi schimbata ulterior. Capitolul cel mai semnificativ din lucrare, va contine toate detaliile de implementare ale solutiei curente
+\subsection{Prezentare Generală Maude}
+\subsection{Modelarea Logicilor Separatoare}
+\subsection{Interacțiunea prin LOOP-MODE}
+\subsection{Schemă Generală de funcționare}
+\subsection{Procese automatizate}
+\subsection{Interfața}
+\subsection{Viitor}
+\section{Cercetări adiționale}
+\subsection{Automatizarea demonstrațiilor}
+\subsection{Extensii pentru programe concurente}
+\subsection{Java+ITP}
+
+\section{Concluzii}
 \end{document}

### 2018-06-04 paper/paper.tex
wrote the introduction to the paper

@@
 \tableofcontents
+\pagebreak
 
 \section{Introducere}
-De ce am ales aceasta tema?
+Compararea programelor sau a fragmentelor de cod și studierea echivalenței acestora este parte din activitatea fiecărui programator atunci când testează o implementare alternativă la ceva existent, repară erori din codul sursă, lansează versiuni noi ale unui produs, etc.
+Natural, pentru orice proces realizat de oameni se încearcă să se găsească soluții care să eficientizeze, să reducă potențiale erori și, în final, să automatizeze complet procesul.
+Odată ce procesul poate fi automatizat, acesta poate fi inclus în etapele realizării unui program.
+Cel mai relevant astfel de exemplu ar fi optimizarea codului realizată de compilator: în astfel de situație, codul optimizat trebuie sa fie echivalent cu varianta originală.
+\\
+
+Prezenta lucrare descrie dezvoltarea  unui utilitar de verificare a modului cum sunt relaționate doua programe, utilizând fundamente teoretice deja bine studiate și folosite, și tehnologii ce facilitează implementarea respectivelor concepte.
+\\
+
+Utilitarul se bazează pe Logica Hoare împreună cu extensiile sale, Logica Separatoare (numită in continuare Logica Separatoare) și Logica Separatoare Relațională (numită în continuare Logica Relațională), ce ușurează procesul de argumentare asupra programelor, implementate folosind o abordare bazată pe Logica Rescrierii în limbajul Maude.
+\\
+
+Acesta reprezintă un program de tip CLI în care se pot demonstra în mod interactiv relații între programe și, consecință a dependenței logicii relaționale de cea separatoare, proprietăți ale programelor (fară a fi relaționate cu alt program).
+Dezvoltarea utilitarului s-a realizat cu ideea de a putea fi extins ulterior, principalele extensii fiind suportarea modelării programelor concurente și automatizarea demonstrațiilor.
+\\
+
+Restul lucrării este structurat după cum urmează : 
+\begin{itemize}
+	\item Capitolul 1 va descrie limbajul utilizat pentru a descrie programele, împreună cu Logicile utilizate pentru a realiza raționamente peste programele descrise de limbaj
+	\item Capitolul 2 va descrie în mod detaliat modul de construire și folosire a utilitarului, cu accent pe funcționalitățile oferite de limbajul Maude.
+	\item Capitolul 3 va prezenta câteva din cercetările conexe cu tema lucrării și cum acestea ar putea fi integrate în aceasta
+	\item Capitolul 4 va prezenta concluziile lucrării, atât pentru aspectele teoretice utilizate (Logicile prin care se realizează raționamente), cât și pentru aspectele ce țin de implementare (limbajul Maude).
+\end{itemize}
+
+\section{Contribuții}
+Contribuțiile aduse de absolvent:
+\begin{itemize}
+	\item Modelarea logicilor relaționale și separatoare prin intermediul limbajului Maude
+	\item Modelarea unui limbaj simplu de programare folosind Maude
+	\item Crearea unui utilitar interactiv de demonstrare a relațiilor dintre programe sau a proprietăților unor programe
+	\item Integrarea acestuia cu o soluție deja existentă pentru a rezolva o sub-problemă (dacă reușesc să mai fac integrarea cu Cyclist)
+\end{itemize}
 \section{Fundamente Teoretice}
 În acest capitol voi prezenta pe scurt fundamentele teoretice ale prezentei lucrări.
+\subsection{Limbaj utilizat}
+\subsubsection{Model de stocare}
+\subsubsection{Sintaxa și semantica limbajului}
 \subsection{Logica Hoare}
@@
 \subsection{Prezentare Generală Maude}
+\subsection{Semantică executabilă a limbajului folosit}
 \subsection{Modelarea Logicilor Separatoare}
@@
 \subsection{Procese automatizate}
+\subsubsection{Potrivire automată a axiomelor și a goal-urilor dovedite}
+\subsubsection{Demonstrarea automată a implicațiilor}
 \subsection{Interfața}

### 2018-06-07 paper/paper.tex
translated introduction to english

--- 2018-05-31 paper/paper.tex
@@
 \usepackage{amssymb}
+\usepackage[english]{babel}
 \author{ANDREI-ALIN CORODESCU}
-\title{Prover pentru logica separatoare relațională în Maude}
+\title{Program Equivalence : Relational Separation Logic interactive prover implemented in Maude}
 \begin{document}
@@
 \end{center}
+\end{titlepage}
+\tableofcontents
+\pagebreak
 
-\end{titlepage}
+\section{Introduction}
+Comparing programs or code fragments and studying their equivalence is part of every software engineer's activities when they are testing an alternative implementation for an existing solution, fixing bugs, launching new product versions, etc .
+Naturally, for every process completed by persons there are efforts being made in order to make it more efficient, less error-prone and, in the end, automate the process all together.
+Once such as a task is automated in software engineering, it can be included in the flow of any research or development phase.
+An example benefiting from a formal proof of program equivalence is compiler optimization, where the optimized code needs to be equivalent to the input one .
+\\
+
+The present paper describes the development of an interactive tool for arguing how to programs are related, based on studied and previously used theoretical concepts and technologies which facilitate the implementation of those concepts .
+\\
+
+The tool represents an implementation of Hoare Logic - which allows formal reasoning about a program - , along  with 2 of its extensions, namely the Separation Logic (named Separation Logic from now on) and Relational Separation Logic (named Relational Logic from now on).
+The 2 extensions simplify the Hoare Logic proofs, mainly using the "*" connector, allowing for local reasoning of effects of statements in a program .
+The tool has been implemented in Maude, a high performance logical framework with powerful metalanguage applications which facilitate the implementations of executable environments for logics.\\
+
+The tool is built as a CLI which helps argue how two programs are related using Relational Separation Logic specifications.
+As a consequence of the dependency of Relational Separation Logic on Separation Logic, proofs about single programs using the latter are also supported by the tool.
+The tool has been developed with extensibility in mind, the main desired extensions being concurrent programs support and automatic proofs.
+
+The rest of the paper is organized as follows: 
+\begin{itemize}
+	\item Section 1 will describe the language supported by the tool and a brief description of the logics utilized for reasoning .
+	\item Section 2 will describe in detail the building process of the tool and how it can be used, with an accent on the features offered by the Maude language.
+	\item Section 3 will present some of the research done on subjects related to the theme of the paper and discuss how those could be integrated into the current solution.
+	\item Section 4 will present the conclusions of the paper, regarding both the theoretical and technical aspects of the paper.
+\end{itemize}
+
+\section{Contributions}
+Personal contributions to the realization of the project : 
+\begin{itemize}
+	\item Modelled the Relational Logic and Separational Logic using Maude equational and rewriting logic specifications . 
+	\item Executable semantics of a simple programming language using Maude
+	\item Developed an interactive tool for reasoning about program behaviour using the aforementioned logics.
+	\item Automation of some tasks which makes the tool more convenient to use .
+\end{itemize}
+\section{Theoretical Foundations}
+În acest capitol voi prezenta pe scurt fundamentele teoretice ale prezentei lucrări.
+\subsection{Language}
+\subsubsection{Storage Model}
+\subsubsection{Syntax and Semantics of the language}
+\subsection{Hoare Logic}
+\subsection{Separational Logic}
+\subsection{Relational Separation Logic}
+\subsection{Rewriting Logic}
+\section{Relational Separation Logic Interactive Prover}
+Ordinea subsectiunilor mai poate fi schimbata ulterior. Capitolul cel mai semnificativ din lucrare, va contine toate detaliile de implementare ale solutiei curente
+\subsection{Maude - General Overview}
+\subsection{Executable semantics of the language}
+\subsection{Modelling the Separation Logics}
+\subsection{Interaction by Maude LOOP-MAUDE}
+\subsection{Prover execution flow}
+\subsection{Automated processes}
+\subsubsection{Automatic matching of axioms and previously proven goals}
+\subsubsection{Automatic demonstration of implications}
+\subsection{User Interface}
+\subsection{Future directions}
+\section{Additional Research}
+\subsection{Automatic prover}
+\subsection{Concurrent programs extension}
+\subsection{Java+ITP}
+
+\section{Conclusions}
 \end{document}

### 2018-06-08 paper/paper.tex
wrote the language part of the paper

@@
 \usepackage[english]{babel}
+\usepackage{array}
+\usepackage{tabularx}
 \author{ANDREI-ALIN CORODESCU}
@@
 \textbf{
-UNIVERSITATEA "ALEXANDRU IOAN CUZA" DIN IAȘI
+"ALEXANDRU IOAN CUZA" UNIVERSITY OF IAȘI
 }
 \\
-\textbf{FACULTATEA DE INFORMATICĂ}
+\textbf{FACULTY OF COMPUTER SCIENCE}
 \end{center}
-   \vspace{50mm}
+   \vspace{40mm}
 \begin{center}
-	\Large\textbf {TITLU PROVIZORIU}\\
-	\vspace{30mm}
+	\Large\textbf {Program Equivalence : Relational Separation Logic interactive prover implemented in Maude}\\
+	\vspace{40mm}
 	\large\textit {ANDREI-ALIN CORODESCU}
@@
 	\vspace{20mm}
-	\textbf{Sesiunea: }\textit{iulie, 2018}\\
+	\textbf{Session: }\textit{July, 2018}\\
 	\vspace{30mm}
-	\textbf{Coordonator științific}\\
+	\textbf{Scientific Coordinator}\\
 	\textbf{\textit{Conf. Dr. Ciobâcă Ștefan}}
@@
 
-The tool represents an implementation of Hoare Logic - which allows formal reasoning about a program - , along  with 2 of its extensions, namely the Separation Logic (named Separation Logic from now on) and Relational Separation Logic (named Relational Logic from now on).
+The tool represents an implementation of Hoare Logic - which allows formal reasoning about a program - , along  with 2 of its extensions, namely the Separation Logic (named Separation Logic from now on) and Relational Separation Logic \cite{relational} (named Relational Logic from now on).
 The 2 extensions simplify the Hoare Logic proofs, mainly using the "*" connector, allowing for local reasoning of effects of statements in a program .
@@
 
-The tool is built as a CLI which helps argue how two programs are related using Relational Separation Logic specifications.
+The tool is built as a CLI which helps \cite{primer} \cite{SeparationLogic} \cite{JAVAITP} \cite{REWRITING} \cite{maudeprimer} \cite{manual} \cite{rewrConcurrency} \cite{cyclist} argue how two programs are related using Relational Separation Logic specifications.
 As a consequence of the dependency of Relational Separation Logic on Separation Logic, proofs about single programs using the latter are also supported by the tool.
 The tool has been developed with extensibility in mind, the main desired extensions being concurrent programs support and automatic proofs.
+\\
 
@@
 \begin{itemize}
-	\item Modelled the Relational Logic and Separational Logic using Maude equational and rewriting logic specifications . 
+	\item Modelled the Relational Logic and Separation Logic using Maude equational and rewriting logic specifications . 
 	\item Executable semantics of a simple programming language using Maude
@@
 	\item Automation of some tasks which makes the tool more convenient to use .
+	\item Examples of formal proofs done using the tool
 \end{itemize}
 \section{Theoretical Foundations}
-În acest capitol voi prezenta pe scurt fundamentele teoretice ale prezentei lucrări.
+In this section we will briefly present the theoretical aspects on which the project is based. 
 \subsection{Language}
+The prover supports expressing programs in a simple, imperative language, commonly used throughout papers \cite{SeparationLogic} \cite{primer} related to the subject of program verification, including the one describing Relational Separation Logic \cite{relational}, around  which this project is based.
 \subsubsection{Storage Model}
+A state of in our storage model is defined by a pair consisting of a \(Store\) and a \(Heap\) .
+\\
+ Assuming that all the variables usable in programs from the set \(\mathtt{Vars}\) and the set of positive natural numbers is denoted by \(\mathtt{PosNats}\): \\
+
+A \(Store\) is defined as:
+\[ \mathtt{S} : \mathtt{Vars} \rightarrow \mathtt{PosNats} \]
+
+A \(Heap\) represents a mapping from the \(\mathtt{PosNats}\) to \(\mathtt{Integers}\)
+\[ \mathtt{H} : \mathtt{PosNats} \rightarrow \mathtt{Integers} \] 
+More informally, the \(Store\) holds the value of the variables while the \(Heap\) maps the active memory cells during a program execution to their contents.
 \subsubsection{Syntax and Semantics of the language}
+\begin{figure}[h]
+	\begin{tabularx}{\linewidth}{l  X}
+	Integer Expressions& \(E ::= x \mid Integer \mid E\ \mathtt{plus}\ E \mid E\ \mathtt{times}\ E \mid E\ \mathtt{minus}\ E \) \\
+	\\
+	Boolean Expressions& \(B ::= false \mid true \mid B\ \mathtt{\&\&}\ B \mid  B\ ||\ B \mid B\  \mathtt{->}\ B \mid B \mathtt{<=>} B \mid \ !
+B \mid E\ \mathtt{ge}\ E \mid E\ \mathtt{le}\ E \mid E\ \mathtt{eqs}\ E \)\\
+	\\ 	
+	Commands& \(C ::= x := alloc(E) \mid x := [E] \mid [E] := E \mid free(E) \mid x := E \mid C;C \mid if\ B\ then\ C\ else\ C \mid while\ B\ do\ C\ od \) \\
+	\end{tabularx}
+	\caption{Syntax of the language}
+	\label{fig:langSyntax}
+\end{figure}
+The syntax of the language is presented in Figure \ref{fig:langSyntax} . It represents an adapted subset of the language presented in the Relational Separation Logic paper \cite{relational} . 
+\paragraph{Semantics of the language}
+The semantics of the previously defined language are standard but a few clarifications are necessary to point out how our language constructs interact with the storage model, as well as a few differences from regular programming languages:
+\begin{itemize}
+	\item{Verbosity of operators - most operators are replaced by their literal names ( \(+\) becomes \(\mathtt{plus}\) etc.); we have opted for this approach to avoid complication when implementing the language in Maude, because most of the operators are already defined in Maude for its built-in types, and overloading them could cause conflicts since we are basing our own defined types on Maude's primitives.}
+		\subitem{\( B\ \mathtt{ge}\ B\) translates to the usual \(>=\) operator}
+		\subitem{\( B\ \mathtt{le}\ B\) translates to the usual \(<=\) operator}
+		\subitem{\( B\ \mathtt{eqs}\ B\) translates to the usual \(==\) equality comparison operator}
+		\subitem{\( B\ \mathtt{->}\ B\) denotes implication between boolean expressions}
+		\subitem{\(B\ \mathtt{<=>}\ B\) denotes equivalence between boolean expressions}
+		\subitem{The rest of the operators are mostly similar to their C++ or Java counterparts and their semantics are self explanatory}
+	\item{Memory allocation / deallocation: }
+		\subitem{\(x := alloc(E)\) allocates a new cell in the memory, initializes it with the value of \(E\) and stores its address in the variable \(x\)}
+		\subitem{\(x := free(E)\) deallocates the cell at the address equal to the value of \(E\)}
+	\item{Working with variables and memory: }
+		\subitem{\( x := [E] \) reads the contents of the memory cell at address \(E\) and stores the value in the variable \(x\)}
+		\subitem{\( [E] := E\prime \) updates the contents of the memory cell at address \(E\) with the value of the expression \(E\prime\)}
+		\subitem{\( x := E \) updates the value of the variable \(x\) with the value of the expression \(E\) - note that this command does not modify the heap in any way, as it usually happens with regular programming languages when updating the value of a variable}
+\end{itemize}
 \subsection{Hoare Logic}
@@
 \section{Conclusions}
+\pagebreak
+\bibliographystyle{unsrt}
+\bibliography{bibliography}
 \end{document}

### 2018-06-08 paper/paper.tex
added explanations for assertion languauge SL

@@
 \usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
 \usepackage{amsmath}
@@
 \subsection{Hoare Logic}
-\subsection{Separational Logic}
+Hoare Logic is a formal system which allows us to rigorously reason about the behaviour of programs.
+The main component of Hoare Logic is the Hoare Triple, defined as follows:
+\[ \{P\}\  C\  \{Q\} \]
+where \(P\) denotes the state of the program before the execution of the command \(C\) and \(Q\) denotes the state of the program after the execution of \(C\). \\
+
+The role of a Hoare triple is to capture how a command or set of commands modify the state of a program in a formal manner. \\
+
+\(P\) and \(Q\), called precondition and postcondition, respectively can be specified using an assertion language .
+Figure \ref{fig:assertionSyntax} represents the assertion language, defined in relation with the language syntax:
+\vspace{1cm}
+\begin{figure}
+	\begin{tabularx}{\linewidth}{l  X}
+		Assertions& \(P ::= B \mid P\ \Rightarrow\ P \mid P \land P \mid P \lor P \mid \neg P \mid {\exists x . P} \) \\
+	\end{tabularx}
+	\caption{Syntax of the assertion language}
+	\label{fig:assertionSyntax}
+\end{figure}
+\\
+
+At the base of proofs based on Hoare Logic are a set of axioms and proof rules which can be applied to Hoare triples. These axioms and rules will be discussed in the following section.
+\subsection{Separation Logic}
+Separation Logic is an extension of Hoare Logic which simplifies reasoning about program execution by introducing ways of localising parts of the proof : draw conclusions based on a subset of the program state, the subset chosen such that it contains only the parts relevant to the command specified by the analysed Hoare triple.
+\\
+
+The main feature of Separation Logic is the \textbf{separating conjunction} \(*\) which allows to split the assertion into parts which refer to disjoint areas of the heap.
+Through the \(*\) operator, Separation Logic enables reasoning about the effects of commands only at a local level, by splitting the assertions into a section which is relevant to the current command and "saving" the rest for subsequent commands.
+\\
+
+Separation Logic introduces new elements to the assertions language - Figure \ref{fig:SLassertionSyntax}:  \\
+
+\begin{figure}
+	\begin{tabularx}{\linewidth}{l  X}
+		Assertions& \(P ::= ... (specified\ previously) \mid E \mapsto E \mid P * P \mid emp \) \\
+	\end{tabularx}
+	\caption{Syntax of the assertion language}
+	\label{fig:SLassertionSyntax}
+\end{figure}
+
+\paragraph{Semantics of the new elements}
+\begin{itemize}
+	\item{\(E \mapsto E\prime \) means that the heap has an active cell at address \(E\), with the content \(E\prime\), and the cell is the \textbf{only} active cell in the heap}
+	\item{\(P * Q\) holds for heap \(h\) iff \(\exists h_0,h_1\) such that \(h_0 * h_1 = h\) and \(P\) holds for \(h_0\) and \(Q\) holds for \(h_1\)}
+	\item{\(emp\) denotes a heap without any active cells}
+\end{itemize}
 \subsection{Relational Separation Logic}

### 2018-06-10 paper/paper.tex
finished hoare + sep logic paper parts'

@@
 \usepackage{tabularx}
+\usepackage{ebproof}
 \author{ANDREI-ALIN CORODESCU}
@@
 \begin{figure}[h]
+	\noindent\rule{\linewidth}{0.4pt}
 	\begin{tabularx}{\linewidth}{l  X}
@@
 	\label{fig:langSyntax}
+	\noindent\rule{\linewidth}{0.4pt}
 \end{figure}
@@
 \paragraph{Semantics of the language}
+{
 The semantics of the previously defined language are standard but a few clarifications are necessary to point out how our language constructs interact with the storage model, as well as a few differences from regular programming languages:
@@
 \end{itemize}
+}
 \subsection{Hoare Logic}
@@
 \vspace{1cm}
-\begin{figure}
+\begin{figure}[h]
+	\noindent\rule{\linewidth}{0.4pt}
 	\begin{tabularx}{\linewidth}{l  X}
@@
 	\caption{Syntax of the assertion language}
+	\noindent\rule{\linewidth}{0.4pt}
 	\label{fig:assertionSyntax}
@@
 
-At the base of proofs based on Hoare Logic are a set of axioms and proof rules which can be applied to Hoare triples. These axioms and rules will be discussed in the following section.
+\begin{figure}[h!]
+	\noindent\rule{\linewidth}{0.4pt}
+	Empty Statement Axiom
+	\[
+	\begin{prooftree}
+	\Hypo{}
+	\Infer 1 {\{P\}\  \mathtt{skip}\  \{P\}}
+	\end{prooftree}	
+	\]
+	Assignment Axiom 
+	\medskip
+	\[
+	\begin{prooftree}
+	\Hypo{}
+	\Infer 1 {\{P[E/x]\}\  \mathtt{x := E}\  \{P\}}
+	\end{prooftree}	
+	\]
+	Composition Rule
+	\medskip
+	\[
+	\begin{prooftree}
+	\Hypo{ \{P\} S \{Q\}}
+	\Hypo{ \{Q\} T \{R\}}
+	\Infer 2 {\{P\}\  \mathtt{S ; T}\  \{Q\}}
+	\end{prooftree}	
+	\]
+	Consequence Rule
+	\medskip
+	\[
+	\begin{prooftree}
+	\Hypo{P \Rightarrow P\prime}
+	\Hypo{\{P\prime\} C \{Q\prime\}}
+	\Hypo{Q \Rightarrow Q\prime}
+	\Infer 3 {\{P\}\  C  \{Q\}}
+	\end{prooftree}	
+	\]
+	Auxiliary Variable Elimination Rule
+	\medskip
+	\[
+	\begin{prooftree}
+	\Hypo{\{P\} C \{Q\}}
+	\Infer 1 [\(x \notin Free(C)\)]{\{\exists x.P\}\ C\ \{\exists x. Q\}}
+	\end{prooftree}	
+	\]
+	Conditional Rule
+	\medskip
+	\[
+	\begin{prooftree}
+	\Hypo{\{B \land P\} S \{Q\}}
+	\Hypo{\{\neg B \land P\} T \{Q\}}
+	\Infer 2 {\{P\} \mathtt{if\ B\ then\ S\ else\ T\ fi} \{Q\}}
+	\end{prooftree}	
+	\]
+	While Rule
+	\medskip
+	\[
+	\begin{prooftree}
+	\Hypo{\{P \land B\} S\{P\}}
+	\Infer 1 {\{P\}\  \mathtt{while\ B\ do\ S\ od}\  \{\neg B \land P\}}
+	\end{prooftree}	
+	\]
+	\caption{Hoare Logic Rules}
+	\label{fig:HLRules}
+	\noindent\rule{\linewidth}{0.4pt}
+\end{figure}
+
+At the base of proofs based on Hoare Logic are a set of axioms and proof rules which can be applied to Hoare triples, presented in Figure \ref{fig:HLRules}
+
 \subsection{Separation Logic}
-Separation Logic is an extension of Hoare Logic which simplifies reasoning about program execution by introducing ways of localising parts of the proof : draw conclusions based on a subset of the program state, the subset chosen such that it contains only the parts relevant to the command specified by the analysed Hoare triple.
+Separation Logic is an extension of Hoare Logic which simplifies reasoning about program execution by introducing ways of localising parts of the proof : draw conclusions based on a subset of the program state, the subset chosen such that it contains only the parts relevant to the command specified in the analysed Hoare triple.
 \\
@@
 \begin{figure}
+	\noindent\rule{\linewidth}{0.4pt}
 	\begin{tabularx}{\linewidth}{l  X}
@@
 	\label{fig:SLassertionSyntax}
+	\noindent\rule{\linewidth}{0.4pt}
 \end{figure}
@@
 \end{itemize}
+\paragraph{Inference Rules for Separation Logic} 
+Separation Logic introduces a new rule, called Frame Rule, which makes use of the \(*\) operator to allow local reasoning :
+\\
+\noindent\rule{\linewidth}{0.4pt}
+Frame Rule
+\medskip
+\[
+\begin{prooftree}
+\Hypo{\{P\}\ C\ \{Q\}}
+\Infer 1 [\(Modifies(C) \cup Free(R) = \emptyset \)]{\{P * R \}\ C\ \{Q * R\}}
+\end{prooftree}		
+\]
+\noindent\rule{\linewidth}{0.4pt}
 \subsection{Relational Separation Logic}
+Relational Separation Logic builds upon the foundations layed by the Separation Logic by extending it to facilitate analysing how two programs are related. 
+\paragraph{Hoare Quadruple}
+The main abstraction introduced by the Relational Separation Logic is the Hoare Quadruple, which express the effects of commands on the states of the two programs. 
+\[\{R\}\ {C_1 \atop C_2}\   \{T\}\]
+
+\(R\) represents a \textbf{relation} between the two program states holding before the execution of \(C_1\) and \(C_2\) respectively while \(T\) represents a \textbf{relation} which holds after the execution of the two commands.
 \subsection{Rewriting Logic}

### 2018-06-10 paper/paper.tex
finished Relational Separation Logic paper part

@@
 \title{Program Equivalence : Relational Separation Logic interactive prover implemented in Maude}
+\newcommand{\hq}[4]{
+	\left\{{#1}\right\}
+	\let\scriptstyle\textstyle 
+	\substack{{#2} \\ 	\let\scriptstyle\textstyle {#3}} 
+	\left\{{#4}\right\}
+}
+
 \begin{document}
@@
 \(R\) represents a \textbf{relation} between the two program states holding before the execution of \(C_1\) and \(C_2\) respectively while \(T\) represents a \textbf{relation} which holds after the execution of the two commands.
+\\
+
+Since relational separation language reasons about two programs simultaneously, it employs a storage model in which both programs share a single \(Store\) but have independent \(Heaps\).
+This implies that the programs need to use \textbf{disjoint} parts of the same \(Store\).
+The benefit of such a model is that we can use variables in Relations which aren't used by the two programs directly to relate them.
+\begin{figure}[h]
+	\noindent\rule{\linewidth}{0.4pt}
+	\medskip
+	\begin{tabularx}{\linewidth}{l  X}
+		Relation& \(R ::= Same \mid Emp \mid \left( P_1 \atop P_2 \right) \mid R_1 * R_2 \mid B \mid R_1 \Rightarrow R_2 \mid R_1 \land R_2 \mid R_1 \lor R_2 \mid \neg R \mid \exists x.
+R \mid \forall x.
+R \) \\
+	\end{tabularx}
+	\caption{Syntax of the relation language}
+	\label{fig:RelationSyntax}
+	\noindent\rule{\linewidth}{0.4pt}
+\end{figure}
+\paragraph{Semantics of the Relation Language}
+The semantics of the Relation Language are derived from the semantics of the Assertion Language, and in the following section I will present the newly introduced elements. 
+\begin{itemize}
+	\item{ \(Same\) denotes that the heaps associated with the 2 programs are identical}
+	\item{ \(Emp\) is the Relational equivalent of the \(emp\) assertion; specifies two empty heaps}
+	\item{ \(\left(P_1 \atop P_2\right)\) is the building block of the Relational separation logic: it allows to construct a relation between programs by putting together 2 assertions, \(P_1\) holding for the first program and \(P_2\) holding for the second program}
+	\item{ \(R_1 * R_2\) represents the relational separating conjunction and it keeps a similar meaning to the Separation Logic one ; it separates two relations referring to \textbf{disjoint} parts of the heaps of the two programs.}
+\end{itemize}
+\begin{figure}
+		\noindent\rule{\linewidth}{0.4pt}
+	Loop:
+	\[
+	\begin{prooftree}
+	\Hypo{R \Rightarrow (B \Leftrightarrow B\prime)}
+	\Hypo{\{R \land B \} {C \atop C\prime} {R}}
+	\Infer 2 {\{R\}
+		\let\scriptstyle\textstyle 
+		\substack{\mathtt{while\ B\ do\ C\ od} \\ \mathtt{while\ B\prime\ do\ C\prime\ od}} \{R \land \neg B\}}
+	\end{prooftree}	
+	\]
+	Conditional Statement
+	\[
+	\begin{prooftree}
+	\Hypo{R \Rightarrow (B \Leftrightarrow B\prime)}
+	\Hypo{ \{R \land B\} 		
+		\let\scriptstyle\textstyle 
+		\substack{C_1 \\ C_1\prime} \{S\}
+		}
+	\Hypo{
+		\{R \land \neg B\}
+		\let\scriptstyle\textstyle 
+		\substack{C_2 \\ C_2\prime}
+		\{S\}
+	}
+	\Infer 3 {\{R\}\  	
+				\let\scriptstyle\textstyle 
+				\substack{\mathtt{if\ B\ then\ C_1\ else\ C_2\ fi} \\ \mathtt{if\ B\prime\ then\ C_1\prime\ else\ C_2\prime fi}} \{S\}}
+	\end{prooftree}	
+	\]
+	Sequencing Rule
+	\[
+	\begin{prooftree}
+	\Hypo{ \hq{R}{C_1}{C_1\prime}{S}}
+	\Hypo{ \hq{S}{C_2}{C_2\prime}{T}}
+	\Infer 2 {\hq{R}{C_1 ; C_2}{C_1\prime ; C_2\prime}{T}}
+	\end{prooftree}	
+	\]
+	Frame Rule
+	\[
+	\begin{prooftree}
+	\Hypo { \hq{R}{C}{C\prime}{S}}
+	\Infer 1 {\hq{R * T} {C}{C\prime}{S * T}}
+	\end{prooftree}	
+	\]
+	Embedding rule
+	\[
+	\begin{prooftree}
+	\Hypo{\{P\} C \{Q\}}
+	\Hypo{\{P\prime\} C\prime \{Q\prime\}}
+	\Infer 2 {\hq{\left( \substack{P \\ P\prime}\right)}{C}{C\prime}{\left( \substack{Q \\ Q\prime}\right)}}
+	\end{prooftree}	
+	\]
+	Consequence Rule
+	\[
+	\begin{prooftree}
+	\Hypo{R \Rightarrow R_1}
+	\Hypo{\hq{R_1}{C}{C\prime}{S_1}}
+	\Hypo{S \Rightarrow S_1}
+	\Infer 3 {\hq{R}{C}{C\prime}{S}}
+	\end{prooftree}	
+	\]
+	Conjunction Rule
+	\[
+	\begin{prooftree}
+	\Hypo{\hq{R_1}{C}{C\prime}{S_1}}
+		\Hypo{\hq{R_2}{C}{C\prime}{S_2}}
+	\Infer 2 {\hq{R_1 \land R_2}{C}{C\prime}{S_1 \land S_2}}
+	\end{prooftree}	
+	\]
+	Auxiliary Variable Elimination
+	\[
+	\begin{prooftree}
+	\Hypo{\hq{R}{C}{C\prime}{S}}
+	\Infer 1 {\hq{\exists x.R}{C}{C\prime}{\exists x.S}}
+	\end{prooftree}	
+	\]
+	\caption{Relational Separation Logic Proof Rules}
+	\label{fig:ProofRue}
+	\noindent\rule{\linewidth}{0.4pt}
+\end{figure}
+
+Most of the rules are adapted from the Separation Logic ones, and the link between the two logics is given by the \textbf{Embedding Rule}, which allows to transform a Relational Separation Logic Hoare Quadruple into two Separation Logic Hoare Triples.
+The rules are presented in Figure \ref{fig:ProofRue}.
+\clearpage
 \subsection{Rewriting Logic}
+
 \section{Relational Separation Logic Interactive Prover}

### 2018-06-10 paper/paper.tex
finished draft version of the Theoretical foundations part of the paper

@@
 \subsection{Rewriting Logic}
+Rewriting logic is both a semantic and logical framework \cite{rewritingLogic} in which, via \textbf{term rewriting}, changes within systems (concurrent or not) and other logics can be expressed naturally.
+The latter represents the motivation for choosing rewriting logic for our project, as well as extensibility in the future, in terms of concurrent program analysis.
+\\
 
+One of the strong points of rewriting logic is that it reduces the \textbf{representational distance}, as it was named in \cite{rewritingLogic}, of the systems modelled using it.
+Representational distance is how much detail is lost in the translation process between semantic representation and implementation.
+This feature will be highlighted in the following sections, describing the Maude representation of the Relational Separation Logic and an executable semantic specification of the language supported by the prover.
+As we can see, the Relational Separation Logic has been represented naturally using rewrite rules and the translation process between representation and implementation usually involves just syntactic differences.\\
+
+A rewrite theory is a triplet : \[\mathcal{R} = (\Sigma, E, R)\]
+where \(\Sigma\) represent the "environment" - in our case, \(\Sigma\) represents all the symbols which can appear when representing a Hoare Quadruple and their corresponding operators , \(E\) represents a set of equations denoting algebraic identities for \(\Sigma\) and \(R\) represents a set of rewrite rules, possibly conditional which take the form of \(t \leftarrow t\prime\ [condition]\), where \(t\) and \(t\prime\) are terms.
 \section{Relational Separation Logic Interactive Prover} 

### 2018-06-12 paper/paper.tex
wrote the Maude introduction part of the paper

@@
 \section{Relational Separation Logic Interactive Prover} 
-Ordinea subsectiunilor mai poate fi schimbata ulterior. Capitolul cel mai semnificativ din lucrare, va contine toate detaliile de implementare ale solutiei curente
+This chapter will include details related to the implementation and usage of the Relational Separation Logic prover and highlight a few of Maude's features which made it the a language fit for the purpose of this project.
 \subsection{Maude - General Overview}
+Maude is a programming language which is based on Rewriting Logic, discussed in the previous section. 
+The main features used for this project which set Maude apart are :
+\begin{itemize}
+	\item \textbf{Expressiveness}
+	\subitem Maude allows the user to model a wide range of applications through user-defined data types and operators
+	\subitem The principles upon which Maude was built make the implementations be close to the problem they are trying to solve.
+This forces programmers to come up with clever, often simple and self-explanatory solutions.
+	\item \textbf{Simplicity}
+	\subitem
+	The previously mentioned expressiveness is augmented by the simplicity of the Maude language, which incorporates just a few keywords and commands,and the user is then tasked with building solutions using the underlying system (and, if desired, using pre-defined modules).
+	\item \textbf{Metalanguage applications}
+	\subitem
+	Maude has a powerful, built-in way of analysing and controlling Maude's execution environment at runtime via the META-LEVEL module.
+Throughout this project we make heavy use of the meta language capabilities of Maude to control the flow of the prover execution.
+This approach also has the benefit of adding extensibility to it.
+\end{itemize} 
+Good references for Maude language include:
+\begin{itemize}
+	\item Maude Primer \cite{primer} which was written for Maude 2.0.1 but still applies to the latest versions of Maude is a good starting point for learning Maude, as it introduces the language in a more informal, friendlier way
+	\item Maude Manual \cite{manual} which presents the whole Maude system in depth, along with the mathematical foundations
+	\item All about Maude book \cite{allAboutMaude} which includes everything contained in the manual and presents some of the more relevant tools implemented in Maude .
+\end{itemize}
 \subsection{Executable semantics of the language}

### 2018-06-15 paper/paper.tex
intermediary commit

@@
 \subsection{Executable semantics of the language}
+Using Maude we were able to model an executable semantics of the language accepted by the prover, which further underlines the capability of Maude to model a wide range of applications.
+The main ideas used in the implementations are presented in \cite{REWRITING}, which presents a number of different approaches of modelling language semantics using rewriting logic, together with their advantages and disadvantages.
+Using Maude's rewrite engine we were able to create an executable semantic specification of our language.
+\\
+
+Making the semantics of the language executable assures us further that they are correct and the specifications define correctly the intended behaviour of language constructs.
 \subsection{Modelling the Separation Logics}

### 2018-06-17 paper/paper_after_guide.tex
started writing the paper after the guide release

--- 2018-06-10 paper/paper.tex
@@
 \section{Introduction}
-Comparing programs or code fragments and studying their equivalence is part of every software engineer's activities when they are testing an alternative implementation for an existing solution, fixing bugs, launching new product versions, etc .
-Naturally, for every process completed by persons there are efforts being made in order to make it more efficient, less error-prone and, in the end, automate the process all together.
-Once such as a task is automated in software engineering, it can be included in the flow of any research or development phase.
-An example benefiting from a formal proof of program equivalence is compiler optimization, where the optimized code needs to be equivalent to the input one .
-\\
-
-The present paper describes the development of an interactive tool for arguing how to programs are related, based on studied and previously used theoretical concepts and technologies which facilitate the implementation of those concepts .
+The present paper describes the development of an interactive tool for reasoning how to programs are related, based on studied and previously used theoretical concepts and technologies which facilitate the implementation.
 \\
@@
 
-The tool is built as a CLI which helps \cite{primer} \cite{SeparationLogic} \cite{JAVAITP} \cite{REWRITING} \cite{maudeprimer} \cite{manual} \cite{rewrConcurrency} \cite{cyclist} argue how two programs are related using Relational Separation Logic specifications.
+The tool is built as a CLI which helps \cite{primer} \cite{SeparationLogic} \cite{JAVAITP} \cite{REWRITING} \cite{maudeprimer} \cite{manual} \cite{rewrConcurrency} \cite{cyclist} with reasoning how two programs are related using Relational Separation Logic specifications.
 As a consequence of the dependency of Relational Separation Logic on Separation Logic, proofs about single programs using the latter are also supported by the tool.
@@
 The rest of the paper is organized as follows:
-\begin{itemize}
-	\item Section 1 will describe the language supported by the tool and a brief description of the logics utilized for reasoning .
-	\item Section 2 will describe in detail the building process of the tool and how it can be used, with an accent on the features offered by the Maude language.
-	\item Section 3 will present some of the research done on subjects related to the theme of the paper and discuss how those could be integrated into the current solution.
-	\item Section 4 will present the conclusions of the paper, regarding both the theoretical and technical aspects of the paper.
-\end{itemize}
 
@@
 	\item Modelled the Relational Logic and Separation Logic using Maude equational and rewriting logic specifications . 
-	\item Executable semantics of a simple programming language using Maude
 	\item Developed an interactive tool for reasoning about program behaviour using the aforementioned logics.
@@
 \end{itemize}
-\section{Theoretical Foundations}
-In this section we will briefly present the theoretical aspects on which the project is based. 
-\subsection{Language}
-The prover supports expressing programs in a simple, imperative language, commonly used throughout papers \cite{SeparationLogic} \cite{primer} related to the subject of program verification, including the one describing Relational Separation Logic \cite{relational}, around  which this project is based.
-\subsubsection{Storage Model}
-A state of in our storage model is defined by a pair consisting of a \(Store\) and a \(Heap\) .
-\\
- Assuming that all the variables usable in programs from the set \(\mathtt{Vars}\) and the set of positive natural numbers is denoted by \(\mathtt{PosNats}\): \\
+\section{Description of the problem}
+The problem this project is aiming to solve is related to formal reasoning about the execution of code, mainly focusing on how two programs are related to each other (most often the relation to be proven is equivalence)\\
 
-A \(Store\) is defined as:
-\[ \mathtt{S} : \mathtt{Vars} \rightarrow \mathtt{PosNats} \]
-
-A \(Heap\) represents a mapping from the \(\mathtt{PosNats}\) to \(\mathtt{Integers}\)
-\[ \mathtt{H} : \mathtt{PosNats} \rightarrow \mathtt{Integers} \] 
-More informally, the \(Store\) holds the value of the variables while the \(Heap\) maps the active memory cells during a program execution to their contents.
-\subsubsection{Syntax and Semantics of the language}
-\begin{figure}[h]
-	\noindent\rule{\linewidth}{0.4pt}
-	\begin{tabularx}{\linewidth}{l  X}
-	Integer Expressions& \(E ::= x \mid Integer \mid E\ \mathtt{plus}\ E \mid E\ \mathtt{times}\ E \mid E\ \mathtt{minus}\ E \) \\
-	\\
-	Boolean Expressions& \(B ::= false \mid true \mid B\ \mathtt{\&\&}\ B \mid  B\ ||\ B \mid B\  \mathtt{->}\ B \mid B \mathtt{<=>} B \mid \ !
-B \mid E\ \mathtt{ge}\ E \mid E\ \mathtt{le}\ E \mid E\ \mathtt{eqs}\ E \)\\
-	\\ 	
-	Commands& \(C ::= x := alloc(E) \mid x := [E] \mid [E] := E \mid free(E) \mid x := E \mid C;C \mid if\ B\ then\ C\ else\ C \mid while\ B\ do\ C\ od \) \\
-	\end{tabularx}
-	\caption{Syntax of the language}
-	\label{fig:langSyntax}
-	\noindent\rule{\linewidth}{0.4pt}
-\end{figure}
-The syntax of the language is presented in Figure \ref{fig:langSyntax} . It represents an adapted subset of the language presented in the Relational Separation Logic paper \cite{relational} . 
-\paragraph{Semantics of the language}
-{
-The semantics of the previously defined language are standard but a few clarifications are necessary to point out how our language constructs interact with the storage model, as well as a few differences from regular programming languages:
-\begin{itemize}
-	\item{Verbosity of operators - most operators are replaced by their literal names ( \(+\) becomes \(\mathtt{plus}\) etc.); we have opted for this approach to avoid complication when implementing the language in Maude, because most of the operators are already defined in Maude for its built-in types, and overloading them could cause conflicts since we are basing our own defined types on Maude's primitives.}
-		\subitem{\( B\ \mathtt{ge}\ B\) translates to the usual \(>=\) operator}
-		\subitem{\( B\ \mathtt{le}\ B\) translates to the usual \(<=\) operator}
-		\subitem{\( B\ \mathtt{eqs}\ B\) translates to the usual \(==\) equality comparison operator}
-		\subitem{\( B\ \mathtt{->}\ B\) denotes implication between boolean expressions}
-		\subitem{\(B\ \mathtt{<=>}\ B\) denotes equivalence between boolean expressions}
-		\subitem{The rest of the operators are mostly similar to their C++ or Java counterparts and their semantics are self explanatory}
-	\item{Memory allocation / deallocation: }
-		\subitem{\(x := alloc(E)\) allocates a new cell in the memory, initializes it with the value of \(E\) and stores its address in the variable \(x\)}
-		\subitem{\(x := free(E)\) deallocates the cell at the address equal to the value of \(E\)}
-	\item{Working with variables and memory: }
-		\subitem{\( x := [E] \) reads the contents of the memory cell at address \(E\) and stores the value in the variable \(x\)}
-		\subitem{\( [E] := E\prime \) updates the contents of the memory cell at address \(E\) with the value of the expression \(E\prime\)}
-		\subitem{\( x := E \) updates the value of the variable \(x\) with the value of the expression \(E\) - note that this command does not modify the heap in any way, as it usually happens with regular programming languages when updating the value of a variable}
-\end{itemize}
-}
-\subsection{Hoare Logic}
-Hoare Logic is a formal system which allows us to rigorously reason about the behaviour of programs.
-The main component of Hoare Logic is the Hoare Triple, defined as follows:
-\[ \{P\}\  C\  \{Q\} \]
-where \(P\) denotes the state of the program before the execution of the command \(C\) and \(Q\) denotes the state of the program after the execution of \(C\). \\
-
-The role of a Hoare triple is to capture how a command or set of commands modify the state of a program in a formal manner. \\
-
-\(P\) and \(Q\), called precondition and postcondition, respectively can be specified using an assertion language .
-Figure \ref{fig:assertionSyntax} represents the assertion language, defined in relation with the language syntax:
-\vspace{1cm}
-\begin{figure}[h]
-	\noindent\rule{\linewidth}{0.4pt}
-	\begin{tabularx}{\linewidth}{l  X}
-		Assertions& \(P ::= B \mid P\ \Rightarrow\ P \mid P \land P \mid P \lor P \mid \neg P \mid {\exists x . P} \) \\
-	\end{tabularx}
-	\caption{Syntax of the assertion language}
-	\noindent\rule{\linewidth}{0.4pt}
-	\label{fig:assertionSyntax}
-\end{figure}
+Comparing programs or code fragments and studying their equivalence is part of every software engineer's activities when they are testing an alternative implementation for an existing solution, fixing bugs, launching new product versions, etc .
+Naturally, for every process completed manually there are efforts being made in order to make it more efficient, less error-prone and, in the end, automate the process all together.
+Once such a task is automated in software engineering, it can be included in the flow of any research or development phase of a product.
+An example benefiting from a formal proof of program equivalence is compiler optimization, where the optimized code needs to be equivalent to the input one .
 \\
 
-\begin{figure}[h!]
-	\noindent\rule{\linewidth}{0.4pt}
-	Empty Statement Axiom
-	\[
-	\begin{prooftree}
-	\Hypo{}
-	\Infer 1 {\{P\}\  \mathtt{skip}\  \{P\}}
-	\end{prooftree}	
-	\]
-	Assignment Axiom 
-	\medskip
-	\[
-	\begin{prooftree}
-	\Hypo{}
-	\Infer 1 {\{P[E/x]\}\  \mathtt{x := E}\  \{P\}}
-	\end{prooftree}	
-	\]
-	Composition Rule
-	\medskip
-	\[
-	\begin{prooftree}
-	\Hypo{ \{P\} S \{Q\}}
-	\Hypo{ \{Q\} T \{R\}}
-	\Infer 2 {\{P\}\  \mathtt{S ; T}\  \{Q\}}
-	\end{prooftree}	
-	\]
-	Consequence Rule
-	\medskip
-	\[
-	\begin{prooftree}
-	\Hypo{P \Rightarrow P\prime}
-	\Hypo{\{P\prime\} C \{Q\prime\}}
-	\Hypo{Q \Rightarrow Q\prime}
-	\Infer 3 {\{P\}\  C  \{Q\}}
-	\end{prooftree}	
-	\]
-	Auxiliary Variable Elimination Rule
-	\medskip
-	\[
-	\begin{prooftree}
-	\Hypo{\{P\} C \{Q\}}
-	\Infer 1 [\(x \notin Free(C)\)]{\{\exists x.P\}\ C\ \{\exists x. Q\}}
-	\end{prooftree}	
-	\]
-	Conditional Rule
-	\medskip
-	\[
-	\begin{prooftree}
-	\Hypo{\{B \land P\} S \{Q\}}
-	\Hypo{\{\neg B \land P\} T \{Q\}}
-	\Infer 2 {\{P\} \mathtt{if\ B\ then\ S\ else\ T\ fi} \{Q\}}
-	\end{prooftree}	
-	\]
-	While Rule
-	\medskip
-	\[
-	\begin{prooftree}
-	\Hypo{\{P \land B\} S\{P\}}
-	\Infer 1 {\{P\}\  \mathtt{while\ B\ do\ S\ od}\  \{\neg B \land P\}}
-	\end{prooftree}	
-	\]
-	\caption{Hoare Logic Rules}
-	\label{fig:HLRules}
-	\noindent\rule{\linewidth}{0.4pt}
-\end{figure}
+This project aims to lay the foundations of a tool which facilitates formal reasoning about program equivalence with a focus on extensibility and automation of tasks.
 
-At the base of proofs based on Hoare Logic are a set of axioms and proof rules which can be applied to Hoare triples, presented in Figure \ref{fig:HLRules}
+\section{Previous work}
+Previous work related to the topic has been done mostly in terms of Separation Logic based tools, with Relational Separation Logic not being treated as much. \\
 
-\subsection{Separation Logic}
-Separation Logic is an extension of Hoare Logic which simplifies reasoning about program execution by introducing ways of localising parts of the proof : draw conclusions based on a subset of the program state, the subset chosen such that it contains only the parts relevant to the command specified in the analysed Hoare triple.
-\\
-
-The main feature of Separation Logic is the \textbf{separating conjunction} \(*\) which allows to split the assertion into parts which refer to disjoint areas of the heap.
-Through the \(*\) operator, Separation Logic enables reasoning about the effects of commands only at a local level, by splitting the assertions into a section which is relevant to the current command and "saving" the rest for subsequent commands.
-\\
-
-Separation Logic introduces new elements to the assertions language - Figure \ref{fig:SLassertionSyntax}:  \\
-
-\begin{figure}
-	\noindent\rule{\linewidth}{0.4pt}
-	\begin{tabularx}{\linewidth}{l  X}
-		Assertions& \(P ::= ... (specified\ previously) \mid E \mapsto E \mid P * P \mid emp \) \\
-	\end{tabularx}
-	\caption{Syntax of the assertion language}
-	\label{fig:SLassertionSyntax}
-	\noindent\rule{\linewidth}{0.4pt}
-\end{figure}
-
-\paragraph{Semantics of the new elements}
-\begin{itemize}
-	\item{\(E \mapsto E\prime \) means that the heap has an active cell at address \(E\), with the content \(E\prime\), and the cell is the \textbf{only} active cell in the heap}
-	\item{\(P * Q\) holds for heap \(h\) iff \(\exists h_0,h_1\) such that \(h_0 * h_1 = h\) and \(P\) holds for \(h_0\) and \(Q\) holds for \(h_1\)}
-	\item{\(emp\) denotes a heap without any active cells}
-\end{itemize}
-\paragraph{Inference Rules for Separation Logic} 
-Separation Logic introduces a new rule, called Frame Rule, which makes use of the \(*\) operator to allow local reasoning :
-\\
-\noindent\rule{\linewidth}{0.4pt}
-Frame Rule
-\medskip
-\[
-\begin{prooftree}
-\Hypo{\{P\}\ C\ \{Q\}}
-\Infer 1 [\(Modifies(C) \cup Free(R) = \emptyset \)]{\{P * R \}\ C\ \{Q * R\}}
-\end{prooftree}		
-\]
-\noindent\rule{\linewidth}{0.4pt}
-\subsection{Relational Separation Logic}
-Relational Separation Logic builds upon the foundations layed by the Separation Logic by extending it to facilitate analysing how two programs are related. 
-\paragraph{Hoare Quadruple}
-The main abstraction introduced by the Relational Separation Logic is the Hoare Quadruple, which express the effects of commands on the states of the two programs. 
-\[\{R\}\ {C_1 \atop C_2}\   \{T\}\]
-
-\(R\) represents a \textbf{relation} between the two program states holding before the execution of \(C_1\) and \(C_2\) respectively while \(T\) represents a \textbf{relation} which holds after the execution of the two commands.
-\\
-
-Since relational separation language reasons about two programs simultaneously, it employs a storage model in which both programs share a single \(Store\) but have independent \(Heaps\).
-This implies that the programs need to use \textbf{disjoint} parts of the same \(Store\).
-The benefit of such a model is that we can use variables in Relations which aren't used by the two programs directly to relate them.
-\begin{figure}[h]
-	\noindent\rule{\linewidth}{0.4pt}
-	\medskip
-	\begin{tabularx}{\linewidth}{l  X}
-		Relation& \(R ::= Same \mid Emp \mid \left( P_1 \atop P_2 \right) \mid R_1 * R_2 \mid B \mid R_1 \Rightarrow R_2 \mid R_1 \land R_2 \mid R_1 \lor R_2 \mid \neg R \mid \exists x.
-R \mid \forall x.
-R \) \\
-	\end{tabularx}
-	\caption{Syntax of the relation language}
-	\label{fig:RelationSyntax}
-	\noindent\rule{\linewidth}{0.4pt}
-\end{figure}
-\paragraph{Semantics of the Relation Language}
-The semantics of the Relation Language are derived from the semantics of the Assertion Language, and in the following section I will present the newly introduced elements. 
-\begin{itemize}
-	\item{ \(Same\) denotes that the heaps associated with the 2 programs are identical}
-	\item{ \(Emp\) is the Relational equivalent of the \(emp\) assertion; specifies two empty heaps}
-	\item{ \(\left(P_1 \atop P_2\right)\) is the building block of the Relational separation logic: it allows to construct a relation between programs by putting together 2 assertions, \(P_1\) holding for the first program and \(P_2\) holding for the second program}
-	\item{ \(R_1 * R_2\) represents the relational separating conjunction and it keeps a similar meaning to the Separation Logic one ; it separates two relations referring to \textbf{disjoint} parts of the heaps of the two programs.}
-\end{itemize}
-\begin{figure}
-		\noindent\rule{\linewidth}{0.4pt}
-	Loop:
-	\[
-	\begin{prooftree}
-	\Hypo{R \Rightarrow (B \Leftrightarrow B\prime)}
-	\Hypo{\{R \land B \} {C \atop C\prime} {R}}
-	\Infer 2 {\{R\}
-		\let\scriptstyle\textstyle 
-		\substack{\mathtt{while\ B\ do\ C\ od} \\ \mathtt{while\ B\prime\ do\ C\prime\ od}} \{R \land \neg B\}}
-	\end{prooftree}	
-	\]
-	Conditional Statement
-	\[
-	\begin{prooftree}
-	\Hypo{R \Rightarrow (B \Leftrightarrow B\prime)}
-	\Hypo{ \{R \land B\} 		
-		\let\scriptstyle\textstyle 
-		\substack{C_1 \\ C_1\prime} \{S\}
-		}
-	\Hypo{
-		\{R \land \neg B\}
-		\let\scriptstyle\textstyle 
-		\substack{C_2 \\ C_2\prime}
-		\{S\}
-	}
-	\Infer 3 {\{R\}\  	
-				\let\scriptstyle\textstyle 
-				\substack{\mathtt{if\ B\ then\ C_1\ else\ C_2\ fi} \\ \mathtt{if\ B\prime\ then\ C_1\prime\ else\ C_2\prime fi}} \{S\}}
-	\end{prooftree}	
-	\]
-	Sequencing Rule
-	\[
-	\begin{prooftree}
-	\Hypo{ \hq{R}{C_1}{C_1\prime}{S}}
-	\Hypo{ \hq{S}{C_2}{C_2\prime}{T}}
-	\Infer 2 {\hq{R}{C_1 ; C_2}{C_1\prime ; C_2\prime}{T}}
-	\end{prooftree}	
-	\]
-	Frame Rule
-	\[
-	\begin{prooftree}
-	\Hypo { \hq{R}{C}{C\prime}{S}}
-	\Infer 1 {\hq{R * T} {C}{C\prime}{S * T}}
-	\end{prooftree}	
-	\]
-	Embedding rule
-	\[
-	\begin{prooftree}
-	\Hypo{\{P\} C \{Q\}}
-	\Hypo{\{P\prime\} C\prime \{Q\prime\}}
-	\Infer 2 {\hq{\left( \substack{P \\ P\prime}\right)}{C}{C\prime}{\left( \substack{Q \\ Q\prime}\right)}}
-	\end{prooftree}	
-	\]
-	Consequence Rule
-	\[
-	\begin{prooftree}
-	\Hypo{R \Rightarrow R_1}
-	\Hypo{\hq{R_1}{C}{C\prime}{S_1}}
-	\Hypo{S \Rightarrow S_1}
-	\Infer 3 {\hq{R}{C}{C\prime}{S}}
-	\end{prooftree}	
-	\]
-	Conjunction Rule
-	\[
-	\begin{prooftree}
-	\Hypo{\hq{R_1}{C}{C\prime}{S_1}}
-		\Hypo{\hq{R_2}{C}{C\prime}{S_2}}
-	\Infer 2 {\hq{R_1 \land R_2}{C}{C\prime}{S_1 \land S_2}}
-	\end{prooftree}	
-	\]
-	Auxiliary Variable Elimination
-	\[
-	\begin{prooftree}
-	\Hypo{\hq{R}{C}{C\prime}{S}}
-	\Infer 1 {\hq{\exists x.R}{C}{C\prime}{\exists x.S}}
-	\end{prooftree}	
-	\]
-	\caption{Relational Separation Logic Proof Rules}
-	\label{fig:ProofRue}
-	\noindent\rule{\linewidth}{0.4pt}
-\end{figure}
-
-Most of the rules are adapted from the Separation Logic ones, and the link between the two logics is given by the \textbf{Embedding Rule}, which allows to transform a Relational Separation Logic Hoare Quadruple into two Separation Logic Hoare Triples.
-The rules are presented in Figure \ref{fig:ProofRue}.
-\clearpage
-\subsection{Rewriting Logic}
-Rewriting logic is both a semantic and logical framework \cite{rewritingLogic} in which, via \textbf{term rewriting}, changes within systems (concurrent or not) and other logics can be expressed naturally.
-The latter represents the motivation for choosing rewriting logic for our project, as well as extensibility in the future, in terms of concurrent program analysis.
-\\
-
-One of the strong points of rewriting logic is that it reduces the \textbf{representational distance}, as it was named in \cite{rewritingLogic}, of the systems modelled using it.
-Representational distance is how much detail is lost in the translation process between semantic representation and implementation.
-This feature will be highlighted in the following sections, describing the Maude representation of the Relational Separation Logic and an executable semantic specification of the language supported by the prover.
-As we can see, the Relational Separation Logic has been represented naturally using rewrite rules and the translation process between representation and implementation usually involves just syntactic differences.\\
-
-A rewrite theory is a triplet : \[\mathcal{R} = (\Sigma, E, R)\]
-where \(\Sigma\) represent the "environment" - in our case, \(\Sigma\) represents all the symbols which can appear when representing a Hoare Quadruple and their corresponding operators , \(E\) represents a set of equations denoting algebraic identities for \(\Sigma\) and \(R\) represents a set of rewrite rules, possibly conditional which take the form of \(t \leftarrow t\prime\ [condition]\), where \(t\) and \(t\prime\) are terms.
-\section{Relational Separation Logic Interactive Prover} 
-Ordinea subsectiunilor mai poate fi schimbata ulterior. Capitolul cel mai semnificativ din lucrare, va contine toate detaliile de implementare ale solutiei curente
-\subsection{Maude - General Overview}
-\subsection{Executable semantics of the language}
-\subsection{Modelling the Separation Logics}
-\subsection{Interaction by Maude LOOP-MAUDE}
-\subsection{Prover execution flow}
-\subsection{Automated processes}
-\subsubsection{Automatic matching of axioms and previously proven goals}
-\subsubsection{Automatic demonstration of implications}
-\subsection{User Interface}
-\subsection{Future directions}
-\section{Additional Research}
-\subsection{Automatic prover}
-\subsection{Concurrent programs extension}
-\subsection{Java+ITP}
-
-\section{Conclusions}
-\pagebreak
+A notable example which also uses the same framework as this project, namely Maude, is the Java+ITP\cite{JAVAITP} tool, which enables analysis of Java programs using Separation Logic.
+The implementation relies heavily on Maude's ITP (iterative theorem prover).
 \bibliographystyle{unsrt}
 \bibliography{bibliography}
+
 \end{document}

### 2018-06-18 paper/paper_after_guide.tex
started describing personal contributions to the project

@@
 The implementation relies heavily on Maude's ITP (iterative theorem prover).
+
+\section{Relational Separation Logic Interactive Prover} 
+This chapter will include details related to the implementation and usage of the Relational Separation Logic prover and highlight a few of Maude's features which made it the a language fit for the purpose of this project.
+\subsection{Modelling the Separation Logics}
+Thanks to Maude's ability to naturally represent logics, the modelling of the Separation Logic and Relational Separation Logic is mostly reduced to translating the logical formulae into appropriate syntax for Maude, making the representational distance \cite{maudeprimer} almost non existent.
+\\
+
+Each proof rule in the Separation Logic and Relational Separation Logic has been translated into a Maude rewrite rule.
+The resulting rules have been marked as non-executable because the goal is to control when they are applied.
+\subsection{Interaction by Maude LOOP-MODE}
+Maude's LOOP-MODE module is the entry point for any interactive Maude application, being the only way to store state between commands.
+In this chapter we will discuss how we handle input and output , the structure of a state and the role every element plays in the execution of the prover.\\
+
+We will make a distinction between \textbf{Loop state}, which specific to Maude's LOOP-MODE module and the \textbf{Prover state} which is specific to our use-case, and holds the necessary data related to the state of the proof we are currently working on.
+The \textbf{Prover state} is encapsulated within \textbf{Loop state}.
+\subsection{Input and output handling}
+To understand how our prover handles input and output, it is important to note that the flows of the LOOP-MODE module is as follows: 
+\begin{figure}
+	Aici va veni figura care explica input -> rewriting maxim -> output
+\end{figure}
+\subsection{State of the program}
+Following the examples provided together with the Maude Manual \cite{manual}, our state is composed multiple sections modified accordingly during program execution .
+\subsection{Prover execution flow}
+In this section we will describe the flow of a demonstration made using our prover.
+\subsection{Automated processes}
+This section will describe the functional parts of the prover which have been automated to make it more user-friendly and even prove sub-goals of the main demonstration by itself.
+Since the automation of the prover is part of the future goals of this project, we will also include a few notes on how we might approach problems related to this goal, even though they have not been implemented yet.
+\subsubsection{Automatic matching of axioms and previously proven goals}
+\subsubsection{Automatic demonstration of implications}
+\subsection{User Interface}
+Since our project aims to simplify the demonstrations of Separation Logic / Relational Separation Logic formulae, using an interactive prover, the user interface plays a major role in the success of the project - the easier it is to use and understand, the more chances of success it has.
+This idea has been presented in \cite{primer}, when discussing key elements of tools related to program verification.
+\\
+
+Maude provides a simple, yet powerful system for controlling the output formatting of the CLI through which we aim to make the demonstrations more readable and user-friendly. \\
+
+For a more advanced user interface or to expose the prover's functionalities through a programming interface, a wrapper written in more feature-rich language through which to control the Maude environment is probably the best choice.
+The concept is exemplified the Maude plug-in for Eclipse, \textbf{citation needed} which enables writing of Maude code inside the Eclipse IDE, and the plug-in communicates with the underlying Maude environment.
+\subsection{Future directions}
+
+\section{Conclusions}
+
+\pagebreak
 \bibliographystyle{unsrt}

### 2018-06-19 paper/paper_after_guide.tex
intermediary commit
wrote about actions and program states

@@
 The resulting rules have been marked as non-executable because the goal is to control when they are applied.
+\\
+The prover is centered around the concept of \textbf{Goals} which can be one of the three things: 
+\begin{itemize}
+	\item {Hoare Quadruple} - corresponding to Relational Separation Logic
+	\item {Hoare Triple} - corresponding to Separation Logic
+	\item {Implication between relations / assertions} 
+\end{itemize} 
+The proof rules are interpreted in a bottom-up manner, meaning that applying a rule to a goal matching the conclusion of a rule will generate new goals consisting of the hypothesis elements of the rule.
+\begin{figure}
+	This figure will explain how we translated the proof rules into Maude syntax
+\end{figure}
+\subsubsection{Sort Hierarchy}
+This section will describe the sorts defined in Maude to handle the constructs of both Separation logics.
+\subsection{Language Grammar and executable semantics}
+This section will describe how we defined our language in Maude [and how it is possible to create executable semantics for this language]
 \subsection{Interaction by Maude LOOP-MODE}
@@
 Following the examples provided together with the Maude Manual \cite{manual}, our state is composed multiple sections modified accordingly during program execution .
+\begin{itemize}
+	\item{\textbf{Action} - represents the current action to be executed by the prover, more details about supported actions are included in the following sections.}
+	\item{\textbf{Root Goal} - represents the end-goal of this demonstration}
+	\item{\textbf{Current Goal} - the goal being treated currently - all actions will be applied to this goal}
+	\item{\textbf{Goal Stack} - Stack of goals necessary to be proven in order to prove the root goal.
+The current goal is the last element popped from the stack and new elements are generated and pushed by the application of proof rules to the current goal.}
+	\item{\textbf{Proven Goals} - List of goals which have been already been proven or axioms.
+Each goal will be first checked to see if it matches any goal in this list to prevent repeating the same proofs.}
+	\item{\textbf{Staging output} - contains the output generated by the current action, before being passed to the Loop state.
+This staging mechanism enables each action (user or system) to generate output independent of the other actions.}
+\end{itemize}
 \subsection{Prover execution flow}
 In this section we will describe the flow of a demonstration made using our prover.
+\subsubsection{User Actions}
+User actions are the main entry point for user interaction and they describe how the user intends to process the current goal.
+\begin{itemize}
+	\item {Rule application action - indicates the application of a specific rule to the current goal, the action can be parameterized or not, depending on the rule.}
+	\item {ok action - admits the current goal}
+	\item {showGoal action - prints the current goal to the console - it does not modify the state of the prover}
+\end{itemize}
+\subsubsection{System Actions}
+System actions were implemented to mimic the behaviour of a "chain of responsibility" design pattern from object-oriented programming.
+The system actions are all applied in order before asking for user input.
+System actions are the main component through which our prover can be enriched with other features in the future, because integrating a new system action is simple.
+At the moment, the system actions are:
+\begin{itemize}
+	\item {check} - marks the current goal to be checked against previously proven goals or axioms
+	\item {implication} - marks the current goal to be run through the implication prover - in case the goal is an implication, try to prove it automatically
+	\item {stop} - when there are no more sub-goals to be proven, the prover should stop and indicate the success of proving the root goal
+\end{itemize}
 \subsection{Automated processes}

### 2018-06-20 paper/paper_after_guide.tex
added brief introduction into separation logic and hoare logic

@@
 \usepackage{tabularx}
+\usepackage{tikz}
 \usepackage{ebproof}
+\usepackage{listings}
 \author{ANDREI-ALIN CORODESCU}
@@
 }
+\usepackage{color}
 
+\definecolor{codegreen}{rgb}{0,0.6,0}
+\definecolor{codegray}{rgb}{0.5,0.5,0.5}
+\definecolor{codepurple}{rgb}{0.58,0,0.82}
+\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
+\lstdefinestyle{mystyle}{
+	backgroundcolor=\color{backcolour},   
+	commentstyle=\color{codegreen},
+	keywordstyle=\color{magenta},
+	numberstyle=\tiny\color{codegray},
+	stringstyle=\color{codepurple},
+	basicstyle=\footnotesize,
+	breakatwhitespace=false,         
+	breaklines=true,                 
+	captionpos=b,                    
+	keepspaces=true,                 
+	numbers=left,                    
+	numbersep=5pt,                  
+	showspaces=false,                
+	showstringspaces=false,
+	showtabs=false,                  
+	tabsize=2
+}
+
+\lstset{style=mystyle}
 \begin{document}
@@
 The rest of the paper is organized as follows: 
+\begin{itemize}
+	\item {\textbf{Section 1} will describe the main personal contributions to the realization of this project}
+	\item {\textbf{Section 2} will present the problem this project aims to solve}
+	\item {\textbf{Section 3} will shortly present some other projects related to ours}
+	\item {\textbf{Section 4} will briefly touch upon the theoretical foundations of this project, together with the technologies used to implement them}
+	\item {\textbf{Section 5}, the main section of this paper, will present our approach to solving the problem, discuss shortcomings of the current solution and how it can be improved in the future.
+All the elements of our project will be presented in an individual sub-section}
+\end{itemize}
 
@@
 
-This project aims to lay the foundations of a tool which facilitates formal reasoning about program equivalence with a focus on extensibility and automation of tasks.
+This project aims to lay the foundations of a tool which facilitates formal reasoning on the way two programs are related with a focus on extensibility and automation of tasks.
 
@@
 
+\section{Theoretical Foundations and technologies}
+This section will briefly introduce the concepts on which the project is based, together with the technologies used to implement it, along with a few references to resources which explain them in depth.
+\subsection{Separation Logic}
+Separation Logic allows for reasoning about the effects of code on the program state in a formal manner. The main abstraction used in separation logic is the \textbf{Hoare Triple}
+\[ \{P\}\  C\  \{Q\} \]
+where \(P\) denotes the a condition satisfied by state of the program before the execution of the command \(C\) and \(Q\) denotes another condition satisfied by state of the program after the execution of \(C\).
+\\
+
+Good references for reading on separation logic include : 
+\begin{itemize}
+	\item \cite{primer} - for a good introduction and some interesting usages
+	\item \cite{SeparationLogic} - for a more in depth explanation, including the mathematical fundaments of the logic
+\end{itemize} 
+\subsection{Relational Separation Logic}
+Relational Separation Logic, which is the central concept of our project builds upon the Separation Logic to reason about how to programs are related, by using the concept of a \textbf{Hoare Quadruple}
+\[\{R\}\ {C_1 \atop C_2}\   \{T\}\]
+\(R\) represents a \textbf{relation} between the two program states holding before the execution of commands \(C_1\) and \(C_2\) respectively while \(T\) represents a \textbf{relation} which holds after the execution of the two commands.
+\\
+
+Relational Separation Logic is presented in detail in \cite{relational}.
+\subsection{Maude}
+Maude is a framework based on rewriting logic which allows for natural representations of a wide range of applications, including other logics, which made it a perfect fit for our case.
+Maude allows for short and simple, yet clever and self-explanatory solutions to problems.
+\\
+
+ Good references for Maude language include:
+ \begin{itemize}
+ 	\item Maude Primer \cite{primer} which was written for Maude 2.0.1 but still applies to the latest versions of Maude is a good starting point for learning Maude, as it introduces the language in a more informal, friendlier way
+ 	\item Maude Manual \cite{manual} which presents the whole Maude system in depth, along with the mathematical foundations
+ 	\item All about Maude book \cite{allAboutMaude} which includes everything contained in the manual and presents some of the more relevant tools implemented in Maude .
+ \end{itemize}
 \section{Relational Separation Logic Interactive Prover} 
-This chapter will include details related to the implementation and usage of the Relational Separation Logic prover and highlight a few of Maude's features which made it the a language fit for the purpose of this project.
+This section will include details related to the implementation and usage of the Relational Separation Logic prover and highlight a few of Maude's features which made it the a language fit for the purpose of this project.
+\\
+
+The information presented in this section assumes the reader's familiarity with Maude, especially the META-LEVEL module and with the underlying theoretical concepts implemented by the prover (Separation Logic and Relational Separation Logic)
 \subsection{Modelling the Separation Logics}
-Thanks to Maude's ability to naturally represent logics, the modelling of the Separation Logic and Relational Separation Logic is mostly reduced to translating the logical formulae into appropriate syntax for Maude, making the representational distance \cite{maudeprimer} almost non existent.
+Thanks to Maude's ability to naturally represent logics, the modelling of the Separation Logic and Relational Separation Logic is mostly reduced to translating the logical formulae into appropriate syntax for Maude, making the representational distance (the amount of information lost when representing a theoretical concept into a programming language)\cite{manual} almost non existent.
 \\
@@
 Each proof rule in the Separation Logic and Relational Separation Logic has been translated into a Maude rewrite rule. 
-The resulting rules have been marked as non-executable because the goal is to control when they are applied.
 \\
@@
 The \textbf{Prover state} is encapsulated within \textbf{Loop state}.
-\subsection{Input and output handling}
-To understand how our prover handles input and output, it is important to note that the flows of the LOOP-MODE module is as follows: 
-\begin{figure}
-	Aici va veni figura care explica input -> rewriting maxim -> output
+\begin{figure}[h]
+	\noindent\rule{\linewidth}{0.4pt}
+
+	\[
+		[\mathtt{INPUT},\ \mathtt{PROVER-STATE},\ \mathtt{OUPTUT}]
+	\]
+	\label{fig:loopState}
+	\caption{Loop state}
+	\noindent\rule{\linewidth}{0.4pt}
 \end{figure}
 \subsection{State of the program}
-Following the examples provided together with the Maude Manual \cite{manual}, our state is composed multiple sections modified accordingly during program execution .
+Following the examples provided together with the Maude Manual \cite{manual}, our state (Figure \ref{fig:ProverState}) is composed multiple sections modified accordingly during program execution .
 \begin{itemize}
@@
 \end{itemize}
+\begin{figure}[h]
+	\noindent\rule{\linewidth}{0.4pt}
+	\(
+	< \mathtt{Action}, \mathtt{Root Goal}, \mathtt{Current Goal}, \mathtt{Goal Stack}, \mathtt{Proven Goals}, \mathtt{Staging Output} >
+	\)
+	\caption{Prover State}
+	\label{fig:ProverState}
+	\noindent\rule{\linewidth}{0.4pt}
+\end{figure}
+\subsection{Input and output handling}
+To understand how our prover handles input and output, it is important to note that the flows of the LOOP-MODE module is as follows: 
+\begin{enumerate}
+	\item User input is placed in the \(\mathtt{INPUT}\) member of the loop state
+	\item Maude engine applies all the rewritings possible, resulting in a new loop state.
+
+	This is the step where all the logic of the prover goes into, in the form of rewriting rules which modify the prover state.
+	\item The member \(\mathtt{OUTPUT}\) of this new loop state is taken and displayed at the console.
+\end{enumerate}
+There are two main rules used for handling input and output : 
+\begin{enumerate}
+	\item{\texttt{in} rule, which is responsible for parsing the user input and modifying the action in the prover state accordingly}
+	\begin{lstlisting}[caption=in rule]
+crl [in] : 
+--- [ INPUT, <PROVER_STATE>, OUTPUT]
+[QIL, < noRule ; RG ; G ; GS ; GL ; nil > , QIL']
+=> 
+if T:ResultPair? :: ResultPair  
+--- If parsing succeeded, place the parsed action in
+--- the prover state
+then [nil, < downTerm(getTerm(T:ResultPair?), noAction) ; RG ; G ; GS ; GL ; nil >, QIL']  
+--- If the parsing failed, display an error
+else [nil, < noRule ; RG ; G ; GS ; GL ; nil >, 'ERROR QIL]  
+fi  
+--- Try to parse the input as an term of sort Action
+if QIL =/= nil /\ T:ResultPair? := metaParse(upModule('PROVER-GRAMMAR, false), QIL, 'Action) .
+\end{lstlisting}
+	\item{\texttt{out} rule, which takes the staging output from the prover state and appends it to the currently existing output in the loop state}
+	\begin{lstlisting}[caption=out rule]
+crl [out] :
+[QIL, < A ; RG ; G ; GS ; GL ;  QIL' >, QIL'']
+=> [QIL, < A ; RG ; G ; GS ; GL ; nil >, QIL''  QIL']
+if QIL' =/= nil .
+\end{lstlisting}
+\end{enumerate}
+
 \subsection{Prover execution flow}
-In this section we will describe the flow of a demonstration made using our prover.
+In this section we will describe the flow of a demonstration made using our prover. A diagram presenting how the prover works is presented in Figure \ref{fig:ProverDiagram}
+\\
+\begin{enumerate}
+	\item The user issues the command \texttt{loop init .} in the Maude console. This will initialize the loop state.
+	\item Now the user will have to specify the goal it wants to prove, by issuing the command \begin{center}(\texttt{prove} G)\end{center}, where G is the representation of the goal using the syntax defined for our logics.
+The command will populate the required fields of the prover state (\textbf{RootGoal}, \textbf{GoalStack}) with G.
+	\\
+	Please note that the command is enclosed within parentheses, this being a requirement of Maude LOOP-MODE \cite{manual}.
+All the prover specific commands need to be enclosed in parenthesis.
+The previous command, \texttt{loop init .} was not enclosed because it is a Maude specific command, not something we want to pass as input to our prover.
+	\item The next phase involves applying the logic proof rules to the goals in the \textbf{GoalStack} to generate sub-goals and prove them.
+This phase lasts until there are no more goals left in the \textbf{GoalStack}, meaning that the \textbf{RootGoal} has been proven.
+\end{enumerate}
+\begin{figure}[h]
+	\caption{Prover Execution Diagram}
+	\label{fig:ProverDiagram}
+\end{figure}
 \subsubsection{User Actions}
@@
 \begin{itemize}
-	\item {Rule application action - indicates the application of a specific rule to the current goal, the action can be parameterized or not, depending on the rule.}
-	\item {ok action - admits the current goal}
-	\item {showGoal action - prints the current goal to the console - it does not modify the state of the prover}
+	\item {Rule application action - indicates the application of a specific rule to the current goal, the action can be parametrized or not, depending on the rule.
+These actions are named following the pattern :
+	\begin{center}
+		[\textbf{SL}] + \textbf{apply} + \textit{RuleName}
+	\end{center}
+		With \textbf{SL} being added only when applying Separation Logic rules, to distinguish between the Relational Separation Logic rules with the same name.
+	}
+	\begin{figure}[h]
+		\caption{Examples of user actions which control the application of rules}
+		\label{fig:userActions}
+	\end{figure}
+	\item {\(\mathtt{ok}\) action - admits the current goal}
+	\item {\(\mathtt{showGoal}\) action - prints the current goal to the console - it does not modify the state of the prover}
 \end{itemize}
@@
 \begin{itemize}
-	\item {check} - marks the current goal to be checked against previously proven goals or axioms
-	\item {implication} - marks the current goal to be run through the implication prover - in case the goal is an implication, try to prove it automatically
-	\item {stop} - when there are no more sub-goals to be proven, the prover should stop and indicate the success of proving the root goal
+	\item {\texttt{check}} - marks the current goal to be checked against previously proven goals or axioms
+	\item {\texttt{implication}} - marks the current goal to be run through the implication prover - in case the goal is an implication, try to prove it automatically
+	\item {\texttt{stop}} - when there are no more sub-goals to be proven, the prover should stop and indicate the success of proving the root goal
 \end{itemize}

### 2018-06-20 paper/paper_after_guide.tex
added translations to Maude syntax for proof rules

@@
 \usepackage{listings}
+\usepackage{url}
 \author{ANDREI-ALIN CORODESCU}
@@
 \subsection{Maude}
-Maude is a framework based on rewriting logic which allows for natural representations of a wide range of applications, including other logics, which made it a perfect fit for our case.
+Maude \cite{maudesite} is a framework based on rewriting logic \cite{rewritingLogic} which allows for natural representations of a wide range of applications, including other logics, which made it a perfect fit for our case.
 Maude allows for short and simple, yet clever and self-explanatory solutions to problems.
@@
 
-The information presented in this section assumes the reader's familiarity with Maude, especially the META-LEVEL module and with the underlying theoretical concepts implemented by the prover (Separation Logic and Relational Separation Logic)
+The information presented in this section assumes the reader's familiarity with Maude, especially the META-LEVEL module and with the underlying theoretical concepts implemented by the prover (Separation Logic and Relational Separation Logic).
+References for these can be found in the previous section.
+\\
+
+This section will include snippets of Maude code, but since Maude is a very expressive and self-explanatory language, I have not included of thorough presentation of every language construct defined for the scope of this project.
+Ideas presented will be accompanied by some examples and key ideas of the implementation but for a more detailed presentation, please refer to the code itself.
+
 \subsection{Modelling the Separation Logics}
@@
 \end{itemize} 
-The proof rules are interpreted in a bottom-up manner, meaning that applying a rule to a goal matching the conclusion of a rule will generate new goals consisting of the hypothesis elements of the rule.
-\begin{figure}
-	This figure will explain how we translated the proof rules into Maude syntax
+The proof rules are interpreted in a bottom-up manner, meaning that applying a rule to a goal matching the conclusion of a rule will generate new goals consisting of the hypothesis elements of the rule : Figure \ref{fig:SLTranslation} presents how a Separation Logic rule has been translated into Maude syntax and Figure \ref{fig:RSLTranslation} presents the same process for the Relational Separation Logic counterpart of the rule.
+\begin{figure}[h]
+	Consequence Rule
+	\medskip
+	\[
+	\begin{prooftree}
+	\Hypo{P \Rightarrow P\prime}
+	\Hypo{\{P\prime\} C \{Q\prime\}}
+	\Hypo{Q \Rightarrow Q\prime}
+	\Infer 3 {\{P\}\  C  \{Q\}}
+	\end{prooftree}	
+	\]
+	Is represented in Maude syntax as : 
+\begin{lstlisting}[caption=Separation Logic Consequence rule]
+	rl [SeparationLogic-Consequence] : {P} C {Q} => ((P => P1) <> ({P1} C {Q1})) <> (Q1 => Q) [nonexec] .
+\end{lstlisting}
+	\caption{Example of a translation to Maude syntax of a Separation Logic proof rule}
+	\label{fig:SLTranslation}
 \end{figure}
+
+\begin{figure}[h]
+	Consequence Rule
+	\[
+	\begin{prooftree}
+	\Hypo{R \Rightarrow R_1}
+	\Hypo{\hq{R_1}{C}{C\prime}{S_1}}
+	\Hypo{S \Rightarrow S_1}
+	\Infer 3 {\hq{R}{C}{C\prime}{S}}
+	\end{prooftree}	
+	\]
+	Is represented in Maude syntax as : 
+	\begin{lstlisting}[caption=Relational Separation Logic Consequence rule]
+	rl [Consequence] : { R } C1 -- C2  { S } => ((R => R1) <> ({R1} C1 -- C2 {S1})) <> (S1 => S) [nonexec] .
+	\end{lstlisting}
+	\caption{Example of a translation to Maude syntax of a Relational Separation Logic proof rule}
+	\label{fig:RSLTranslation}
+\end{figure}
+The \texttt{<>} operator is used to separate sub-goals generated by the rule.
+\\
+
+The \texttt{---} operator is used to separate the two snippets of code mentioned in the \textbf{Hoare Quadruple}.
+\\
+
+All the rules are marked with the attribute \texttt{[nonexec]} because we want them to be applied in a controlled manner, at the meta-level.
+Some of the rules, the examples included, are not even valid executable Maude rules, because they make use of variables before binding them (for example \texttt{P1} is used in a rule before it is bound).
+At the meta-level however we can manually bind values to those variables, as we will exemplify when discussing how we apply these rules to goals.
 \subsubsection{Sort Hierarchy}
@@
 For a more advanced user interface or to expose the prover's functionalities through a programming interface, a wrapper written in more feature-rich language through which to control the Maude environment is probably the best choice.
-The concept is exemplified the Maude plug-in for Eclipse, \textbf{citation needed} which enables writing of Maude code inside the Eclipse IDE, and the plug-in communicates with the underlying Maude environment.
+The concept is exemplified the Maude plug-in for Eclipse, \cite{maudeEclipsePLugin} which enables writing of Maude code inside the Eclipse IDE, and the plug-in communicates with the underlying Maude environment.
+The project also includes a plug-in which allows any Java program to communicate with Maude.
 \subsection{Future directions}

### 2018-06-21 paper/paper_after_guide.tex
explained sorts defined for language and SL

@@
 \usepackage{listings}
+\usepackage{graphicx}
 \usepackage{url}
@@
 \subsubsection{Sort Hierarchy}
-This section will describe the sorts defined in Maude to handle the constructs of both Separation logics.
+Much in the same manner as we modeled the language grammar, the Relational Separation Logic \cite{relational} and Separation Logic \cite{SeparationLogic} \cite{primer} have been modeled by defining sorts and declaring operators using these sorts.
+The main point of reference for our modeling has been \cite{relational}, for both logics.
+Some examples of translations from specification to code are included below.
+\begin{itemize}
+	\item \texttt{Assertion} is the sort used to handle Separation Logic assertions. It is a super sort of the \texttt{BExp} sort defined as part of our language.
+	\item \texttt{HoareTriple} is the sort associated with the concept with the same name, in a Separation Logic context.
+	\begin{lstlisting}[caption=Hoare Triple constructor operator]
+op {_}_{_} : Assertion Command Assertion -> HoareTriple .\end{lstlisting}
+	\item \texttt{Relation} is the sort associated with Relational Separation Logic relations.
+As it was the case with \texttt{Assertion}, it is a super sort of the \texttt{BExp} sort of our language grammar.
+Because both the \texttt{Relation} and \texttt{Assertion} are super sorts of the same sort, Maude will display a few warnings which are not affecting functionality, but in the future, creating a separate \texttt{BExp} sort for both the \texttt{Assertion} and \texttt{Relation} sorts would be a better option.
+	\item \texttt{HoareQuadruple} is again associated with the concept with the same name, in the Relational Separation Logic context.
+	\begin{lstlisting}[caption=Examples of Relational Separation Logic specific constructs]
+--- Operator which creates a relation from two assertions
+op [_;_] : Assertion Assertion -> Relation .
+--- Operator which constructs a Hoare Quadruple 
+op {_}_--_{_} : Relation Command Command Relation -> HoareQuadruple .\end{lstlisting}
+\end{itemize}
+The other operators defined for the Assertion and Relation languages have been in the same manner as the programming language operators, following their presentation in \cite{relational}.
+For a full reference, please refer to the code accompanying this paper.
 \subsection{Language Grammar and executable semantics}
-This section will describe how we defined our language in Maude [and how it is possible to create executable semantics for this language]
+The prover supports expressing programs in a simple, imperative language, commonly used throughout papers \cite{SeparationLogic} \cite{primer} related to the subject of program verification, including the one describing Relational Separation Logic \cite{relational}, around  which this project is based.
+\subsubsection{Storage Model}
+A state of in our storage model is defined by a pair consisting of a \(Store\) and a \(Heap\) .
+\\
+Assuming that all the variables usable in programs from the set \(\mathtt{Vars}\) and the set of positive natural numbers is denoted by \(\mathtt{PosNats}\): \\
+
+A \(Store\) is defined as:
+\[ \mathtt{S} : \mathtt{Vars} \rightarrow \mathtt{PosNats} \]
+
+A \(Heap\) represents a mapping from the \(\mathtt{PosNats}\) to \(\mathtt{Integers}\)
+\[ \mathtt{H} : \mathtt{PosNats} \rightarrow \mathtt{Integers} \] 
+More informally, the \(Store\) holds the value of the variables while the \(Heap\) maps the active memory cells during a program execution to their contents.
+\subsubsection{Syntax and Semantics of the language}
+\begin{figure}[h]
+	\noindent\rule{\linewidth}{0.4pt}
+	\begin{tabularx}{\linewidth}{l  X}
+		Integer Expressions& \(E ::= x \mid Integer \mid E\ \mathtt{plus}\ E \mid E\ \mathtt{times}\ E \mid E\ \mathtt{minus}\ E \) \\
+		\\
+		Boolean Expressions& \(B ::= false \mid true \mid B\ \mathtt{\&\&}\ B \mid  B\ ||\ B \mid B\  \mathtt{->}\ B \mid B \mathtt{<=>} B \mid \ !
+B \mid E\ \mathtt{ge}\ E \mid E\ \mathtt{le}\ E \mid E\ \mathtt{eqs}\ E \)\\
+		\\ 	
+		Commands& \(C ::= x := alloc(E) \mid x := [E] \mid [E] := E \mid free(E) \mid x := E \mid C;C \mid if\ B\ then\ C\ else\ C \mid while\ B\ do\ C\ od \) \\
+	\end{tabularx}
+	\caption{Syntax of the language}
+	\label{fig:langSyntax}
+	\noindent\rule{\linewidth}{0.4pt}
+\end{figure}
+The syntax of the language is presented in Figure \ref{fig:langSyntax} . It represents an adapted subset of the language presented in the Relational Separation Logic paper \cite{relational} . 
+\paragraph{Semantics of the language}
+{
+	The semantics of the previously defined language are standard but a few clarifications are necessary to point out how our language constructs interact with the storage model, as well as a few differences from regular programming languages:
+	\begin{itemize}
+		\item{Verbosity of operators - most operators are replaced by their literal names ( \(+\) becomes \(\mathtt{plus}\) etc.); we have opted for this approach to avoid complication when implementing the language in Maude, because most of the operators are already defined in Maude for its built-in types, and overloading them could cause conflicts since we are basing our own defined types on Maude's primitives.}
+		\subitem{\( B\ \mathtt{ge}\ B\) translates to the usual \(>=\) operator}
+		\subitem{\( B\ \mathtt{le}\ B\) translates to the usual \(<=\) operator}
+		\subitem{\( B\ \mathtt{eqs}\ B\) translates to the usual \(==\) equality comparison operator}
+		\subitem{\( B\ \mathtt{->}\ B\) denotes implication between boolean expressions}
+		\subitem{\(B\ \mathtt{<=>}\ B\) denotes equivalence between boolean expressions}
+		\subitem{The rest of the operators are mostly similar to their C++ or Java counterparts and their semantics are self explanatory}
+		\item{Memory allocation / deallocation: }
+		\subitem{\(x := alloc(E)\) allocates a new cell in the memory, initializes it with the value of \(E\) and stores its address in the variable \(x\)}
+		\subitem{\(x := free(E)\) deallocates the cell at the address equal to the value of \(E\)}
+		\item{Working with variables and memory: }
+		\subitem{\( x := [E] \) reads the contents of the memory cell at address \(E\) and stores the value in the variable \(x\)}
+		\subitem{\( [E] := E\prime \) updates the contents of the memory cell at address \(E\) with the value of the expression \(E\prime\)}
+		\subitem{\( x := E \) updates the value of the variable \(x\) with the value of the expression \(E\) - note that this command does not modify the heap in any way, as it usually happens with regular programming languages when updating the value of a variable}
+	\end{itemize}
+\paragraph{Maude Modelling of the language}
+Maude makes the representation of programming languages grammar a straight forward and natural process, by defining sorts corresponding to language elements and their associated operators.
+The sorts defined in Maude for the grammar are the following :
+\begin{itemize}
+	\item \texttt{AExp} - abbreviation for Arithmetic Expression - equivalent for Integer expressions in the specification.
+To capture the first two possible forms of Integer expressions in Figure \ref{fig:langSyntax}, the AExp sort is a super sort of \texttt{Int} of \texttt{INT} standard module and \texttt{Id}, which is the sort defined for variables.
+	\item \texttt{BExp} - abbreviation for Boolean Expressions - equivalent for the Boolean Expressions type in the specification. It is a super sort of \texttt{Bool} of standard module \texttt{BOOL}. 
+	\item \texttt{Command} sort maintains the same name as in the specification.
+\end{itemize}
+An example of operator translation from specification to Maude code is presented in Listing \ref{code:languageGrammer}.
+Note that we have opted to skip the attributes associated with the operators, as they are irrelevant in this case.
+\\
+
+\begin{lstlisting}[label=code:languageGrammer,caption=Example of operator translation to Maude code]
+	op while_do_od : BExp Command -> Command [...].
+	op _:=_ : Id AExp -> Command [...]. 
+\end{lstlisting}
+
+\paragraph{Executable semantics of the language, in Maude}
+Maude also supports specifying executable semantics for the language using rewriting logic \cite{rewrConcurrency}.
+A proof of concept for a language similar to the one used by the prover is present in the code of the project, but it is out of scope for the presentation of the prover \textbf{Need reference to the final file name}.
+An executable environment for the programming language used in the prover is a valid candidate for future improvements.
 \subsection{Interaction by Maude LOOP-MODE}
@@
 \subsection{Prover execution flow}
-In this section we will describe the flow of a demonstration made using our prover. A diagram presenting how the prover works is presented in Figure \ref{fig:ProverDiagram}
+In this section we will describe the flow of a demonstration made using our prover.
+The most important parts of the prover's execution are controlled through the first member of a prover state, \textbf{Action}, which specifies the next step in the processing of the current goal.
+There are two types of actions, \textbf{System Actions}, colored in the figure in purple and \textbf{User Actions}, colored in light-yellow.
+The diagram presenting how the prover works is presented in Figure \ref{fig:ProverDiagram}
 \\
@@
 	\\
+
+	This command will also populate the \textbf{ProvenGoals} list with axioms.
+	\\
+
 	Please note that the command is enclosed within parentheses, this being a requirement of Maude LOOP-MODE \cite{manual}.
@@
 \begin{figure}[h]
+	\includegraphics[width=\linewidth]{"pictures/Prover Flow".png}
 	\caption{Prover Execution Diagram}
@@
 \end{figure} 
+\clearpage
 \subsubsection{User Actions}
@@
 The system actions are all applied in order before asking for user input.
+After an system action completes execution, it will decide the next action to be placed in the prover state.
 System actions are the main component through which our prover can be enriched with other features in the future, because integrating a new system action is simple.

### 2018-06-21 paper/paper_after_guide.tex
preparing for user interface screenshot

@@
 	}
-	\begin{figure}[h]
-		\caption{Examples of user actions which control the application of rules}
-		\label{fig:userActions}
-	\end{figure}
+		\begin{lstlisting}[label=userAction,caption=Rule Application Action]
+	crl [applyConsequence] : < applyConsequence R1 -- S1 ; RG ; G ; GS ; GL ; nil > =>
+		if SubGoals? :: Result4Tuple then 
+		if downTerm(getTerm(SubGoals?), emptyGL) :: GoalList then
+		< noAction ; RG ; noGoal ; downTerm(getTerm(SubGoals?), emptyGL) <> GS ; GL ; 'applied '  'consequence '  'rule '\n > 
+		else
+		< noAction ; RG ; G ; GS ; GL ; 'did ' 'not ' 'apply ' 'consequence '  'rule '\n > 
+		fi
+		else 
+		< noAction ; RG ; G ; GS ; GL ; 'error '  'consequence '  'rule '\n > 
+		fi 
+	if SubGoals? := metaXapply(upModule('PROVER-INTERFACE, false), upTerm(G), 'Consequence, 'R1:Relation <- upTerm(R1) ; 'S1:Relation <- upTerm(S1) , 0, unbounded, 0).
+		\end{lstlisting}
+		The example given in Listing \ref{userAction} illustrates all the core concepts involved in the application of proof rules to goals: 
+		\begin{itemize}
+			\item The rewrite rule is applied to a \textbf{Prover state} which has the Action field equal to \texttt{applyConsequence R1 -- S1}, where \texttt{R1} and \texttt{S1} are parameters to be passed to the proof rule
+			\item The Consequence rule is applied at a meta level, using the \texttt{metaXapply} operator [line 11] from the \texttt{META-LEVEL} module.
+To this operator we also pass the values of the parameters (in their meta representation) with which to bind variables appearing in the \texttt{Consequence} rule.
+			\item The result is then checked for errors to see if there were some errors when applying the \texttt{metaXapply} operator [line 8] or if the term returned is not actually of the required type [line 3].
+			\item If the result corresponds to what the prover was expecting, we modify the state by adding the newly generated goals to the \textbf{GoalStack}, by moving down the "meta"-hierarchy - parsing meta-representation of terms.
+			\item The last thing to note is an example of how the rules generate output independent of other applications.
+In the last field of the \textbf{Prover State}, as \textbf{StagingOutput}, there will be a list of quoted identifiers which will eventually get moved to the loop state and then outputted to the user.
+		\end{itemize}
+		All the other actions which control the application of proof rules are written in a similar manner.
 	\item {\(\mathtt{ok}\) action - admits the current goal}
@@
 
+The Maude features we used for this prover's user interface are :
+\begin{itemize}
+	\item The \texttt{format} attribute of operators, which allows the programmer to control the style of the output when a term which makes use of the respective operator is printed to the console.
+It allows specifying modifiers for each possible white space in an operator, modifiers which will remain active until reset or until overriden.
+More information on the \texttt{format} attribute can be found in the Maude Manual \cite{manual}.
+	\item The \texttt{metaPrettyPrint} operator in the \texttt{META-LEVEL} module, which returns a term as a list of quoted identifiers to be printed, formatted respecting the \texttt{format} attributes defined for the operators used in the term.
+An example is presented in Listing \ref{takeFirst}, which presents the rule used to take the top element of the \textbf{GoalStack} for processing, and writes the formatted output of the goal to the \textbf{StagingOutput} field.
+	\begin{lstlisting}[label=takeFirst,caption=Rewrite rule making use of metaPrettyPrint]
+crl [takeFirstGoalFromList] : < noAction ; RG ; noGoal ; G <> GS ; GL ; nil > 
+=> 
+< check ; RG ; G ; GS ; GL ; 'current ' 'goal '  '  'is '\n metaPrettyPrint(upModule('PROVER-INTERFACE, false), upTerm(G)) '\n > 
+if G =/= noGoal .
+	\end{lstlisting}
+\end{itemize}
+All throughout the prover calls to \texttt{metaPrettyPrint} have been made in order to inform the user of what the prover is doing and how.
+\\
+
 For a more advanced user interface or to expose the prover's functionalities through a programming interface, a wrapper written in more feature-rich language through which to control the Maude environment is probably the best choice.

### 2018-06-21 paper/paper_after_guide.tex
added CLI screenshot + minor modifications

@@
 	\item {\textbf{Section 4} will briefly touch upon the theoretical foundations of this project, together with the technologies used to implement them}
-	\item {\textbf{Section 5}, the main section of this paper, will present our approach to solving the problem, discuss shortcomings of the current solution and how it can be improved in the future.
+	\item {\textbf{Section 5}, the main section of this paper, will present our approach to solving the problem, and discuss how it can be improved in the future.
 All the elements of our project will be presented in an individual sub-section}
@@
 An example of operator translation from specification to Maude code is presented in Listing \ref{code:languageGrammer}.
-Note that we have opted to skip the attributes associated with the operators, as they are irrelevant in this case.
+Note that we have opted to skip the attributes associated with the operators, as they are irrelevant for the purpose of this example.
 \\
@@
 More information on the \texttt{format} attribute can be found in the Maude Manual \cite{manual}.
+
+	A sample output of the prover is presented in Figure \ref{fig:CLIScreenShot}, showcasing the manipulation of white spaces (newlines, indentation and spaces), usage of colours to distinguish between different elements - Relations are coloured in green, while the analysed code has it's keyword highlighted using cyan.
+The separator between the two pieces of code is also coloured in red.
+	\begin{figure}[h]
+		\includegraphics[width=\linewidth]{pictures/CLI.png}
+		\caption{Formatted output of the prover}
+		\label{fig:CLIScreenShot}
+	\end{figure}
 	\item The \texttt{metaPrettyPrint} operator in the \texttt{META-LEVEL} module, which returns a term as a list of quoted identifiers to be printed, formatted respecting the \texttt{format} attributes defined for the operators used in the term.

### 2018-06-21 paper/paper.tex
left only with conlcusion to write

@@
 
-The tool is built as a CLI which helps \cite{primer} \cite{SeparationLogic} \cite{JAVAITP} \cite{REWRITING} \cite{maudeprimer} \cite{manual} \cite{rewrConcurrency} \cite{cyclist} argue how two programs are related using Relational Separation Logic specifications.
+The tool is built as a CLI which helps reason how two programs are related using Relational Separation Logic specifications.
 As a consequence of the dependency of Relational Separation Logic on Separation Logic, proofs about single programs using the latter are also supported by the tool.

### 2018-06-21 paper/paper_after_guide.tex
left only with conlcusion to write

@@
 	\item The next phase involves applying the logic proof rules to the goals in the \textbf{GoalStack} to generate sub-goals and prove them.
+Once a goal is popped from the \textbf{GoalStack}, it can be replaced by sub-goals generated by proof rules or, matched with an proven goal / axiom or be admitted manually.
 This phase lasts until there are no more goals left in the \textbf{GoalStack}, meaning that the \textbf{RootGoal} has been proven.
@@
 \end{figure} 
+\paragraph{Goal Graph} One of the improvements which could make the user experience much better for our prover would be the capability to backtrack in the proof and try another approach for the same goal.
+The initial idea for this prover was to have a \textbf{GoalGraph} instead of \textbf{GoalStack} such that when the user applies a rule to a goal, the sub goals are represented as nodes in the same graph, making it possible to trace back the progress to intermediary states.
+This approach would also make the \textbf{ProvenGoals} a lot more useful by increasing the chance of running into an already proven goal and the ability to mark complex goals as proven.
+At the moment, the only goals which can be used from the \textbf{ProvenGoals} are those admitted manually by the user, since the other proven goals already matched axioms.
 \clearpage
@@
 \subsubsection{Automatic matching of axioms and previously proven goals}
+The prover is capable of automatically recognizing goals matching an axiom or a previously proven goals, for a better user experience.
+It achieves this goal by using \texttt{metaXmatch} operator included in the standard \texttt{META-LEVEL} module, which determines if two terms match. 
+\begin{itemize}
+	\item In terms of previously proven goals, the process is straight-forward, as it will compare terms in a literal manner (since they do not contain any variable)
+	\item Axioms are modeled as terms with variables in them, allowing them to be matched with any term for which all variables in the axiom can be bound.
+	For example, the axiom 
+	\[
+		\{E \mapsto -\} [E] := F \{E \mapsto F\}
+	\]
+	will be represented as a term of sort \texttt{HoareTriple}, but with free variables:
+	\begin{lstlisting}
+	{E:AExp |-> - } [E:AExp] := F:AExp {E:AExp |-> F:AExp}\end{lstlisting}
+
+	However, Maude does not allow for variables to appear for the first time on the right hand side of a rewrite rule which needs to be used without meta-level computations (problem present when modeling the Separation Logics as well).
+We had to find a work around for this problem and the solution we came up with was to write the axiom in its meta-representation, and then use the \texttt{downTerm} operator to bring it down in the meta-hierarchy (Listing \ref{axiom})
+
+	\begin{lstlisting}[label=axiom,caption=Initialization of Prover state]
+rl [proveGoal] : < prove(HQ) ; RG ; G ; GS ; GL ; nil > =>
+< noAction ; HQ ; noGoal ; HQ <> emptyGL ; 
+downTerm('`{_`}_`{_`}['_|->_['E:AExp,'_:AExp],'`[_`]:=_['E:AExp,'F:AExp],'_|->_['E:AExp,'F:AExp]] , emptyGL)
+--- ... [other axioms omitted for clarity] 
+; 'begin '\n > .\end{lstlisting}
+\end{itemize}
 \subsubsection{Automatic demonstration of implications}
+Automatic demonstration of implications is one of the most challenging aspects of this paper and this section will present our incipient approach to this problem.
+
+We have modeled implication proof rules as rewrite rules in Maude (example in Listing \ref{implicationProofRule}), in order to make use of its \texttt{metaSearchPath} operator, which will search for a series of rewrites which transform a term into another.
+We used this functionality to try and solve implications
+\[
+	R \Rightarrow S
+\]
+by searching for a series of rewrites from \(R\) to \(S\). 
+\begin{lstlisting}[label=implicationProofRule,caption=Example of implication proof rule]
+rl R * ( S \/ T ) => (R * S) \/ (R * T) .
+\end{lstlisting}
+
+\begin{lstlisting}[label=eqImplicationProving,caption=Equation using the metaSearchPath operator]
+eq tryImplicationProving(RR => TT) = metaSearchPath(upModule('IMPLICATION-PROVER, false), upTerm(RR), upTerm(TT), nil, '* , 5, 0) . 
+\end{lstlisting}
+In it's current form, it cannot offer any guarantee, except for the certainty that if the implication has been proven automatically, the proof is correct given the rewrite rules specified in the \textbf{implication-prover.maude} file.
+The found path is presented to the user if the implication has been proven.
+
+After studying the implications involved in an example, we have found that, in order to properly prove implications, there is a need to implement a sort of symbolic execution at the level of \texttt{Assertions} or \texttt{Relations}.
+The easiest way to explain this idea is by exemplifying:
+\begin{lstlisting}
+{  ( emp /\ c eqs c0 ) * (c0 plus 1)|-> c1  }
+c := [c plus 1]
+{ ( emp /\ c eqs c1 ) * (c0 plus 1)|-> c1 }
+\end{lstlisting}
+The above goal can only be proven by symbolically executing equality between \texttt{c} and \texttt{c0} .
+In the future, this symbolical execution could enable a wider range of implications to be proven automatically.
+In it's current state, an easy way of extending the capabilities of the implication prover is to add more (specific) rewrite rules for it to search through.
+
+\paragraph{Cyclist}\cite{cyclist} \cite{cyclistSite} is an automatic entailment prover for Separation logic which we planned to integrate with our prover for separation logic implications and eventually extend to Relational Separation Logic, since it provides a generic framework.
+Since Maude does not easily support external commands, the idea would be to modify Maude's C++ code and add a hook for the \texttt{[special]} operator attribute which would invoke that hook, which will call the external command for Cyclist.
+We have however focused on other aspects of our prover, and left this feature for the future.
 \subsection{User Interface}
@@
 An example is presented in Listing \ref{takeFirst}, which presents the rule used to take the top element of the \textbf{GoalStack} for processing, and writes the formatted output of the goal to the \textbf{StagingOutput} field.
+	\begin{figure}[h]
 	\begin{lstlisting}[label=takeFirst,caption=Rewrite rule making use of metaPrettyPrint]
@@
 	\end{lstlisting}
+	\end{figure}
 \end{itemize}
@@
 The project also includes a plug-in which allows any Java program to communicate with Maude.
-\subsection{Future directions}
-
 \section{Conclusions}

### 2018-06-22 paper/paper_after_guide.tex
created the cover

@@
 \author{ANDREI-ALIN CORODESCU}
-\title{Program Equivalence : Relational Separation Logic interactive prover implemented in Maude}
+\title{Program Equivalence : A Relational Separation Logic interactive prover implemented in Maude}
 \newcommand{\hq}[4]{
@@
 \textbf{
-"ALEXANDRU IOAN CUZA" UNIVERSITY OF IAȘI
+ALEXANDRU IOAN CUZA UNIVERSITY OF IAȘI
 }
@@
 \begin{center}
-	\Large\textbf {Program Equivalence : Relational Separation Logic interactive prover implemented in Maude}\\
+	\Large\textbf {Program Equivalence: An Interactive Relational Separation Logic Prover Implemented in Maude}\\
 	\vspace{40mm}

### 2018-06-26 paper/paper_after_guide.tex
wrote abstract and conclusion

@@
 }
+
+\newcommand{\stoptocwriting}{%
+	\addtocontents{toc}{\protect\setcounter{tocdepth}{-5}}}
+\newcommand{\resumetocwriting}{%
+	\addtocontents{toc}{\protect\setcounter{tocdepth}{\arabic{tocdepth}}}}
 \usepackage{color}
@@
 \end{titlepage}
+\begin{abstract}
+	Lucrarea de fata descrie procesul de dezvoltare a unui utilitar interactiv utilizat in analiza formala a programelor, folosindu-se de Logica Separatoare Relationala \cite{relational} si Logica Separatoare \cite{primer} \cite{SeparationLogic}, utilizand Maude \cite{maudesite} drept cadru de dezvoltare.
+Componenta interactiva se imbina cu o componenta automatizata, prin care parti din demonstratie vor fi realizate automat.
+Lucrarea este orientata pe rezolvarea problemei prin intermediul functionalitatilor oferite de Maude si va include secvente de cod ce vor ilustra conceptele cheie in modelarea si aplicarea fundamentelor teoretice.
+\end{abstract}
+\pagebreak
 \tableofcontents
 \pagebreak
-
-\section{Introduction}
+\section*{Introduction}
 The present paper describes the development of an interactive tool for reasoning how to programs are related, based on studied and previously used theoretical concepts and technologies which facilitate the implementation.
@@
 \end{itemize}
-
 \section{Contributions}
@@
 For a more advanced user interface or to expose the prover's functionalities through a programming interface, a wrapper written in more feature-rich language through which to control the Maude environment is probably the best choice.
-The concept is exemplified the Maude plug-in for Eclipse, \cite{maudeEclipsePLugin} which enables writing of Maude code inside the Eclipse IDE, and the plug-in communicates with the underlying Maude environment.
+The concept is exemplified by the Maude plug-in for Eclipse, \cite{maudeEclipsePLugin} which enables writing of Maude code inside the Eclipse IDE, and the plug-in communicates with the underlying Maude environment.
 The project also includes a plug-in which allows any Java program to communicate with Maude.
-\section{Conclusions}
+\section*{Conclusions}
+The development of the Relational Separation Logic prover helped us get a deeper understating of it, along with an introduction to other theoretical concepts used in program analysis and programming language semantics, such as Separation Logic and Rewriting Logic.
+\\
+
+While the two Separation Logics used throughout the paper are powerful tools for analyzing the behavior of program and are relatively easy to understand, it takes time to become familiar with them and use the m at their full potential.
+\\
+
+The logics are better suited for studying small snippets of code and not entire programs, because the demonstration can get cumbersome and end up spending a lot of time on focusing on irrelevant parts of the program.
+\\
+
+Maude has been interesting to work because it required an entirely different mindset than the other programming languages I was familiar with .
+Once getting grasping the concepts around Maude which was built, it was easy to come up with simple, clever solutions to the problems I was facing.
+As it is described on it's website \cite{maudesite}, Maude is a powerful logical framework which allows modeling of other logics in it; it proved to be exactly that, enabling us to represent the logics in a natural manner, which made the implementation much less error-prone and allowed us to focus on the relevant part of this project, namely how to apply the logics instead of focusing on how to properly implement them.
+\\
+
+While being a powerful and interesting language to work with, being a fairly specialized and not very widespread, guidance and help are limited to the manual \cite{maudeprimer} and \cite{manual}.
+This obstacle resulted in significant time spent on searching for solutions to otherwise trivial problems, especially when starting using the language, because the source of the problem is usually unclear to a beginner.
+\\
+
+Overall, this whole project has been an interesting introduction to both  theoretical concepts regarding program analysis and new, different technologies.
+The mix of the two resulted in the built prover, which could be improved in the future with the features discussed throughout the chapters and others to easily accommodate real-world usage.
 

### 2018-06-26 paper/paper_after_guide.tex
finished paper content - proof-reading follows

@@
 	\item {\(\mathtt{showGoal}\) action - prints the current goal to the console - it does not modify the state of the prover}
+	\item {\texttt{auto x}} action - instructs the prover to attempt to automatically prove an implication, search for a solution up to a depth of \texttt{x} rewrites
 \end{itemize}
@@
 Since the automation of the prover is part of the future goals of this project, we will also include a few notes on how we might approach problems related to this goal, even though they have not been implemented yet.
+\subsubsection{Variable substitution}
+In both sections describing automated processes we will interpret the equality operator between variables and replace, textually, one variable with the other in \texttt{Assertions}, \texttt{Relations} and \texttt{Commands}.
+The definition of the operator for \texttt{Assertions} is presented in Listing \ref{replaceOp}.
+The operator is defined recursively, with the base case being treated using the \texttt{owise} equational attribute.
+A similar approach is used for all the definitions of this operator.
+\begin{lstlisting}[label=replaceOp,caption=Replace operator definition for assertions]
+op replace : Assertion Id Id -> Assertion .
+eq replace(P * Q, X, Y) = replace(P, X, Y) * replace(Q, X , Y) .
+eq replace(P /\ Q, X, Y) = replace(P, X, Y) /\ replace(Q, X, Y) .
+eq replace(P \/ Q, X, Y) = replace(P, X, Y) \/ replace(Q, X, Y) .
+eq replace(emp, X, Y) = emp .
+eq replace(E |-> E2, X, Y) = replace(E, X, Y) |-> replace(E2, X, Y) .
+eq replace(P, X, Y) = P [owise] .
+\end{lstlisting}
 \subsubsection{Automatic matching of axioms and previously proven goals}
@@
 ; 'begin '\n > .\end{lstlisting}
+	\item For matching we also interpret the equality between variables using the \texttt{replace} operator introduced previously to reduce the \texttt{Goal} to a simpler form, which might match to an axiom.
+	\begin{lstlisting}[caption=Rule intepreting variable equality]
+rl {P * (emp /\ X eqs Y)} X1 := E {Q} =>  
+if X1 =/= X then 
+{replace(P, X, Y)} replace(X1 := E, X, Y) {replace(Q, X, Y)}
+else 
+{replace(P, X, Y)} X1 := replace(E, X, Y) {Q}
+fi .
+	\end{lstlisting}
 \end{itemize}
@@
 \]
-by searching for a series of rewrites from \(R\) to \(S\). 
-\begin{lstlisting}[label=implicationProofRule,caption=Example of implication proof rule]
-rl R * ( S \/ T ) => (R * S) \/ (R * T) .
+by searching for a series of rewrites from \texttt{R => S} to \texttt{true}. 
+\begin{lstlisting}[label=implicationProofRule,caption=Example of implication rewrite rules]
+rl R:Relation * ( S:Relation \/ T:Relation ) => (R:Relation * S:Relation) \/ (R:Relation * T:Relation) .
+--- Example for the usage of the replace operator
+rl R * (Emp /\ X eqs Y) => replace(R, X , Y) .
+rl (R:Relation => R:Relation) => true .
 \end{lstlisting}
@@
 \begin{lstlisting}[label=eqImplicationProving,caption=Equation using the metaSearchPath operator]
-eq tryImplicationProving(RR => TT) = metaSearchPath(upModule('IMPLICATION-PROVER, false), upTerm(RR), upTerm(TT), nil, '* , 5, 0) . 
+op tryImplicationProving : Goal Int -> Trace? .
+eq tryImplicationProving(RR:Relation => TT:Relation, depth:Int) = metaSearchPath(upModule('IMPLICATION-PROVER, false), upTerm(RR:Relation => TT:Relation),upTerm(true), nil, '* , depth:Int, 0) . 
 \end{lstlisting}
-In it's current form, it cannot offer any guarantee, except for the certainty that if the implication has been proven automatically, the proof is correct given the rewrite rules specified in the \textbf{implication-prover.maude} file.
+In it's current form, it cannot offer any guarantee, except for the certainty that if the implication has been proven automatically, the proof is correct in respect to  the rewrite rules specified in the \textbf{implication-prover.maude} file.
+The approach however has an exponential running time since it searches exhaustively throughout the state space for a solution.
+The second parameter is there to control the depth up to which the search goes.
+The prover will try automatically to search a solution within a depth of 3 rewrites, but the user can manually specify searching for a solution using the \texttt{auto x} command, where \texttt{x} is the depth up to which Maude should try to search the solution (our experiments show that searches up to a depth around 12 should finish use a reasonable amount of resources and finish in under 10 minutes - this observation of course depends on the implication and the number of possible rewrites starting from it).
 The found path is presented to the user if the implication has been proven.
-
-After studying the implications involved in an example, we have found that, in order to properly prove implications, there is a need to implement a sort of symbolic execution at the level of \texttt{Assertions} or \texttt{Relations}.
-The easiest way to explain this idea is by exemplifying:
-\begin{lstlisting}
-{  ( emp /\ c eqs c0 ) * (c0 plus 1)|-> c1  }
-c := [c plus 1]
-{ ( emp /\ c eqs c1 ) * (c0 plus 1)|-> c1 }
+\paragraph{Inductive predicates} - the prover currently supports defining inductive predicates only by modifying the underlying Maude code.
+We have defined a single predicate, used in the Relational Separation Logic paper \cite{relational} :
+\begin{lstlisting}[caption=Predicate syntax definition]
+op List : Id -> Relation . 
 \end{lstlisting}
-The above goal can only be proven by symbolically executing equality between \texttt{c} and \texttt{c0} .
-In the future, this symbolical execution could enable a wider range of implications to be proven automatically.
-In it's current state, an easy way of extending the capabilities of the implication prover is to add more (specific) rewrite rules for it to search through.
-
+In terms of the semantics of the \texttt{List} predicate, we have added rules to the \textbf{implication-prover.maude} file, to be considered when rewriting implications.
+\begin{lstlisting}[caption=Example of rule interpreting the List predicate during implication proving]
+rl [ (X:Id |-> E:AExp) * ((X:Id plus 1) |-> Y:Id) ; (X:Id |-> E:AExp) * ((X:Id plus 1) |-> Y:Id) ] * List(Y:Id) => List(X) .
+\end{lstlisting}
 \paragraph{Cyclist}\cite{cyclist} \cite{cyclistSite} is an automatic entailment prover for Separation logic which we planned to integrate with our prover for separation logic implications and eventually extend to Relational Separation Logic, since it provides a generic framework.
@@
 
-\pagebreak
 \bibliographystyle{unsrt}

### 2018-06-26 paper/paper_after_guide.tex
first proof-reading done

@@
 \section*{Introduction}
-The present paper describes the development of an interactive tool for reasoning how to programs are related, based on studied and previously used theoretical concepts and technologies which facilitate the implementation.
+The present paper describes the development of an interactive tool for reasoning how two programs are related, based theoretical concepts from the field of formal program analysis and technologies which facilitate the implementation of those concepts.
 \\
 
-The tool represents an implementation of Hoare Logic - which allows formal reasoning about a program - , along  with 2 of its extensions, namely the Separation Logic (named Separation Logic from now on) and Relational Separation Logic \cite{relational} (named Relational Logic from now on).
-The 2 extensions simplify the Hoare Logic proofs, mainly using the "*" connector, allowing for local reasoning of effects of statements in a program .
+The tool represents an implementation of Hoare Logic - which allows formal reasoning about a program - along  with 2 of its extensions, namely the Separation Logic and Relational Separation Logic \cite{relational}.
+The 2 extensions simplify the Hoare Logic proofs, mainly using the "*" connector, allowing for local reasoning about the effects of statements in a program .
 The tool has been implemented in Maude, a high performance logical framework with powerful metalanguage applications which facilitate the implementations of executable environments for logics.\\
 
-The tool is built as a CLI which helps \cite{primer} \cite{SeparationLogic} \cite{JAVAITP} \cite{REWRITING} \cite{maudeprimer} \cite{manual} \cite{rewrConcurrency} \cite{cyclist} with reasoning how two programs are related using Relational Separation Logic specifications.
+The tool is built as a CLI which helps with reasoning how two programs are related using Relational Separation Logic specifications.
 As a consequence of the dependency of Relational Separation Logic on Separation Logic, proofs about single programs using the latter are also supported by the tool.
@@
 	\item {\textbf{Section 4} will briefly touch upon the theoretical foundations of this project, together with the technologies used to implement them}
-	\item {\textbf{Section 5}, the main section of this paper, will present our approach to solving the problem, and discuss how it can be improved in the future.
-All the elements of our project will be presented in an individual sub-section}
+	\item {\textbf{Section 5}, the main section of this paper, will present our approach to solving the problem, and discuss how it can be improved in the future.}
 \end{itemize}
+\pagebreak
 \section{Contributions}
@@
 	\item Developed an interactive tool for reasoning about program behaviour using the aforementioned logics.
-	\item Automation of some tasks which makes the tool more convenient to use .
-	\item Examples of formal proofs done using the tool
+	\item Automation of tasks, which makes the tool more convenient to use .
+	\item Example of formal proof done using the tool \textbf{need annex}
 \end{itemize}
@@
 A notable example which also uses the same framework as this project, namely Maude, is the Java+ITP\cite{JAVAITP} tool, which enables analysis of Java programs using Separation Logic.
-The implementation relies heavily on Maude's ITP (iterative theorem prover).
+The implementation relies heavily on Maude's ITP (inductive theorem prover).
+\\
+
+Several other tools are presented or referenced in \cite{primer} .
 
@@
 This section will include snippets of Maude code, but since Maude is a very expressive and self-explanatory language, I have not included of thorough presentation of every language construct defined for the scope of this project.
-Ideas presented will be accompanied by some examples and key ideas of the implementation but for a more detailed presentation, please refer to the code itself.
+Ideas presented will be accompanied by some examples and key parts of the implementation but for a more detailed presentation, please refer to the code itself.
+\subsection{Language Grammar and executable semantics}
+The prover supports expressing programs in a simple, imperative language, commonly used throughout papers  \cite{primer} \cite{SeparationLogic} related to the subject of program verification, including the one describing Relational Separation Logic \cite{relational}, around  which this project is based.
+\subsubsection{Storage Model}
+A state of in our storage model is defined by a pair consisting of a \(Store\) and a \(Heap\) .
+\\
+Assuming that all the variables usable in programs from the set \(\mathtt{Vars}\) and the set of positive natural numbers is denoted by \(\mathtt{PosNats}\): \\
+
+A \(Store\) is defined as:
+\[ \mathtt{S} : \mathtt{Vars} \rightarrow \mathtt{PosNats} \]
+
+A \(Heap\) represents a mapping from the \(\mathtt{PosNats}\) to \(\mathtt{Integers}\)
+\[ \mathtt{H} : \mathtt{PosNats} \rightarrow \mathtt{Integers} \] 
+More informally, the \(Store\) holds the value of the variables while the \(Heap\) maps the active memory cells during a program execution to their contents.
+\subsubsection{Syntax and Semantics of the language}
+\begin{figure}[h]
+	\noindent\rule{\linewidth}{0.4pt}
+	\begin{tabularx}{\linewidth}{l  X}
+		Integer Expressions& \(E ::= x \mid Integer \mid E\ \mathtt{plus}\ E \mid E\ \mathtt{times}\ E \mid E\ \mathtt{minus}\ E \) \\
+		\\
+		Boolean Expressions& \(B ::= false \mid true \mid B\ \mathtt{\&\&}\ B \mid  B\ ||\ B \mid B\  \mathtt{->}\ B \mid B \mathtt{<=>} B \mid \ !
+B \mid E\ \mathtt{ge}\ E \mid E\ \mathtt{le}\ E \mid E\ \mathtt{eqs}\ E \)\\
+		\\ 	
+		Commands& \(C ::= x := alloc(E) \mid x := [E] \mid [E] := E \mid free(E) \mid x := E \mid C;C \mid if\ B\ then\ C\ else\ C \mid while\ B\ do\ C\ od \) \\
+	\end{tabularx}
+	\caption{Syntax of the language}
+	\label{fig:langSyntax}
+	\noindent\rule{\linewidth}{0.4pt}
+\end{figure}
+The syntax of the language is presented in Figure \ref{fig:langSyntax} . It represents an adapted subset of the language presented in the Relational Separation Logic paper \cite{relational} . 
+\paragraph{Semantics of the language}
+{
+	The semantics of the previously defined language are standard, but a few clarifications are necessary to point out how our language constructs interact with the storage model, as well as a few differences from regular programming languages:
+	\begin{itemize}
+		\item{Verbosity of operators - most operators are replaced by their literal names ( \(+\) becomes \(\mathtt{plus}\) etc.); we have opted for this approach to avoid complication when implementing the language in Maude, because most of the operators are already defined in Maude for its built-in types, and overloading them could cause conflicts since we are basing our own defined types on Maude's primitives.}
+		\subitem{\( B\ \mathtt{ge}\ B\) translates to the usual \(>=\) operator}
+		\subitem{\( B\ \mathtt{le}\ B\) translates to the usual \(<=\) operator}
+		\subitem{\( B\ \mathtt{eqs}\ B\) translates to the usual \(==\) equality comparison operator}
+		\subitem{\( B\ \mathtt{->}\ B\) denotes implication between boolean expressions}
+		\subitem{\(B\ \mathtt{<=>}\ B\) denotes equivalence between boolean expressions}
+		\subitem{The rest of the operators are mostly similar to their C++ or Java counterparts and their semantics are self explanatory}
+		\item{Memory allocation / deallocation: }
+		\subitem{\(x := alloc(E)\) allocates a new cell in the memory, initializes it with the value of \(E\) and stores its address in the variable \(x\)}
+		\subitem{\(x := free(E)\) deallocates the cell at the address equal to the value of \(E\)}
+		\item{Working with variables and memory: }
+		\subitem{\( x := [E] \) reads the contents of the memory cell at address \(E\) and stores the value in the variable \(x\)}
+		\subitem{\( [E] := E\prime \) updates the contents of the memory cell at address \(E\) with the value of the expression \(E\prime\)}
+		\subitem{\( x := E \) updates the value of the variable \(x\) with the value of the expression \(E\) - note that this command does not modify the heap in any way, as it usually happens with regular programming languages when updating the value of a variable}
+	\end{itemize}
+	\paragraph{Maude Modelling of the language}
+	Maude makes the representation of programming languages grammar a straight forward and natural process, by defining sorts corresponding to language elements and their associated operators.
+The sorts defined in Maude for the grammar are the following :
+	\begin{itemize}
+		\item \texttt{AExp} - abbreviation for Arithmetic Expression - equivalent for Integer expressions in the specification.
+To capture the first two possible forms of Integer expressions in Figure \ref{fig:langSyntax}, the AExp sort is a super sort of \texttt{Int} of \texttt{INT} standard module and \texttt{Id}, which is the sort defined for variables.
+		\item \texttt{BExp} - abbreviation for Boolean Expressions - equivalent for the Boolean Expressions type in the specification. It is a super sort of \texttt{Bool} of standard module \texttt{BOOL}. 
+		\item \texttt{Command} sort maintains the same name as in the specification.
+	\end{itemize}
+	An example of operator translation from specification to Maude code is presented in Listing \ref{code:languageGrammer}.
+Note that we have opted to skip the attributes associated with the operators, as they are irrelevant for the purpose of this example.
+	\\
+
+	\begin{lstlisting}[label=code:languageGrammer,caption=Example of operator translation to Maude code]
+	op while_do_od : BExp Command -> Command [...].
+	op _:=_ : Id AExp -> Command [...]. 
+	\end{lstlisting}
+
+	\paragraph{Executable semantics of the language, in Maude}
+	Maude also supports specifying executable semantics for the language using rewriting logic \cite{rewrConcurrency}.
+A proof of concept for a language similar to the one used by the prover is present in the code of the project, but it is out of scope for the presentation of the prover \textbf{Need reference to the final file name}.
+An executable environment for the programming language used in the prover is a valid candidate for future improvements.
 
@@
 \end{itemize} 
-The proof rules are interpreted in a bottom-up manner, meaning that applying a rule to a goal matching the conclusion of a rule will generate new goals consisting of the hypothesis elements of the rule : Figure \ref{fig:SLTranslation} presents how a Separation Logic rule has been translated into Maude syntax and Figure \ref{fig:RSLTranslation} presents the same process for the Relational Separation Logic counterpart of the rule.
+The proof rules are interpreted in a bottom-up manner, meaning that, applying a rule to a goal, which must match the conclusion of the used rule, will generate new goals consisting of the hypothesis: Figure \ref{fig:SLTranslation} presents how a Separation Logic rule has been translated into Maude syntax and Figure \ref{fig:RSLTranslation} presents the same process for the Relational Separation Logic counterpart of the rule.
 \begin{figure}[h]
@@
 	\item \texttt{HoareQuadruple} is again associated with the concept with the same name, in the Relational Separation Logic context.
+	\begin{figure}[h]
 	\begin{lstlisting}[caption=Examples of Relational Separation Logic specific constructs]
@@
 op {_}_--_{_} : Relation Command Command Relation -> HoareQuadruple .\end{lstlisting}
+	\end{figure}
 \end{itemize}
-The other operators defined for the Assertion and Relation languages have been in the same manner as the programming language operators, following their presentation in \cite{relational}.
-For a full reference, please refer to the code accompanying this paper.
-\subsection{Language Grammar and executable semantics}
-The prover supports expressing programs in a simple, imperative language, commonly used throughout papers \cite{SeparationLogic} \cite{primer} related to the subject of program verification, including the one describing Relational Separation Logic \cite{relational}, around  which this project is based.
-\subsubsection{Storage Model}
-A state of in our storage model is defined by a pair consisting of a \(Store\) and a \(Heap\) .
-\\
-Assuming that all the variables usable in programs from the set \(\mathtt{Vars}\) and the set of positive natural numbers is denoted by \(\mathtt{PosNats}\): \\
+The other operators for the Assertion and Relation languages have been defined in the same manner as the programming language operators, following their presentation in \cite{relational}.
 
-A \(Store\) is defined as:
-\[ \mathtt{S} : \mathtt{Vars} \rightarrow \mathtt{PosNats} \]
-
-A \(Heap\) represents a mapping from the \(\mathtt{PosNats}\) to \(\mathtt{Integers}\)
-\[ \mathtt{H} : \mathtt{PosNats} \rightarrow \mathtt{Integers} \] 
-More informally, the \(Store\) holds the value of the variables while the \(Heap\) maps the active memory cells during a program execution to their contents.
-\subsubsection{Syntax and Semantics of the language}
-\begin{figure}[h]
-	\noindent\rule{\linewidth}{0.4pt}
-	\begin{tabularx}{\linewidth}{l  X}
-		Integer Expressions& \(E ::= x \mid Integer \mid E\ \mathtt{plus}\ E \mid E\ \mathtt{times}\ E \mid E\ \mathtt{minus}\ E \) \\
-		\\
-		Boolean Expressions& \(B ::= false \mid true \mid B\ \mathtt{\&\&}\ B \mid  B\ ||\ B \mid B\  \mathtt{->}\ B \mid B \mathtt{<=>} B \mid \ !
-B \mid E\ \mathtt{ge}\ E \mid E\ \mathtt{le}\ E \mid E\ \mathtt{eqs}\ E \)\\
-		\\ 	
-		Commands& \(C ::= x := alloc(E) \mid x := [E] \mid [E] := E \mid free(E) \mid x := E \mid C;C \mid if\ B\ then\ C\ else\ C \mid while\ B\ do\ C\ od \) \\
-	\end{tabularx}
-	\caption{Syntax of the language}
-	\label{fig:langSyntax}
-	\noindent\rule{\linewidth}{0.4pt}
-\end{figure}
-The syntax of the language is presented in Figure \ref{fig:langSyntax} . It represents an adapted subset of the language presented in the Relational Separation Logic paper \cite{relational} . 
-\paragraph{Semantics of the language}
-{
-	The semantics of the previously defined language are standard but a few clarifications are necessary to point out how our language constructs interact with the storage model, as well as a few differences from regular programming languages:
-	\begin{itemize}
-		\item{Verbosity of operators - most operators are replaced by their literal names ( \(+\) becomes \(\mathtt{plus}\) etc.); we have opted for this approach to avoid complication when implementing the language in Maude, because most of the operators are already defined in Maude for its built-in types, and overloading them could cause conflicts since we are basing our own defined types on Maude's primitives.}
-		\subitem{\( B\ \mathtt{ge}\ B\) translates to the usual \(>=\) operator}
-		\subitem{\( B\ \mathtt{le}\ B\) translates to the usual \(<=\) operator}
-		\subitem{\( B\ \mathtt{eqs}\ B\) translates to the usual \(==\) equality comparison operator}
-		\subitem{\( B\ \mathtt{->}\ B\) denotes implication between boolean expressions}
-		\subitem{\(B\ \mathtt{<=>}\ B\) denotes equivalence between boolean expressions}
-		\subitem{The rest of the operators are mostly similar to their C++ or Java counterparts and their semantics are self explanatory}
-		\item{Memory allocation / deallocation: }
-		\subitem{\(x := alloc(E)\) allocates a new cell in the memory, initializes it with the value of \(E\) and stores its address in the variable \(x\)}
-		\subitem{\(x := free(E)\) deallocates the cell at the address equal to the value of \(E\)}
-		\item{Working with variables and memory: }
-		\subitem{\( x := [E] \) reads the contents of the memory cell at address \(E\) and stores the value in the variable \(x\)}
-		\subitem{\( [E] := E\prime \) updates the contents of the memory cell at address \(E\) with the value of the expression \(E\prime\)}
-		\subitem{\( x := E \) updates the value of the variable \(x\) with the value of the expression \(E\) - note that this command does not modify the heap in any way, as it usually happens with regular programming languages when updating the value of a variable}
-	\end{itemize}
-\paragraph{Maude Modelling of the language}
-Maude makes the representation of programming languages grammar a straight forward and natural process, by defining sorts corresponding to language elements and their associated operators.
-The sorts defined in Maude for the grammar are the following :
-\begin{itemize}
-	\item \texttt{AExp} - abbreviation for Arithmetic Expression - equivalent for Integer expressions in the specification.
-To capture the first two possible forms of Integer expressions in Figure \ref{fig:langSyntax}, the AExp sort is a super sort of \texttt{Int} of \texttt{INT} standard module and \texttt{Id}, which is the sort defined for variables.
-	\item \texttt{BExp} - abbreviation for Boolean Expressions - equivalent for the Boolean Expressions type in the specification. It is a super sort of \texttt{Bool} of standard module \texttt{BOOL}. 
-	\item \texttt{Command} sort maintains the same name as in the specification.
-\end{itemize}
-An example of operator translation from specification to Maude code is presented in Listing \ref{code:languageGrammer}.
-Note that we have opted to skip the attributes associated with the operators, as they are irrelevant for the purpose of this example.
-\\
-
-\begin{lstlisting}[label=code:languageGrammer,caption=Example of operator translation to Maude code]
-	op while_do_od : BExp Command -> Command [...].
-	op _:=_ : Id AExp -> Command [...]. 
-\end{lstlisting}
-
-\paragraph{Executable semantics of the language, in Maude}
-Maude also supports specifying executable semantics for the language using rewriting logic \cite{rewrConcurrency}.
-A proof of concept for a language similar to the one used by the prover is present in the code of the project, but it is out of scope for the presentation of the prover \textbf{Need reference to the final file name}.
-An executable environment for the programming language used in the prover is a valid candidate for future improvements.
 \subsection{Interaction by Maude LOOP-MODE}
-Maude's LOOP-MODE module is the entry point for any interactive Maude application, being the only way to store state between commands.
+Maude's LOOP-MODE module is the entry point for any interactive Maude application, being the only way to store a state between commands.
 In this chapter we will discuss how we handle input and output , the structure of a state and the role every element plays in the execution of the prover.\\
@@
 \subsection{State of the program}
-Following the examples provided together with the Maude Manual \cite{manual}, our state (Figure \ref{fig:ProverState}) is composed multiple sections modified accordingly during program execution .
+Following the examples provided together with the Maude Manual \cite{manual}, our state (Figure \ref{fig:ProverState}) is composed multiple sections modified accordingly during program execution:
 \begin{itemize}
@@
 	\item{\textbf{Staging output} - contains the output generated by the current action, before being passed to the Loop state.
-This staging mechanism enables each action (user or system) to generate output independent of the other actions.}
+This staging mechanism enables each rewriting rule to generate output independent of the others.}
 \end{itemize}
@@
 \subsection{Input and output handling}
-To understand how our prover handles input and output, it is important to note that the flows of the LOOP-MODE module is as follows: 
+To understand how our prover handles input and output, it is important to note that the flow of the LOOP-MODE module is as follows: 
 \begin{enumerate}
@@
 	\item The user issues the command \texttt{loop init .} in the Maude console. This will initialize the loop state.
-	\item Now the user will have to specify the goal it wants to prove, by issuing the command \begin{center}(\texttt{prove} G)\end{center}, where G is the representation of the goal using the syntax defined for our logics.
+	\item Now the user will have to specify the goal it wants to prove, by issuing the command \begin{center}(\texttt{prove(G)})\end{center}, where G is the representation of the goal using the syntax defined for our logics.
 The command will populate the required fields of the prover state (\textbf{RootGoal}, \textbf{GoalStack}) with G.
@@
 	\item The next phase involves applying the logic proof rules to the goals in the \textbf{GoalStack} to generate sub-goals and prove them.
-Once a goal is popped from the \textbf{GoalStack}, it can be replaced by sub-goals generated by proof rules or, matched with an proven goal / axiom or be admitted manually.
+Once a goal is popped from the \textbf{GoalStack}, it can be replaced by sub-goals generated by proof rules, matched with an proven goal / axiom, be proven automatically or be admitted manually.
 This phase lasts until there are no more goals left in the \textbf{GoalStack}, meaning that the \textbf{RootGoal} has been proven.
@@
 		fi 
-	if SubGoals? := metaXapply(upModule('PROVER-INTERFACE, false), upTerm(G), 'Consequence, 'R1:Relation <- upTerm(R1) ; 'S1:Relation <- upTerm(S1) , 0, unbounded, 0).
-		\end{lstlisting}
+	if SubGoals? := metaXapply(upModule('PROVER-INTERFACE, false), upTerm(G), 'Consequence, 'R1:Relation <- upTerm(R1) ; 'S1:Relation <- upTerm(S1) , 0, unbounded, 0).\end{lstlisting}
 		The example given in Listing \ref{userAction} illustrates all the core concepts involved in the application of proof rules to goals: 
 		\begin{itemize}
-			\item The rewrite rule is applied to a \textbf{Prover state} which has the Action field equal to \texttt{applyConsequence R1 -- S1}, where \texttt{R1} and \texttt{S1} are parameters to be passed to the proof rule
+			\item The rewrite rule is applied to a \textbf{Prover state} which has the Action field equal to \texttt{applyConsequence R1 --- S1}, where \texttt{R1} and \texttt{S1} are parameters to be passed to the proof rule
 			\item The Consequence rule is applied at a meta level, using the \texttt{metaXapply} operator [line 11] from the \texttt{META-LEVEL} module.
@@
 	\item {\(\mathtt{showGoal}\) action - prints the current goal to the console - it does not modify the state of the prover}
-	\item {\texttt{auto x}} action - instructs the prover to attempt to automatically prove an implication, search for a solution up to a depth of \texttt{x} rewrites
+	\item {\texttt{auto x}} action - instructs the prover to attempt to automatically prove an implication, by searching for a solution up to a depth of \texttt{x} rewrites.
+This command will do nothing if the current goal is not an implication.
+More details about the automated implication proving are included in the following section
 \end{itemize}
@@
 The system actions are all applied in order before asking for user input.
-After an system action completes execution, it will decide the next action to be placed in the prover state.
-System actions are the main component through which our prover can be enriched with other features in the future, because integrating a new system action is simple.
+After a system action completes execution, it will decide the next action to be placed in the prover state.
+System actions are the main component through which our prover can be enriched with other features in the future.
 At the moment, the system actions are:
@@
 This section will describe the functional parts of the prover which have been automated to make it more user-friendly and even prove sub-goals of the main demonstration by itself.
-Since the automation of the prover is part of the future goals of this project, we will also include a few notes on how we might approach problems related to this goal, even though they have not been implemented yet.
 \subsubsection{Variable substitution}
@@
 	\begin{lstlisting}
-	{E:AExp |-> - } [E:AExp] := F:AExp {E:AExp |-> F:AExp}\end{lstlisting}
+	{E:AExp |-> _ } [E:AExp] := F:AExp {E:AExp |-> F:AExp}\end{lstlisting}
 
@@
 ; 'begin '\n > .\end{lstlisting}
-	\item For matching we also interpret the equality between variables using the \texttt{replace} operator introduced previously to reduce the \texttt{Goal} to a simpler form, which might match to an axiom.
+	\item Before attempting to match terms we also interpret the equality between variables using the \texttt{replace} operator introduced previously to reduce the \texttt{Goal} to a simpler form, which might match to an axiom.
 	\begin{lstlisting}[caption=Rule intepreting variable equality]
@@
 {replace(P, X, Y)} X1 := replace(E, X, Y) {Q}
-fi .
-	\end{lstlisting}
+fi .\end{lstlisting}
 \end{itemize}
@@
 \end{lstlisting}
-In it's current form, it cannot offer any guarantee, except for the certainty that if the implication has been proven automatically, the proof is correct in respect to  the rewrite rules specified in the \textbf{implication-prover.maude} file.
+In it's current form, it cannot offer any guarantee, except for the certainty that if the implication has been proven automatically, the proof is correct with respect to the rewrite rules specified in the \textbf{implication-prover.maude} file.
 The approach however has an exponential running time since it searches exhaustively throughout the state space for a solution.
-The second parameter is there to control the depth up to which the search goes.
+\\
+
+The second parameter controls the depth up to which the search goes.
 The prover will try automatically to search a solution within a depth of 3 rewrites, but the user can manually specify searching for a solution using the \texttt{auto x} command, where \texttt{x} is the depth up to which Maude should try to search the solution (our experiments show that searches up to a depth around 12 should finish use a reasonable amount of resources and finish in under 10 minutes - this observation of course depends on the implication and the number of possible rewrites starting from it).
@@
 \end{lstlisting}
-\paragraph{Cyclist}\cite{cyclist} \cite{cyclistSite} is an automatic entailment prover for Separation logic which we planned to integrate with our prover for separation logic implications and eventually extend to Relational Separation Logic, since it provides a generic framework.
+\paragraph{Cyclist}\cite{cyclist} \cite{cyclistSite} is an automatic entailment prover for Separation Logic which we planned to integrate with our prover for Separation Logic implications and eventually extend to Relational Separation Logic, since it provides a generic framework.
 Since Maude does not easily support external commands, the idea would be to modify Maude's C++ code and add a hook for the \texttt{[special]} operator attribute which would invoke that hook, which will call the external command for Cyclist.
@@
 
-While the two Separation Logics used throughout the paper are powerful tools for analyzing the behavior of program and are relatively easy to understand, it takes time to become familiar with them and use the m at their full potential.
+While the two Separation Logics used throughout the paper are powerful tools for analyzing the behavior of program and are relatively easy to understand, it takes time to become familiar and use them at their full potential.
 \\
 
-The logics are better suited for studying small snippets of code and not entire programs, because the demonstration can get cumbersome and end up spending a lot of time on focusing on irrelevant parts of the program.
+The logics are better suited for studying small snippets of code and not entire programs, because the demonstrations can get cumbersome and end up spending a lot of time on focusing on irrelevant parts of the program instead of its key sections.
 \\
 
-Maude has been interesting to work because it required an entirely different mindset than the other programming languages I was familiar with .
-Once getting grasping the concepts around Maude which was built, it was easy to come up with simple, clever solutions to the problems I was facing.
+Maude has been interesting to work because it required an entirely different mindset than the mainstream programming languages.
+Once grasping the concepts around Maude which was built, it was easy to come up with simple, clever solutions to the problems I was facing.
+\\
 As it is described on it's website \cite{maudesite}, Maude is a powerful logical framework which allows modeling of other logics in it; it proved to be exactly that, enabling us to represent the logics in a natural manner, which made the implementation much less error-prone and allowed us to focus on the relevant part of this project, namely how to apply the logics instead of focusing on how to properly implement them.
@@
 
-While being a powerful and interesting language to work with, being a fairly specialized and not very widespread, guidance and help are limited to the manual \cite{maudeprimer} and \cite{manual}.
+While being a powerful and interesting language to work with, being fairly specialized and not very widespread, guidance and help are limited to the primer \cite{maudeprimer} and the manual \cite{manual}.
 This obstacle resulted in significant time spent on searching for solutions to otherwise trivial problems, especially when starting using the language, because the source of the problem is usually unclear to a beginner.
@@
 Overall, this whole project has been an interesting introduction to both  theoretical concepts regarding program analysis and new, different technologies.
-The mix of the two resulted in the built prover, which could be improved in the future with the features discussed throughout the chapters and others to easily accommodate real-world usage.
+The mix of the two resulted in the built prover, which could be improved in the future with the features discussed throughout the chapters to easily accommodate real-world usage.
 

### 2018-06-26 paper/paper_after_guide.tex
added appendix and one way transformation to the paper

@@
 \usepackage{ebproof}
+\usepackage[toc,page]{appendix}
 \usepackage{listings}
@@
 \usepackage{url}
+\usepackage{afterpage}
+
+\newcommand\blankpage{%
+	\null
+	\thispagestyle{empty}%
+	\addtocounter{page}{-1}%
+	\newpage}
 \author{ANDREI-ALIN CORODESCU}
@@
 \begin{center}
+\afterpage{\blankpage}
 \textbf{
@@
 \end{titlepage}
-\begin{abstract}
-	Lucrarea de fata descrie procesul de dezvoltare a unui utilitar interactiv utilizat in analiza formala a programelor, folosindu-se de Logica Separatoare Relationala \cite{relational} si Logica Separatoare \cite{primer} \cite{SeparationLogic}, utilizand Maude \cite{maudesite} drept cadru de dezvoltare.
-Componenta interactiva se imbina cu o componenta automatizata, prin care parti din demonstratie vor fi realizate automat.
-Lucrarea este orientata pe rezolvarea problemei prin intermediul functionalitatilor oferite de Maude si va include secvente de cod ce vor ilustra conceptele cheie in modelarea si aplicarea fundamentelor teoretice.
-\end{abstract}
-\pagebreak
+
 \tableofcontents
 \pagebreak
+\begin{abstract}
+	Lucrarea de față descrie procesul de dezvoltare a unui utilitar interactiv utilizat în analiza formală a programelor, folosindu-se de Logica Separatoare Relațională \cite{relational} și Logica Separatoare \cite{primer} \cite{SeparationLogic}, utilizând Maude \cite{maudesite} drept cadru de dezvoltare.
+Componenta interactiva se îmbină cu o componentă automatizată, prin care părți din demonstrație vor fi realizate automat.
+Lucrarea este orientata pe rezolvarea problemei prin intermediul funcționalităților oferite de Maude și va include secvențe de cod ce vor ilustra conceptele cheie legate de modelarea si aplicarea fundamentelor teoretice utilizate pe parcursul proiectului.
+\end{abstract}
 \section*{Introduction}
@@
 \end{itemize}
-\pagebreak
 \section{Contributions}
@@
 	\item Automation of tasks, which makes the tool more convenient to use .
-	\item Example of formal proof done using the tool \textbf{need annex}
+	\item Example of formal proof done using the tool - Appendix \ref{proofExample}
 \end{itemize}
@@
 \[ \{P\}\  C\  \{Q\} \]
-where \(P\) denotes the a condition satisfied by state of the program before the execution of the command \(C\) and \(Q\) denotes another condition satisfied by state of the program after the execution of \(C\).
+where \(P\) denotes the a condition satisfied by state of the prover before the execution of the command \(C\) and \(Q\) denotes another condition satisfied by state of the prover after the execution of \(C\).
 \\
@@
 	Maude also supports specifying executable semantics for the language using rewriting logic \cite{rewrConcurrency}.
-A proof of concept for a language similar to the one used by the prover is present in the code of the project, but it is out of scope for the presentation of the prover \textbf{Need reference to the final file name}.
+A proof of concept for a language similar to the one used by the prover is present in the code of the project (\textbf{simpleLanguage.maude}), but it is out of scope for the presentation of the prover .
 An executable environment for the programming language used in the prover is a valid candidate for future improvements.
@@
 \end{figure}
-\subsection{State of the program}
+\subsection{State of the Prover}
 Following the examples provided together with the Maude Manual \cite{manual}, our state (Figure \ref{fig:ProverState}) is composed multiple sections modified accordingly during program execution:
 \begin{itemize}
-	\item{\textbf{Action} - represents the current action to be executed by the prover, more details about supported actions are included in the following sections.}
-	\item{\textbf{Root Goal} - represents the end-goal of this demonstration}
-	\item{\textbf{Current Goal} - the goal being treated currently - all actions will be applied to this goal}
-	\item{\textbf{Goal Stack} - Stack of goals necessary to be proven in order to prove the root goal.
+	\item{\texttt{Action} - represents the current action to be executed by the prover, more details about supported actions are included in the following sections.}
+	\item{\texttt{Root Goal} - represents the end-goal of this demonstration}
+	\item{\texttt{Current Goal} - the goal being treated currently - all actions will be applied to this goal}
+	\item{\texttt{Goal Stack} - Stack of goals necessary to be proven in order to prove the root goal.
 The current goal is the last element popped from the stack and new elements are generated and pushed by the application of proof rules to the current goal.}
-	\item{\textbf{Proven Goals} - List of goals which have been already been proven or axioms.
+	\item{\texttt{Proven Goals} - List of goals which have been already been proven or axioms.
 Each goal will be first checked to see if it matches any goal in this list to prevent repeating the same proofs.}
-	\item{\textbf{Staging output} - contains the output generated by the current action, before being passed to the Loop state.
+	\item{\texttt{Staging Output} - contains the output generated by the current action, before being passed to the Loop state.
 This staging mechanism enables each rewriting rule to generate output independent of the others.}
@@
 In this section we will describe the flow of a demonstration made using our prover.
-The most important parts of the prover's execution are controlled through the first member of a prover state, \textbf{Action}, which specifies the next step in the processing of the current goal.
-There are two types of actions, \textbf{System Actions}, colored in the figure in purple and \textbf{User Actions}, colored in light-yellow.
+The most important parts of the prover's execution are controlled through the first member of a prover state, \texttt{Action}, which specifies the next step in the processing of the current goal.
+There are two types of actions, \texttt{System Actions}, colored in the figure in purple and \texttt{User Actions}, colored in light-yellow.
 The diagram presenting how the prover works is presented in Figure \ref{fig:ProverDiagram}
@@
 	\item Now the user will have to specify the goal it wants to prove, by issuing the command \begin{center}(\texttt{prove(G)})\end{center}, where G is the representation of the goal using the syntax defined for our logics.
-The command will populate the required fields of the prover state (\textbf{RootGoal}, \textbf{GoalStack}) with G.
+The command will populate the required fields of the prover state (\texttt{RootGoal}, \texttt{GoalStack}) with G.
 	\\
 
-	This command will also populate the \textbf{ProvenGoals} list with axioms.
+	This command will also populate the \texttt{ProvenGoals} list with axioms.
 	\\
@@
 The previous command, \texttt{loop init .} was not enclosed because it is a Maude specific command, not something we want to pass as input to our prover.
-	\item The next phase involves applying the logic proof rules to the goals in the \textbf{GoalStack} to generate sub-goals and prove them.
-Once a goal is popped from the \textbf{GoalStack}, it can be replaced by sub-goals generated by proof rules, matched with an proven goal / axiom, be proven automatically or be admitted manually.
-This phase lasts until there are no more goals left in the \textbf{GoalStack}, meaning that the \textbf{RootGoal} has been proven.
+	\item The next phase involves applying the logic proof rules to the goals in the \texttt{GoalStack} to generate sub-goals and prove them.
+Once a goal is popped from the \texttt{GoalStack}, it can be replaced by sub-goals generated by proof rules, matched with an proven goal / axiom, be proven automatically or be admitted manually.
+This phase lasts until there are no more goals left in the \texttt{GoalStack}, meaning that the \texttt{RootGoal} has been proven.
 \end{enumerate}
@@
 \paragraph{Goal Graph} One of the improvements which could make the user experience much better for our prover would be the capability to backtrack in the proof and try another approach for the same goal.
-The initial idea for this prover was to have a \textbf{GoalGraph} instead of \textbf{GoalStack} such that when the user applies a rule to a goal, the sub goals are represented as nodes in the same graph, making it possible to trace back the progress to intermediary states.
-This approach would also make the \textbf{ProvenGoals} a lot more useful by increasing the chance of running into an already proven goal and the ability to mark complex goals as proven.
-At the moment, the only goals which can be used from the \textbf{ProvenGoals} are those admitted manually by the user, since the other proven goals already matched axioms.
+The initial idea for this prover was to have a \texttt{GoalGraph} instead of \texttt{GoalStack} such that when the user applies a rule to a goal, the sub goals are represented as nodes linked to the goal from which they originated, making it possible to trace back the progress to intermediary states.
+This approach would also make the \texttt{ProvenGoals} a lot more useful by increasing the chance of running into an already proven goal and the ability to mark complex goals as proven.
+At the moment, the only goals which can be used from the \texttt{ProvenGoals} are those admitted manually by the user, since the other proven goals already matched axioms.
 \clearpage
@@
 	\begin{center}
-		[\textbf{SL}] + \textbf{apply} + \textit{RuleName}
+		[\texttt{SL}] + \texttt{apply} + \textit{RuleName}
 	\end{center}
-		With \textbf{SL} being added only when applying Separation Logic rules, to distinguish between the Relational Separation Logic rules with the same name.
+		With \texttt{SL} being added only when applying Separation Logic rules, to distinguish between the Relational Separation Logic rules with the same name.
 	}
@@
 			\item The result is then checked for errors to see if there were some errors when applying the \texttt{metaXapply} operator [line 8] or if the term returned is not actually of the required type [line 3].
-			\item If the result corresponds to what the prover was expecting, we modify the state by adding the newly generated goals to the \textbf{GoalStack}, by moving down the "meta"-hierarchy - parsing meta-representation of terms.
+			\item If the result corresponds to what the prover was expecting, we modify the state by adding the newly generated goals to the \texttt{GoalStack}, by moving down the "meta"-hierarchy - parsing meta-representation of terms.
 			\item The last thing to note is an example of how the rules generate output independent of other applications.
-In the last field of the \textbf{Prover State}, as \textbf{StagingOutput}, there will be a list of quoted identifiers which will eventually get moved to the loop state and then outputted to the user.
+In the last field of the \texttt{Prover State}, as \texttt{StagingOutput}, there will be a list of quoted identifiers which will eventually get moved to the loop state and then outputted to the user.
 		\end{itemize}
@@
 	\item Before attempting to match terms we also interpret the equality between variables using the \texttt{replace} operator introduced previously to reduce the \texttt{Goal} to a simpler form, which might match to an axiom.
+	\begin{lstlisting}[caption=Equation reducing the goal before attempting to match it]]
+ceq anyMatches(G, G1 <> GL) = G1
+---if G := G1 .
+if metaXmatch(upModule('PROVER-INTERFACE, false), 
+upTerm(G1),
+--- Try to reduce G as much as possible before matching
+getTerm(metaRewrite(upModule('SYMBOLIC-EXECUTION, false), upTerm(G), unbounded)),
+nil, 0, unbounded, 0) :: MatchPair .
+	\end{lstlisting} 
 	\begin{lstlisting}[caption=Rule intepreting variable equality]
@@
 We have modeled implication proof rules as rewrite rules in Maude (example in Listing \ref{implicationProofRule}), in order to make use of its \texttt{metaSearchPath} operator, which will search for a series of rewrites which transform a term into another.
+\\
 We used this functionality to try and solve implications 
@@
 by searching for a series of rewrites from \texttt{R => S} to \texttt{true}. 
+\\ 
 \begin{lstlisting}[label=implicationProofRule,caption=Example of implication rewrite rules]
@@
 \end{lstlisting}
+Most proof rules are of the form \(R \Leftrightarrow S\) and thus can be naturally expressed in our prover using rewrite rules.
+However, when the proof rules involve just a one way implication, such as \(Emp \Rightarrow Same\), if we were to model it simply as the first rule in the Listing \ref{implicationProofRule}, an implication \texttt{Same => Emp} would be considered true, because Maude would rewrite the \texttt{Emp} to \texttt{Same} and \texttt{Same => Same} evaluates to \texttt{true}.
+To prevent this from happening, we have constrained one-way implications by providing the entire context in which they can be rewritten :
+\begin{lstlisting}
+rl ((R * Emp) => S) => ((R * Same) => S) .
+\end{lstlisting}
+
+We have opted for the approach to search from the term \texttt{R => S} to \texttt{true} instead of searching from \texttt{R} to \texttt{S} because there are implications in which it is beneficial to use information from both sides in order to prove it.
+A simple example would be \texttt{R => true} which should evaluate to \texttt{true} - the rewrite rule corresponding to this implication is used in the proof at Appendix \ref{proofExample} - but if we were to search from \texttt{R} to \texttt{true}, the search will probably fail.
 
@@
 The found path is presented to the user if the implication has been proven.
+\\
+
+In the future, one might consider using Maude internal strategies \cite{manual} to control the rewriting and searching in the implication proving process, to make it follow heuristics and thus be more effective.
+
 \paragraph{Inductive predicates} - the prover currently supports defining inductive predicates only by modifying the underlying Maude code.
@@
 Maude has been interesting to work because it required an entirely different mindset than the mainstream programming languages.
-Once grasping the concepts around Maude which was built, it was easy to come up with simple, clever solutions to the problems I was facing.
+Once grasping the concepts around Maude which was built, it was easy to come up with simple, clever solutions to the encountered problems.
 \\
@@
 
+\begin{appendices}
+	\section{Example of proof using the prover}
+	\label{proofExample}
+	This appendix contains all the necessary commands to be run in a Maude console in order to run an example demonstration using the prover.
+\begin{lstlisting}
+load prover-interface.maude
+loop init .
+(prove(
+{ 
+((
+Same 
+*
+List(c) 
+*
+[ y |-> x0 ; yp |-> x0 ]
+) 
+*
+(y eqs yp /\ Emp))
+*
+(c eqs cp /\ Emp)
+}
+pass ; 
+while (! (c eqs null))
+do 
+x := [y] ; 
+[c] := 0 minus x ;
+c := [c plus 1]
+od
+--
+xp := [yp] ;
+while (! (cp eqs null))
+do 
+[cp] := 0 minus xp ;
+cp := [cp plus 1] 
+od
+{
+(Same
+*
+(y eqs yp /\ Emp))
+* 
+(c eqs cp /\ Emp)
+}
+)
+)
+(applySequencing ( Same * List(c) * [ y |-> x0 ; yp |-> x0 ] * (y eqs yp /\ Emp) * (c eqs cp /\ Emp) * (xp eqs x0 /\ Emp) ) )
+(applyFrameRule (Same * List(c) * (y eqs yp /\ Emp) * (c eqs cp /\ Emp)) )
+(
+applyConsequence
+( [ (y |-> x0) ; (yp |-> x0) ] )
+--
+( [ (y |-> x0) ; ((yp |-> x0) * (xp eqs x0 /\ emp)) ] )
+)
+(applyEmbeddingRule)
+(
+applyConsequence
+( Same * List(c) * (y eqs yp /\ Emp) * (xp eqs x0 /\ Emp) * (c eqs cp /\ Emp) * [y |-> x0 ; yp |-> x0] )
+--
+( (Same * List(c) * (y eqs yp /\ Emp) * (xp eqs x0 /\ Emp) * (c eqs cp /\ Emp) * [y |-> x0 ; yp |-> x0]) /\ !(!(c eqs null)) ) --- R si not B
+)
+(applyLoop)
+(applyConsequence
+([(c0 |-> -) * ((c0 plus 1) |-> c1) * (y |-> x0) * (c eqs c0 /\ emp) 
+; (c0 |-> -) * ((c0 plus 1) |-> c1) * (xp eqs x0 /\ emp ) * (cp eqs c0 /\ emp) ] 
+* List(c1) * Same * (y eqs yp /\ Emp) * [emp ; yp |-> x0])
+--
+([(c0 |-> (0 minus x0)) * ((c0 plus 1) |-> c1) * (y |-> x0) * (c eqs c1 /\ emp) 
+; (c0 |-> (0 minus x0)) * ((c0 plus 1) |-> c1) * (xp eqs x0 /\ emp ) * (cp eqs c1 /\ emp) ]
+* List(c1) * Same * (y eqs yp /\ Emp) * [emp ; yp |-> x0])
+)
+(ok) 
+(applyFrameRule (List(c1) * Same * (y eqs yp /\ Emp) * [emp ; yp |-> x0]))
+(applyEmbeddingRule)
+(SLapplySequencing ((c0 |-> (0 minus x0)) * ((c0 plus 1) |-> c1) * (y |-> x0) * (emp /\ c eqs c0)))
+(SLapplySequencing ((c0 |-> -) * ((c0 plus 1) |-> c1) * (y |-> x0) * (emp /\ c eqs c0) * (emp /\ x eqs x0)))
+(SLapplyFrameRule ((c0 |-> -) * ((c0 plus 1) |-> c1) * (emp /\ c eqs c0)))
+(SLapplyFrameRule ( (y |-> x0) * ((c0 plus 1)|-> c1) ) )
+(SLapplyFrameRule ( (y |-> x0) *  (c0 |->(0 minus x0)) ) )
+(SLapplySequencing ((c0 |-> (0 minus x0)) * ((c0 plus 1) |-> c1) * (xp eqs x0 /\ emp) * (emp /\ cp eqs c0)))
+(SLapplyFrameRule ( (c0 plus 1)|-> c1 ))
+(SLapplyFrameRule  ((emp /\ (xp eqs x0) ) * (c0 |->(0 minus x0))) )
+(ok)
+(auto 9)
+\end{lstlisting}
+\end{appendices}
+
 \end{document}

### 2018-06-27 paper/paper_after_guide.tex
made the prover flow figure be placed relatively ok
second proof-reading done

@@
 \begin{abstract}
-	Lucrarea de față descrie procesul de dezvoltare a unui utilitar interactiv utilizat în analiza formală a programelor, folosindu-se de Logica Separatoare Relațională \cite{relational} și Logica Separatoare \cite{primer} \cite{SeparationLogic}, utilizând Maude \cite{maudesite} drept cadru de dezvoltare.
-Componenta interactiva se îmbină cu o componentă automatizată, prin care părți din demonstrație vor fi realizate automat.
+	Lucrarea de față descrie procesul de dezvoltare al unui utilitar interactiv utilizat în analiza formală a programelor, folosindu-se de Logica Separatoare Relațională \cite{relational} și Logica Separatoare \cite{primer} \cite{SeparationLogic}, utilizând Maude \cite{maudesite} drept cadru de dezvoltare.
+Componenta interactivă se îmbină cu o componentă automatizată, prin care părți din demonstrație vor fi realizate automat.
 Lucrarea este orientata pe rezolvarea problemei prin intermediul funcționalităților oferite de Maude și va include secvențe de cod ce vor ilustra conceptele cheie legate de modelarea si aplicarea fundamentelor teoretice utilizate pe parcursul proiectului.
@@
 
-The tool is built as a CLI which helps with reasoning how two programs are related using Relational Separation Logic specifications.
+The tool is built as a CLI which helps with reasoning about how two programs are related using Relational Separation Logic specifications.
 As a consequence of the dependency of Relational Separation Logic on Separation Logic, proofs about single programs using the latter are also supported by the tool.
@@
 Once such a task is automated in software engineering, it can be included in the flow of any research or development phase of a product.
-An example benefiting from a formal proof of program equivalence is compiler optimization, where the optimized code needs to be equivalent to the input one .
+An example benefiting from a formal proof of program equivalence is compiler optimization, where the optimized code needs to be equivalent to the input one \cite{relational} .
 \\
 
-This project aims to lay the foundations of a tool which facilitates formal reasoning on the way two programs are related with a focus on extensibility and automation of tasks.
+This project aims to lay the foundations of a tool which facilitates formal reasoning about the way two programs are related with a focus on extensibility and automation of tasks.
 
@@
 \section{Relational Separation Logic Interactive Prover} 
-This section will include details related to the implementation and usage of the Relational Separation Logic prover and highlight a few of Maude's features which made it the a language fit for the purpose of this project.
+This section will include details related to the implementation and usage of the Relational Separation Logic prover and highlight a few of Maude's features which made it a language fit for the purpose of this project.
 \\
@@
 Ideas presented will be accompanied by some examples and key parts of the implementation but for a more detailed presentation, please refer to the code itself.
-\subsection{Language Grammar and executable semantics}
+\subsection{Language}
 The prover supports expressing programs in a simple, imperative language, commonly used throughout papers  \cite{primer} \cite{SeparationLogic} related to the subject of program verification, including the one describing Relational Separation Logic \cite{relational}, around  which this project is based.
@@
 	\Hypo{\{P\prime\} C \{Q\prime\}}
-	\Hypo{Q \Rightarrow Q\prime}
+	\Hypo{Q\prime \Rightarrow Q}
 	\Infer 3 {\{P\}\  C  \{Q\}}
@@
 	\Hypo{\hq{R_1}{C}{C\prime}{S_1}}
-	\Hypo{S \Rightarrow S_1}
+	\Hypo{S_1 \Rightarrow S}
 	\Infer 3 {\hq{R}{C}{C\prime}{S}}
@@
 \subsubsection{Sort Hierarchy}
-Much in the same manner as we modeled the language grammar, the Relational Separation Logic \cite{relational} and Separation Logic \cite{SeparationLogic} \cite{primer} have been modeled by defining sorts and declaring operators using these sorts.
-The main point of reference for our modeling has been \cite{relational}, for both logics.
+Much in the same manner as we modelled the language grammar, the Relational Separation Logic \cite{relational} and Separation Logic \cite{SeparationLogic} \cite{primer} have been modeled by defining sorts and declaring operators using these sorts.
+The main point of reference for our modelling has been \cite{relational}, for both logics.
 Some examples of translations from specification to code are included below.
@@
 \end{enumerate}
-\begin{figure}[h]
-	\includegraphics[width=\linewidth]{"pictures/Prover Flow".png}
+\begin{figure}[h!]
+	\includegraphics[width=\textwidth]{"pictures/Prover Flow".png}
 	\caption{Prover Execution Diagram}
@@
 	\item In terms of previously proven goals, the process is straight-forward, as it will compare terms in a literal manner (since they do not contain any variable)
-	\item Axioms are modeled as terms with variables in them, allowing them to be matched with any term for which all variables in the axiom can be bound.
+	\item Axioms are modelled as terms with variables in them, allowing them to be matched with any term for which all variables in the axiom can be bound.
 	For example, the axiom 
@@
 
-	However, Maude does not allow for variables to appear for the first time on the right hand side of a rewrite rule which needs to be used without meta-level computations (problem present when modeling the Separation Logics as well).
+	However, Maude does not allow for variables to appear for the first time on the right hand side of a rewrite rule which needs to be used without meta-level computations (problem present when modelling the Separation Logics as well).
 We had to find a work around for this problem and the solution we came up with was to write the axiom in its meta-representation, and then use the \texttt{downTerm} operator to bring it down in the meta-hierarchy (Listing \ref{axiom})
@@
 
-We have modeled implication proof rules as rewrite rules in Maude (example in Listing \ref{implicationProofRule}), in order to make use of its \texttt{metaSearchPath} operator, which will search for a series of rewrites which transform a term into another.
+We have modelled implication proof rules as rewrite rules in Maude (example in Listing \ref{implicationProofRule}), in order to make use of its \texttt{metaSearchPath} operator, which will search for a series of rewrites which transform a term into another.
 \\
@@
 Most proof rules are of the form \(R \Leftrightarrow S\) and thus can be naturally expressed in our prover using rewrite rules.
-However, when the proof rules involve just a one way implication, such as \(Emp \Rightarrow Same\), if we were to model it simply as the first rule in the Listing \ref{implicationProofRule}, an implication \texttt{Same => Emp} would be considered true, because Maude would rewrite the \texttt{Emp} to \texttt{Same} and \texttt{Same => Same} evaluates to \texttt{true}.
+However, when the proof rules involve just a one way implication, such as \(Emp \Rightarrow Same\), if we were to model it simply as the first rule in the Listing \ref{implicationProofRule}, an implication, \texttt{Same => Emp} for example, could be wrongly considered true, because Maude would rewrite the \texttt{Emp} to \texttt{Same} and \texttt{Same => Same} evaluates to \texttt{true}.
 To prevent this from happening, we have constrained one-way implications by providing the entire context in which they can be rewritten :
@@
 \end{lstlisting}
-In it's current form, it cannot offer any guarantee, except for the certainty that if the implication has been proven automatically, the proof is correct with respect to the rewrite rules specified in the \textbf{implication-prover.maude} file.
+In its current form, the prover does not offer any guarantees, except for the certainty that if the implication has been proven automatically, the proof is correct with respect to the rewrite rules specified in the \textbf{implication-prover.maude} file.
 The approach however has an exponential running time since it searches exhaustively throughout the state space for a solution.
@@
 
+Almost all the implications in Appendix \ref{proofExample} can be automatically proven, the exceptions being the ones for which the running time of the prover is too high, since they require a depth higher than 15 - those are manually admitted using the \texttt{ok} command.
+\\
+
 In the future, one might consider using Maude internal strategies \cite{manual} to control the rewriting and searching in the implication proving process, to make it follow heuristics and thus be more effective.
-
 \paragraph{Inductive predicates} - the prover currently supports defining inductive predicates only by modifying the underlying Maude code.
@@
 The concept is exemplified by the Maude plug-in for Eclipse, \cite{maudeEclipsePLugin} which enables writing of Maude code inside the Eclipse IDE, and the plug-in communicates with the underlying Maude environment.
-The project also includes a plug-in which allows any Java program to communicate with Maude.
+The project also includes a generic plug-in which allows any Java program to communicate with Maude.
 \section*{Conclusions}
@@
 \\
-As it is described on it's website \cite{maudesite}, Maude is a powerful logical framework which allows modeling of other logics in it; it proved to be exactly that, enabling us to represent the logics in a natural manner, which made the implementation much less error-prone and allowed us to focus on the relevant part of this project, namely how to apply the logics instead of focusing on how to properly implement them.
+As it is described on it's website \cite{maudesite}, Maude is a powerful logical framework which allows modelling of other logics in it; it proved to be exactly that, enabling us to represent the logics in a natural manner, which made the implementation much less error-prone and allowed us to focus on the relevant part of this project, namely how to apply the logics instead of focusing on how to properly implement them.
 \\
@@
 Overall, this whole project has been an interesting introduction to both  theoretical concepts regarding program analysis and new, different technologies.
-The mix of the two resulted in the built prover, which could be improved in the future with the features discussed throughout the chapters to easily accommodate real-world usage.
+The mix of the two resulted in the built prover, which could be improved in the future, both from an implementation standpoint (features discussed throughout the chapters) and by refining the theoretical concepts on which it is based (concurrency extensions for logics) to easily accommodate real-world usage.
 
@@
 --
-( (Same * List(c) * (y eqs yp /\ Emp) * (xp eqs x0 /\ Emp) * (c eqs cp /\ Emp) * [y |-> x0 ; yp |-> x0]) /\ !(!(c eqs null)) ) --- R si not B
+( (Same * List(c) * (y eqs yp /\ Emp) * (xp eqs x0 /\ Emp) * (c eqs cp /\ Emp) * [y |-> x0 ; yp |-> x0]) /\ !(!(c eqs null)) )
 )

### 2018-06-30 paper/paper_after_guide.tex
added new figure for states

@@
 \section*{Introduction}
-The present paper describes the development of an interactive tool for reasoning how two programs are related, based theoretical concepts from the field of formal program analysis and technologies which facilitate the implementation of those concepts.
-\\
+In the present paper I describe the development of an interactive tool for reasoning about how two programs are related, in a formal manner. \\
 
-The tool represents an implementation of Hoare Logic - which allows formal reasoning about a program - along  with 2 of its extensions, namely the Separation Logic and Relational Separation Logic \cite{relational}.
-The 2 extensions simplify the Hoare Logic proofs, mainly using the "*" connector, allowing for local reasoning about the effects of statements in a program .
-The tool has been implemented in Maude, a high performance logical framework with powerful metalanguage applications which facilitate the implementations of executable environments for logics.\\
+The tool is an implementation of Hoare Logic, which allows formal reasoning about a program along with two of its extensions, namely the Separation Logic and Relational Separation Logic \cite{relational}.
+The two extensions simplify the Hoare Logic proofs, mainly using the "*" connector, allowing for local reasoning about the effects of statements in a program.
+I have the tool implemented in Maude, a high performance logical framework with powerful metalanguage applications that facilitate the implementation of executable environments for logics.\\
 
-The tool is built as a CLI which helps with reasoning about how two programs are related using Relational Separation Logic specifications.
+The tool is built as a CLI that helps with reasoning about how two programs are related using Relational Separation Logic specifications.
 As a consequence of the dependency of Relational Separation Logic on Separation Logic, proofs about single programs using the latter are also supported by the tool.
@@
 
-The rest of the paper is organized as follows: 
+The paper is organized as follows: 
 \begin{itemize}
-	\item {\textbf{Section 1} will describe the main personal contributions to the realization of this project}
-	\item {\textbf{Section 2} will present the problem this project aims to solve}
-	\item {\textbf{Section 3} will shortly present some other projects related to ours}
-	\item {\textbf{Section 4} will briefly touch upon the theoretical foundations of this project, together with the technologies used to implement them}
-	\item {\textbf{Section 5}, the main section of this paper, will present our approach to solving the problem, and discuss how it can be improved in the future.}
+	\item {\textbf{Section 1} describes the main personal contributions to the realization of this project;}
+	\item {\textbf{Section 2} presents the problem this project aims to solve;}
+	\item {\textbf{Section 3} shortly presents some other projects related to this one;}
+	\item {\textbf{Section 4} briefly touches upon the theoretical foundations of this project, together with the technologies used to implement them;}
+	\item {\textbf{Section 5}, the main section of this paper, presents my approach to solving the problem, and discuss how it can be improved in the future.}
 \end{itemize}
 \section{Contributions}
-Personal contributions to the realization of the project : 
+Personal contributions:
 \begin{itemize}
-	\item Modelled the Relational Logic and Separation Logic using Maude equational and rewriting logic specifications . 
-	\item Developed an interactive tool for reasoning about program behaviour using the aforementioned logics.
-	\item Automation of tasks, which makes the tool more convenient to use .
-	\item Example of formal proof done using the tool - Appendix \ref{proofExample}
+	\item Modelling the Relational Separation Logic and Separation Logic using Maude equational and rewriting logic specifications; 
+	\item Developing an interactive tool for reasoning about program behaviour using the aforementioned logics;
+	\item Automation of tasks that make the tool more convenient to use;
+	\item Example of formal proof performed using the tool - Appendix \ref{proofExample}
 \end{itemize}
-\section{Description of the problem}
-The problem this project is aiming to solve is related to formal reasoning about the execution of code, mainly focusing on how two programs are related to each other (most often the relation to be proven is equivalence)\\
-
-Comparing programs or code fragments and studying their equivalence is part of every software engineer's activities when they are testing an alternative implementation for an existing solution, fixing bugs, launching new product versions, etc .
+Throughout the development of the prover, I have learned how to use a different, unfamiliar technology, that is a good fit for  modelling theoretical concepts which were also new to me.
+This learning by applying process properly introduced me to both the technology and the logics involved in formally verifying program equivalence.
+\section{Description of the Problem}
+Comparing programs or code fragments and studying their equivalence is part of the activities of every software engineer, when they are testing an alternative implementation for an existing solution, fixing bugs, launching new product versions, etc.
 Naturally, for every process completed manually there are efforts being made in order to make it more efficient, less error-prone and, in the end, automate the process all together.
-Once such a task is automated in software engineering, it can be included in the flow of any research or development phase of a product.
-An example benefiting from a formal proof of program equivalence is compiler optimization, where the optimized code needs to be equivalent to the input one \cite{relational} .
+These goals can be achieved by creating an easy to use and reliable formal  method of verifying program equivalence.
 \\
 
-This project aims to lay the foundations of a tool which facilitates formal reasoning about the way two programs are related with a focus on extensibility and automation of tasks.
+An example benefiting from a formal proof of program equivalence is compiler optimization, where the optimized code needs to be equivalent to the input one \cite{relational}.\\
+
+The problem this project aims to solve is reducing the gap between theoretical and practical aspects of formal proofs for program equivalence by creating an executable environment for Relational Separation Logic in which the user can prove the equivalence of programs.
+Through the creation of such a tool, the theoretical concepts become more accessible, easier to apply and understand.
+Making formal verification methods more accessible leads to an overall increase in the quality of software, by replacing the existing methods of verifying equivalence, that are often prone to errors, with more robust ones.\\
+
+The difficult aspects of creating this tool include:
+\begin{itemize}
+	\item Losing as little generality as possible when modelling the theoretical concepts in a programming language;
+	\item Approaching computationally-hard problems required for Relational Separation Logic proofs;
+	\item Understanding the complexities of Relational Separation Logic and create a user experience which facilitate the application of the logic.
+\end{itemize}
 
@@
 
-Several other tools are presented or referenced in \cite{primer} .
+Several other tools are presented or referenced in \cite{primer}.
 
@@
 \subsection{Separation Logic}
-Separation Logic allows for reasoning about the effects of code on the program state in a formal manner. The main abstraction used in separation logic is the \textbf{Hoare Triple}
-\[ \{P\}\  C\  \{Q\} \]
+Separation Logic allows for reasoning about the effects of code on the program state in a formal manner. The main abstraction used in separation logic is the \textbf{Hoare Triple}:
+\[ \{P\}\  C\  \{Q\} ,\]
 where \(P\) denotes the a condition satisfied by state of the prover before the execution of the command \(C\) and \(Q\) denotes another condition satisfied by state of the prover after the execution of \(C\).
@@
 
-Good references for reading on separation logic include : 
+Good references for reading on separation logic include: 
 \begin{itemize}
-	\item \cite{primer} - for a good introduction and some interesting usages
-	\item \cite{SeparationLogic} - for a more in depth explanation, including the mathematical fundaments of the logic
+	\item \cite{primer} - for a good introduction and some interesting usages ;
+	\item \cite{SeparationLogic} - for a more in depth explanation, including the mathematical fundaments of the logic.
 \end{itemize} 
 \subsection{Relational Separation Logic}
-Relational Separation Logic, which is the central concept of our project builds upon the Separation Logic to reason about how to programs are related, by using the concept of a \textbf{Hoare Quadruple}
-\[\{R\}\ {C_1 \atop C_2}\   \{T\}\]
-\(R\) represents a \textbf{relation} between the two program states holding before the execution of commands \(C_1\) and \(C_2\) respectively while \(T\) represents a \textbf{relation} which holds after the execution of the two commands.
+Relational Separation Logic, which is the central concept of our project builds upon Separation Logic to reason about how two programs are related, by using the concept of a \textbf{Hoare Quadruple}:
+\[\{R\}\ {C_1 \atop C_2}\   \{T\},\]
+where \(R\) represents a \textbf{relation} between the two program states holding before the execution of commands \(C_1\) and \(C_2\), while \(T\) represents a \textbf{relation} that holds after the execution of the two commands.
 \\
@@
  \begin{itemize}
- 	\item Maude Primer \cite{primer} which was written for Maude 2.0.1 but still applies to the latest versions of Maude is a good starting point for learning Maude, as it introduces the language in a more informal, friendlier way
- 	\item Maude Manual \cite{manual} which presents the whole Maude system in depth, along with the mathematical foundations
- 	\item All about Maude book \cite{allAboutMaude} which includes everything contained in the manual and presents some of the more relevant tools implemented in Maude .
+ 	\item The Maude Primer \cite{primer}, which was written for Maude 2.0.1 but still applies to the latest versions of Maude is a good starting point for learning Maude, as it introduces the language in a more informal, friendlier way;
+ 	\item The Maude Manual \cite{manual}, which presents the whole Maude system in depth, along with the mathematical foundations;
+ 	\item "All about Maude" book \cite{allAboutMaude}, which includes everything contained in the manual and presents some of the more relevant tools implemented in Maude.
  \end{itemize}
 \section{Relational Separation Logic Interactive Prover} 
-This section will include details related to the implementation and usage of the Relational Separation Logic prover and highlight a few of Maude's features which made it a language fit for the purpose of this project.
+This section includes details related to the implementation and usage of the Relational Separation Logic prover and highlights a few of the features provided by Maude that made it a language fit for the purpose of this project.
 \\
 
-The information presented in this section assumes the reader's familiarity with Maude, especially the META-LEVEL module and with the underlying theoretical concepts implemented by the prover (Separation Logic and Relational Separation Logic).
+The information presented in this section assumes a degree familiarity with Maude, especially the META-LEVEL module, and with the underlying theoretical concepts implemented by the prover (Separation Logic and Relational Separation Logic).
 References for these can be found in the previous section.
@@
 
-This section will include snippets of Maude code, but since Maude is a very expressive and self-explanatory language, I have not included of thorough presentation of every language construct defined for the scope of this project.
-Ideas presented will be accompanied by some examples and key parts of the implementation but for a more detailed presentation, please refer to the code itself.
+This section includes snippets of Maude code, but since Maude is a very expressive and self-explanatory language, I have not included a complete presentation of every language construct defined for the scope of this project.
+The ideas presented are accompanied by some examples and key features of the implementation.
+For a more detailed presentation, please refer to the code itself.
 \subsection{Language}
@@
 \subsubsection{Storage Model}
-A state of in our storage model is defined by a pair consisting of a \(Store\) and a \(Heap\) .
+A state of in our storage model is defined by a pair consisting of a \texttt{Store} and a \texttt{Heap}.
 \\
-Assuming that all the variables usable in programs from the set \(\mathtt{Vars}\) and the set of positive natural numbers is denoted by \(\mathtt{PosNats}\): \\
+The set of program variables is \(\mathtt{Vars}\). The set of positive natural numbers is denoted by \(\mathtt{PosNats}\): 
+\begin{flushleft}
+A \texttt{Store} is defined as:
+\[ \mathtt{S} : \mathtt{Vars} \rightarrow \mathtt{PosNats} .\]
 
-A \(Store\) is defined as:
-\[ \mathtt{S} : \mathtt{Vars} \rightarrow \mathtt{PosNats} \]
-
-A \(Heap\) represents a mapping from the \(\mathtt{PosNats}\) to \(\mathtt{Integers}\)
-\[ \mathtt{H} : \mathtt{PosNats} \rightarrow \mathtt{Integers} \] 
-More informally, the \(Store\) holds the value of the variables while the \(Heap\) maps the active memory cells during a program execution to their contents.
+A \texttt{Heap} represents a mapping from the \(\mathtt{PosNats}\) to \(\mathtt{Integers}\) and is defined as:
+\[ \mathtt{H} : \mathtt{PosNats} \rightarrow \mathtt{Integers} .\] 
+\end{flushleft}
+Informally, the \texttt{Store} holds the value of the variables while the \texttt{Heap} maps the active memory cells during a program execution to their contents.
 \subsubsection{Syntax and Semantics of the language}
@@
 	\begin{tabularx}{\linewidth}{l  X}
-		Integer Expressions& \(E ::= x \mid Integer \mid E\ \mathtt{plus}\ E \mid E\ \mathtt{times}\ E \mid E\ \mathtt{minus}\ E \) \\
+		Integer Expressions& \(E ::= x \mid \textit{Integer} \mid E\ \mathtt{plus}\ E \mid E\ \mathtt{times}\ E \mid E\ \mathtt{minus}\ E \) \\
 		\\
-		Boolean Expressions& \(B ::= false \mid true \mid B\ \mathtt{\&\&}\ B \mid  B\ ||\ B \mid B\  \mathtt{->}\ B \mid B \mathtt{<=>} B \mid \ !
+		Boolean Expressions& \(B ::= \textit{false} \mid \textit{true} \mid B\ \mathtt{\&\&}\ B \mid  B\ ||\ B \mid B\  \texttt{->}\ B \mid B \texttt{<=>} B \mid \ !
 B \mid E\ \mathtt{ge}\ E \mid E\ \mathtt{le}\ E \mid E\ \mathtt{eqs}\ E \)\\
@@
 \end{figure}
-The syntax of the language is presented in Figure \ref{fig:langSyntax} . It represents an adapted subset of the language presented in the Relational Separation Logic paper \cite{relational} . 
-\paragraph{Semantics of the language}
+The syntax of the language is presented in Figure \ref{fig:langSyntax}. It represents a subset of the language presented in the Relational Separation Logic paper \cite{relational}. 
+\paragraph{}
 {
-	The semantics of the previously defined language are standard, but a few clarifications are necessary to point out how our language constructs interact with the storage model, as well as a few differences from regular programming languages:
+	The semantics of the previously are standard, but a few clarifications are necessary to point out how our language constructs interact with the storage model, as well as a few differences from regular programming languages:
 	\begin{itemize}
-		\item{Verbosity of operators - most operators are replaced by their literal names ( \(+\) becomes \(\mathtt{plus}\) etc.); we have opted for this approach to avoid complication when implementing the language in Maude, because most of the operators are already defined in Maude for its built-in types, and overloading them could cause conflicts since we are basing our own defined types on Maude's primitives.}
-		\subitem{\( B\ \mathtt{ge}\ B\) translates to the usual \(>=\) operator}
-		\subitem{\( B\ \mathtt{le}\ B\) translates to the usual \(<=\) operator}
-		\subitem{\( B\ \mathtt{eqs}\ B\) translates to the usual \(==\) equality comparison operator}
-		\subitem{\( B\ \mathtt{->}\ B\) denotes implication between boolean expressions}
-		\subitem{\(B\ \mathtt{<=>}\ B\) denotes equivalence between boolean expressions}
-		\subitem{The rest of the operators are mostly similar to their C++ or Java counterparts and their semantics are self explanatory}
+		\item{Verbosity of operators - most operators are replaced by their literal names (\(+\) becomes \(\mathtt{plus}\) etc.).
+I have opted for this approach to avoid syntactic complication when implementing the language in Maude, because most of the operators are already defined in Maude for its built-in types, and overloading them could cause conflicts since we are basing our own defined types on Maude's primitives.}
+		\subitem{\( B\ \mathtt{ge}\ B\) translates to the usual \(\geq\) operator}
+		\subitem{\( B\ \mathtt{le}\ B\) translates to the usual \(\leq\) operator}
+		\subitem{\( B\ \mathtt{eqs}\ B\) translates to the usual \(=\) equality comparison operator}
+		\subitem{\( B\ \texttt{->}\ B\) denotes implication between boolean expressions}
+		\subitem{\(B\ \texttt{<=>}\ B\) denotes equivalence between boolean expressions}
+		\subitem{The rest of the operators are self-explanatory}
 		\item{Memory allocation / deallocation: }
-		\subitem{\(x := alloc(E)\) allocates a new cell in the memory, initializes it with the value of \(E\) and stores its address in the variable \(x\)}
-		\subitem{\(x := free(E)\) deallocates the cell at the address equal to the value of \(E\)}
+		\subitem{\(x := alloc(E)\) allocates a new memory cells, initializes it with the value of \(E\) and stores its address in the variable \(x\);}
+		\subitem{\(free(E)\) deallocates the cell at the address equal to the value of \(E\).}
 		\item{Working with variables and memory: }
-		\subitem{\( x := [E] \) reads the contents of the memory cell at address \(E\) and stores the value in the variable \(x\)}
-		\subitem{\( [E] := E\prime \) updates the contents of the memory cell at address \(E\) with the value of the expression \(E\prime\)}
-		\subitem{\( x := E \) updates the value of the variable \(x\) with the value of the expression \(E\) - note that this command does not modify the heap in any way, as it usually happens with regular programming languages when updating the value of a variable}
+		\subitem{\( x := [E] \) reads the contents of the memory cell at address \(E\) and stores the value in the variable \(x\);}
+		\subitem{\( [E] := E\prime \) updates the contents of the memory cell at address \(E\) with the value of the expression \(E\prime\);}
+		\subitem{\( x := E \) updates the value of the variable \(x\) with the value of the expression \(E\).
+Note that this command does not modify the heap in any way, as it usually happens with regular programming languages when updating the value of a variable.}
 	\end{itemize}
-	\paragraph{Maude Modelling of the language}
-	Maude makes the representation of programming languages grammar a straight forward and natural process, by defining sorts corresponding to language elements and their associated operators.
-The sorts defined in Maude for the grammar are the following :
+	\paragraph{Maude Modelling of the Language}
+	We define sorts corresponding to language elements and their associated operators:
 	\begin{itemize}
-		\item \texttt{AExp} - abbreviation for Arithmetic Expression - equivalent for Integer expressions in the specification.
-To capture the first two possible forms of Integer expressions in Figure \ref{fig:langSyntax}, the AExp sort is a super sort of \texttt{Int} of \texttt{INT} standard module and \texttt{Id}, which is the sort defined for variables.
-		\item \texttt{BExp} - abbreviation for Boolean Expressions - equivalent for the Boolean Expressions type in the specification. It is a super sort of \texttt{Bool} of standard module \texttt{BOOL}. 
-		\item \texttt{Command} sort maintains the same name as in the specification.
+		\item \texttt{AExp} for Integer expressions in the specification.
+To capture the first two possible forms of Integer expressions in Figure \ref{fig:langSyntax}, the AExp sort is a super sort of \texttt{Int} in the standard \texttt{INT} module and \texttt{Id}, which is the sort defined for variables;
+		\item \texttt{BExp} for the Boolean Expressions type in the specification. It is a super sort of \texttt{Bool} of standard module \texttt{BOOL}; 
+		\item \texttt{Command} for programs.
 	\end{itemize}
-	An example of operator translation from specification to Maude code is presented in Listing \ref{code:languageGrammer}.
+	An example of a translation from specification to Maude code is presented in Listing \ref{code:languageGrammer}.
 Note that we have opted to skip the attributes associated with the operators, as they are irrelevant for the purpose of this example.
@@
 	Maude also supports specifying executable semantics for the language using rewriting logic \cite{rewrConcurrency}.
-A proof of concept for a language similar to the one used by the prover is present in the code of the project (\textbf{simpleLanguage.maude}), but it is out of scope for the presentation of the prover .
+A proof of concept for a language similar to the one used by the prover is present in the code of the project (\textbf{simpleLanguage.maude}), but it is out of scope for the presentation of the prover.
 An executable environment for the programming language used in the prover is a valid candidate for future improvements.
@@
 \subsection{Modelling the Separation Logics}
-Thanks to Maude's ability to naturally represent logics, the modelling of the Separation Logic and Relational Separation Logic is mostly reduced to translating the logical formulae into appropriate syntax for Maude, making the representational distance (the amount of information lost when representing a theoretical concept into a programming language)\cite{manual} almost non existent.
+Thanks to the ability of Maude to naturally represent logics, the modelling of Separation Logic and Relational Separation Logic is mostly reduced to translating the logical formulae into appropriate syntax for Maude, making the representational distance (the amount of information lost when representing a theoretical concept into a programming language) \cite{manual} almost non existent.
 \\
@@
 Each proof rule in the Separation Logic and Relational Separation Logic has been translated into a Maude rewrite rule.
-\\
 The prover is centered around the concept of \textbf{Goals} which can be one of the three things:
 \begin{itemize}
-	\item {Hoare Quadruple} - corresponding to Relational Separation Logic
-	\item {Hoare Triple} - corresponding to Separation Logic
-	\item {Implication between relations / assertions} 
+	\item {Hoare Quadruple} - corresponding to Relational Separation Logic;
+	\item {Hoare Triple} - corresponding to Separation Logic;
+	\item {Implication between relations and assertions}.
 \end{itemize} 
-The proof rules are interpreted in a bottom-up manner, meaning that, applying a rule to a goal, which must match the conclusion of the used rule, will generate new goals consisting of the hypothesis: Figure \ref{fig:SLTranslation} presents how a Separation Logic rule has been translated into Maude syntax and Figure \ref{fig:RSLTranslation} presents the same process for the Relational Separation Logic counterpart of the rule.
-\begin{figure}[h]
-	Consequence Rule
+The proof rules are interpreted in a bottom-up manner, meaning that, applying a rule to a goal, which must match the conclusion of the used rule, will generate new goals consisting of the hypothesis: Listing \ref{slConseq} presents how a Separation Logic rule has been translated into Maude syntax and Listing \ref{rslConseq} presents the same process for the Relational Separation Logic counterpart of the rule.
+\begin{flushleft}
+	The Separation Logic rule of \textsf{Consequence}
+\end{flushleft}
 	\medskip
@@
 	\]
-	Is represented in Maude syntax as : 
-\begin{lstlisting}[caption=Separation Logic Consequence rule]
+	Is represented in Maude syntax as: 
+\begin{lstlisting}[caption=Separation Logic Consequence rule,label=slConseq]
 	rl [SeparationLogic-Consequence] : {P} C {Q} => ((P => P1) <> ({P1} C {Q1})) <> (Q1 => Q) [nonexec] .
 \end{lstlisting}
-	\caption{Example of a translation to Maude syntax of a Separation Logic proof rule}
-	\label{fig:SLTranslation}
-\end{figure}
-
-\begin{figure}[h]
-	Consequence Rule
+\begin{flushleft}
+	The Relational Separation Logic rule of \textsf{Consequence}
+\end{flushleft}
 	\[
@@
 	\]
-	Is represented in Maude syntax as : 
-	\begin{lstlisting}[caption=Relational Separation Logic Consequence rule]
+	is represented in Maude syntax as: 
+	\begin{lstlisting}[caption=Relational Separation Logic Consequence rule,label=rslConseq]
 	rl [Consequence] : { R } C1 -- C2  { S } => ((R => R1) <> ({R1} C1 -- C2 {S1})) <> (S1 => S) [nonexec] .
 	\end{lstlisting}
-	\caption{Example of a translation to Maude syntax of a Relational Separation Logic proof rule}
-	\label{fig:RSLTranslation}
-\end{figure}
 The \texttt{<>} operator is used to separate sub-goals generated by the rule.
@@
 
-All the rules are marked with the attribute \texttt{[nonexec]} because we want them to be applied in a controlled manner, at the meta-level.
-Some of the rules, the examples included, are not even valid executable Maude rules, because they make use of variables before binding them (for example \texttt{P1} is used in a rule before it is bound).
-At the meta-level however we can manually bind values to those variables, as we will exemplify when discussing how we apply these rules to goals.
+All the rules are given the attribute \texttt{[nonexec]} because we want them to be applied in a controlled manner, at the meta-level.
+Some of the rules, including the examples, are not even valid executable Maude rules, because they make use of variables before binding them For example, in the Separation Logic rule of \textsf{Consequence}, \texttt{P1} is used in a rule before it is bound.
+At the meta-level, however we can manually bind values to those variables, as we will show when discussing how we apply these rules to goals.
 \subsubsection{Sort Hierarchy}
-Much in the same manner as we modelled the language grammar, the Relational Separation Logic \cite{relational} and Separation Logic \cite{SeparationLogic} \cite{primer} have been modeled by defining sorts and declaring operators using these sorts.
+Much in the same manner as we modelled the language grammar, Relational Separation Logic and Separation Logic have been modelled by defining sorts and declaring operators using these sorts.
 The main point of reference for our modelling has been \cite{relational}, for both logics.
@@
 \begin{itemize}
-	\item \texttt{Assertion} is the sort used to handle Separation Logic assertions. It is a super sort of the \texttt{BExp} sort defined as part of our language.
-	\item \texttt{HoareTriple} is the sort associated with the concept with the same name, in a Separation Logic context.
-	\begin{lstlisting}[caption=Hoare Triple constructor operator]
+	\item \texttt{Assertion} is the sort used to handle Separation Logic assertions. It is a super sort of the \texttt{BExp} sort defined as part of our language;
+	\item \texttt{HoareTriple} is the sort for Separation Logic \textbf{Hoare Triples} (Listing \ref{HT}):
+	\begin{lstlisting}[caption=Hoare Triple constructor operator,label=HT]
 op {_}_{_} : Assertion Command Assertion -> HoareTriple .\end{lstlisting}
-	\item \texttt{Relation} is the sort associated with Relational Separation Logic relations.
-As it was the case with \texttt{Assertion}, it is a super sort of the \texttt{BExp} sort of our language grammar.
+	\item \texttt{Relation} is the sort for Relational Separation Logic relations.
+As with \texttt{Assertion}, it is a super sort of the \texttt{BExp} sort of our language.
 Because both the \texttt{Relation} and \texttt{Assertion} are super sorts of the same sort, Maude will display a few warnings which are not affecting functionality, but in the future, creating a separate \texttt{BExp} sort for both the \texttt{Assertion} and \texttt{Relation} sorts would be a better option.
-	\item \texttt{HoareQuadruple} is again associated with the concept with the same name, in the Relational Separation Logic context.
+	\item \texttt{HoareQuadruple} denotes the concept with the same name, in the context of Relational Separation Logic .\\
+	Listing \ref{HQ} language constructs relevant for Relational Separation Logic.
 	\begin{figure}[h]
-	\begin{lstlisting}[caption=Examples of Relational Separation Logic specific constructs]
+	\begin{lstlisting}[caption=Examples of Relational Separation Logic specific constructs,label=HQ]
 --- Operator which creates a relation from two assertions
@@
 \subsection{Interaction by Maude LOOP-MODE}
-Maude's LOOP-MODE module is the entry point for any interactive Maude application, being the only way to store a state between commands.
-In this chapter we will discuss how we handle input and output , the structure of a state and the role every element plays in the execution of the prover.\\
+Our Relational Separation Logic prover is implemented as an interactive CLI program, based on the LOOP-MODE module of Maude, which is the entry point for any interactive Maude application.
+The LOOP-MODE module provides the only way to store a state between commands.
+In this chapter we will discuss how we handle input and output, the structure of a state and the role every element plays in the execution of the prover.\\
 
-We will make a distinction between \textbf{Loop state}, which specific to Maude's LOOP-MODE module and the \textbf{Prover state} which is specific to our use-case, and holds the necessary data related to the state of the proof we are currently working on.
-The \textbf{Prover state} is encapsulated within \textbf{Loop state}.
+We will make a distinction between \textbf{Loop state}, which is specific to Maude and the \textbf{Prover state}, which is specific to our use-case, and holds the necessary data related to the state of the proof we are currently working on.
+The \textbf{Prover state} is encapsulated within \textbf{Loop state} (see Figure \ref{fig:states}).
 \begin{figure}[h]
-	\noindent\rule{\linewidth}{0.4pt}
-
-	\[
-		[\mathtt{INPUT},\ \mathtt{PROVER-STATE},\ \mathtt{OUPTUT}]
-	\]
-	\label{fig:loopState}
-	\caption{Loop state}
-	\noindent\rule{\linewidth}{0.4pt}
+	\includegraphics[width=\textwidth]{"pictures/States".png}
+	\caption{Loop and Prover State structure}
+	\label{fig:states}
 \end{figure}
 \subsection{State of the Prover}
-Following the examples provided together with the Maude Manual \cite{manual}, our state (Figure \ref{fig:ProverState}) is composed multiple sections modified accordingly during program execution:
+Following the examples in the Maude Manual \cite{manual}, our prover state (Figure \ref{fig:states}) is composed of multiple sections modified accordingly during the execution of the prover:
 \begin{itemize}
-	\item{\texttt{Action} - represents the current action to be executed by the prover, more details about supported actions are included in the following sections.}
-	\item{\texttt{Root Goal} - represents the end-goal of this demonstration}
-	\item{\texttt{Current Goal} - the goal being treated currently - all actions will be applied to this goal}
-	\item{\texttt{Goal Stack} - Stack of goals necessary to be proven in order to prove the root goal.
-The current goal is the last element popped from the stack and new elements are generated and pushed by the application of proof rules to the current goal.}
-	\item{\texttt{Proven Goals} - List of goals which have been already been proven or axioms.
-Each goal will be first checked to see if it matches any goal in this list to prevent repeating the same proofs.}
+	\item{\texttt{Action} - represents the current action to be executed by the prover;}
+	\item{\texttt{Root Goal} - represents the end-goal of the proof;}
+	\item{\texttt{Current Goal} - the goal being treated currently - all actions will be applied to this goal;}
+	\item{\texttt{Goal Stack} - stack of goals necessary to be proven in order to prove the root goal.
+The current goal is the last element popped from the stack and new elements are generated and pushed by the application of proof rules to the current goal;}
+	\item{\texttt{Proven Goals} - list of goals that have already been proven, or axioms. Each goal will be first checked to see if it matches any goal in this list to prevent repeating the same proofs;}
 	\item{\texttt{Staging Output} - contains the output generated by the current action, before being passed to the Loop state.
@@
 \end{itemize}
-\begin{figure}[h]
-	\noindent\rule{\linewidth}{0.4pt}
-	\(
-	< \mathtt{Action}, \mathtt{Root Goal}, \mathtt{Current Goal}, \mathtt{Goal Stack}, \mathtt{Proven Goals}, \mathtt{Staging Output} >
-	\)
-	\caption{Prover State}
-	\label{fig:ProverState}
-	\noindent\rule{\linewidth}{0.4pt}
-\end{figure}
-\subsection{Input and output handling}
+\subsection{Input and Output Handling}
 To understand how our prover handles input and output, it is important to note that the flow of the LOOP-MODE module is as follows: 
 \begin{enumerate}
-	\item User input is placed in the \(\mathtt{INPUT}\) member of the loop state
-	\item Maude engine applies all the rewritings possible, resulting in a new loop state.
-
-	This is the step where all the logic of the prover goes into, in the form of rewriting rules which modify the prover state.
-	\item The member \(\mathtt{OUTPUT}\) of this new loop state is taken and displayed at the console.
+	\item User input is placed in the \(\mathtt{INPUT}\) member of the loop state;
+	\item Maude engine applies all the possible rewritings, resulting in a new loop state. All the logic of the prover is implemented here, in the form of rewriting rules which modify the prover state;
+	\item The member \(\mathtt{OUTPUT}\) of the new loop state is taken and displayed at the console.
 \end{enumerate}
-There are two main rules used for handling input and output : 
+There are two main rules used for handling input and output: 
 \begin{enumerate}
-	\item{\texttt{in} rule, which is responsible for parsing the user input and modifying the action in the prover state accordingly}
-	\begin{lstlisting}[caption=in rule]
+	\item{The \texttt{in} rule (Listing \ref{inRule}), which is responsible for parsing user input and modifying the action in the prover state accordingly;}
+	\begin{lstlisting}[caption=The \texttt{in} rule,label=inRule]
 crl [in] : 
@@
 \end{lstlisting}
-	\item{\texttt{out} rule, which takes the staging output from the prover state and appends it to the currently existing output in the loop state}
-	\begin{lstlisting}[caption=out rule]
+	\item{The \texttt{out} rule (Listing \ref{outRule}), which takes the staging output from the prover state and appends it to the currently existing output in the loop state.}
+	\begin{lstlisting}[caption=The \texttt{out} rule,label=outRule]
 crl [out] :
@@
 
-\subsection{Prover execution flow}
-In this section we will describe the flow of a demonstration made using our prover.
-The most important parts of the prover's execution are controlled through the first member of a prover state, \texttt{Action}, which specifies the next step in the processing of the current goal.
+\subsection{Prover Execution Flow}
+This section describes the flow of a Relational Separation Logic proof using our prover.
+The most important parts of the execution of the prover are controlled through the first member of a prover state, \texttt{Action}, which specifies the next step in the processing of the current goal.
 There are two types of actions, \texttt{System Actions}, colored in the figure in purple and \texttt{User Actions}, colored in light-yellow.
-The diagram presenting how the prover works is presented in Figure \ref{fig:ProverDiagram}
+The diagram showing how the prover works is presented in Figure \ref{fig:ProverDiagram}.
 \\
 \begin{enumerate}
-	\item The user issues the command \texttt{loop init .} in the Maude console. This will initialize the loop state.
-	\item Now the user will have to specify the goal it wants to prove, by issuing the command \begin{center}(\texttt{prove(G)})\end{center}, where G is the representation of the goal using the syntax defined for our logics.
+	\item The user issues the command \texttt{loop init .} in the Maude console. This will initialize the loop state;
+	\item Now the user will have to specify the goal it wants to prove, by issuing the command \begin{center}(\texttt{prove(G)}),\end{center} where G is the representation of the goal using the syntax defined for our logics.
 The command will populate the required fields of the prover state (\texttt{RootGoal}, \texttt{GoalStack}) with G.
@@
 
-	Please note that the command is enclosed within parentheses, this being a requirement of Maude LOOP-MODE \cite{manual}.
+	Please note that the command is enclosed within parentheses, this being a requirement of the  Maude LOOP-MODE \cite{manual}.
 All the prover specific commands need to be enclosed in parenthesis.
-The previous command, \texttt{loop init .} was not enclosed because it is a Maude specific command, not something we want to pass as input to our prover.
+The previous command, \texttt{loop init .} was not enclosed because it is a Maude specific command, not something we want to pass as input to our prover;
 	\item The next phase involves applying the logic proof rules to the goals in the \texttt{GoalStack} to generate sub-goals and prove them.
@@
 \end{figure} 
-\paragraph{Goal Graph} One of the improvements which could make the user experience much better for our prover would be the capability to backtrack in the proof and try another approach for the same goal.
-The initial idea for this prover was to have a \texttt{GoalGraph} instead of \texttt{GoalStack} such that when the user applies a rule to a goal, the sub goals are represented as nodes linked to the goal from which they originated, making it possible to trace back the progress to intermediary states.
-This approach would also make the \texttt{ProvenGoals} a lot more useful by increasing the chance of running into an already proven goal and the ability to mark complex goals as proven.
-At the moment, the only goals which can be used from the \texttt{ProvenGoals} are those admitted manually by the user, since the other proven goals already matched axioms.
 \clearpage
@@
 	\item {Rule application action - indicates the application of a specific rule to the current goal, the action can be parametrized or not, depending on the rule.
-These actions are named following the pattern :
+These actions are named following the pattern:
 	\begin{center}
-		[\texttt{SL}] + \texttt{apply} + \textit{RuleName}
+		[\texttt{SL}] + \texttt{apply} + \textit{RuleName},
 	\end{center}
-		With \texttt{SL} being added only when applying Separation Logic rules, to distinguish between the Relational Separation Logic rules with the same name.
+		with \texttt{SL} being added only when applying Separation Logic rules, to distinguish between the Relational Separation Logic rules with the same name.
 	}
@@
 		\begin{itemize}
-			\item The rewrite rule is applied to a \textbf{Prover state} which has the Action field equal to \texttt{applyConsequence R1 --- S1}, where \texttt{R1} and \texttt{S1} are parameters to be passed to the proof rule
+			\item The rewrite rule is applied to a \textbf{Prover state} that has the Action field equal to \texttt{applyConsequence R1 --- S1}, where \texttt{R1} and \texttt{S1} are parameters to be passed to the proof rule;
 			\item The Consequence rule is applied at a meta level, using the \texttt{metaXapply} operator [line 11] from the \texttt{META-LEVEL} module.
-To this operator we also pass the values of the parameters (in their meta representation) with which to bind variables appearing in the \texttt{Consequence} rule.
-			\item The result is then checked for errors to see if there were some errors when applying the \texttt{metaXapply} operator [line 8] or if the term returned is not actually of the required type [line 3].
-			\item If the result corresponds to what the prover was expecting, we modify the state by adding the newly generated goals to the \texttt{GoalStack}, by moving down the "meta"-hierarchy - parsing meta-representation of terms.
+To this operator we also pass the values of the parameters (in their meta representation) with which to bind variables appearing in the \texttt{Consequence} rule;
+			\item The result is then checked for errors to see if there were some errors when applying the \texttt{metaXapply} operator (line 8) or if the term returned is not actually of the required type (line 3);
+			\item If the result corresponds to what the prover was expecting, we modify the state by adding the newly generated goals to the \texttt{GoalStack}, by moving down the meta-hierarchy - parsing meta-representation of terms;
 			\item The last thing to note is an example of how the rules generate output independent of other applications.
@@
 		\end{itemize}
-		All the other actions which control the application of proof rules are written in a similar manner.
-	\item {\(\mathtt{ok}\) action - admits the current goal}
-	\item {\(\mathtt{showGoal}\) action - prints the current goal to the console - it does not modify the state of the prover}
+		All other actions which control the application of proof rules are written in a similar manner;
+	\item {\(\mathtt{ok}\) action - admits the current goal;}
+	\item {\(\mathtt{showGoal}\) action - prints the current goal to the console - it does not modify the state of the prover.}
 	\item {\texttt{auto x}} action - instructs the prover to attempt to automatically prove an implication, by searching for a solution up to a depth of \texttt{x} rewrites.
@@
 \subsubsection{System Actions}
-System actions were implemented to mimic the behaviour of a "chain of responsibility" design pattern from object-oriented programming.
+System actions mimic the behaviour of a "chain of responsibility" design pattern from object-oriented programming.
 The system actions are all applied in order before asking for user input.
@@
 \begin{itemize}
-	\item {\texttt{check}} - marks the current goal to be checked against previously proven goals or axioms
-	\item {\texttt{implication}} - marks the current goal to be run through the implication prover - in case the goal is an implication, try to prove it automatically
-	\item {\texttt{stop}} - when there are no more sub-goals to be proven, the prover should stop and indicate the success of proving the root goal
+	\item {\texttt{check}} - marks the current goal to be checked against previously proven goals or axioms;
+	\item {\texttt{implication}} - marks the current goal to be run through the implication prover - in case the goal is an implication, try to prove it automatically;
+	\item {\texttt{stop}} - when there are no more sub-goals to be proven, the prover should stop and indicate the success of proving the root goal.
 \end{itemize}
-\subsection{Automated processes}
-This section will describe the functional parts of the prover which have been automated to make it more user-friendly and even prove sub-goals of the main demonstration by itself.
+\subsection{Automated Parts of the Relational Separation Logic Prover}
+This section describes the functional parts of the prover which have been automated to make it more user-friendly and even prove sub-goals of the main demonstration by itself.
 \subsubsection{Variable substitution}
@@
 \end{lstlisting}
-\subsubsection{Automatic matching of axioms and previously proven goals}
+\subsubsection{Automatic Recognition of Axioms and Previously Proven Goals}
 The prover is capable of automatically recognizing goals matching an axiom or a previously proven goals, for a better user experience.
 It achieves this goal by using \texttt{metaXmatch} operator included in the standard \texttt{META-LEVEL} module, which determines if two terms match.
-\begin{itemize}
-	\item In terms of previously proven goals, the process is straight-forward, as it will compare terms in a literal manner (since they do not contain any variable)
-	\item Axioms are modelled as terms with variables in them, allowing them to be matched with any term for which all variables in the axiom can be bound.
+
+In terms of previously proven goals, the process is straight-forward, as it will compare terms in a literal manner (since they do not contain any variable).
+\\
+
+Axioms are modelled as terms with variables in them, allowing them to be matched by any term for which all variables in the axiom can be bound.
 	For example, the axiom 
 	\[
-		\{E \mapsto -\} [E] := F \{E \mapsto F\}
+		\{E \mapsto -\} [E] := F \{E \mapsto F\}.
 	\]
-	will be represented as a term of sort \texttt{HoareTriple}, but with free variables:
-	\begin{lstlisting}
+	is represented as a term of sort \texttt{HoareTriple}, but with free variables (Listing \ref{axiomRepr}):
+	\begin{lstlisting}[caption=Example Axiom,label=axiomRepr]
 	{E:AExp |-> _ } [E:AExp] := F:AExp {E:AExp |-> F:AExp}\end{lstlisting}
 
-	However, Maude does not allow for variables to appear for the first time on the right hand side of a rewrite rule which needs to be used without meta-level computations (problem present when modelling the Separation Logics as well).
-We had to find a work around for this problem and the solution we came up with was to write the axiom in its meta-representation, and then use the \texttt{downTerm} operator to bring it down in the meta-hierarchy (Listing \ref{axiom})
+	However, Maude does not allow for variables to appear for the first time on the right hand side of a rewrite rule which needs to be used without meta-level computations (problem present when modelling the Separation Logic as well).
+We had to find a workaround for this problem and the solution we came up with was to write the axiom in its meta-representation, and then use the \texttt{downTerm} operator to bring it down in the meta-hierarchy (Listing \ref{axiom}).
 
@@
 ; 'begin '\n > .\end{lstlisting}
-	\item Before attempting to match terms we also interpret the equality between variables using the \texttt{replace} operator introduced previously to reduce the \texttt{Goal} to a simpler form, which might match to an axiom.
-	\begin{lstlisting}[caption=Equation reducing the goal before attempting to match it]]
+Before attempting to match terms we also interpret the equality between variables using the \texttt{replace} operator (Listing \ref{replaceSymb}) introduced previously to reduce the \texttt{Goal} to a simpler form, which might match to an axiom (Listing \ref{rewriteBeforeMatch}).
+	\begin{lstlisting}[caption=Equation reducing the goal before attempting to match it,label=rewriteBeforeMatch]
 ceq anyMatches(G, G1 <> GL) = G1
@@
 	\end{lstlisting} 
-	\begin{lstlisting}[caption=Rule intepreting variable equality]
+	\begin{lstlisting}[caption=Rule intepreting variable equality,label=replaceSymb]
 rl {P * (emp /\ X eqs Y)} X1 := E {Q} =>  
@@
 fi .\end{lstlisting}
-\end{itemize}
-\subsubsection{Automatic demonstration of implications}
-Automatic demonstration of implications is one of the most challenging aspects of this paper and this section will present our incipient approach to this problem.
+
+\subsubsection{Automatic Proof of Implications}
+\label{autoImpl}
+Automatic proof of implications is one of the most challenging aspects of this paper and this section will present our incipient approach to this problem.
 
@@
 However, when the proof rules involve just a one way implication, such as \(Emp \Rightarrow Same\), if we were to model it simply as the first rule in the Listing \ref{implicationProofRule}, an implication, \texttt{Same => Emp} for example, could be wrongly considered true, because Maude would rewrite the \texttt{Emp} to \texttt{Same} and \texttt{Same => Same} evaluates to \texttt{true}.
-To prevent this from happening, we have constrained one-way implications by providing the entire context in which they can be rewritten :
+To prevent this from happening, we have constrained one-way implications by providing the entire context in which they can be rewritten:
 \begin{lstlisting}
@@
 
-We have opted for the approach to search from the term \texttt{R => S} to \texttt{true} instead of searching from \texttt{R} to \texttt{S} because there are implications in which it is beneficial to use information from both sides in order to prove it.
+We have opted for the approach to search from the term \texttt{R => S} to \texttt{true} (Listing \ref{eqImplicationProving}) instead of searching from \texttt{R} to \texttt{S} because there are implications in which it is beneficial to use information from both sides in order to prove it.
 A simple example would be \texttt{R => true} which should evaluate to \texttt{true} - the rewrite rule corresponding to this implication is used in the proof at Appendix \ref{proofExample} - but if we were to search from \texttt{R} to \texttt{true}, the search will probably fail.
@@
 \end{lstlisting}
-In its current form, the prover does not offer any guarantees, except for the certainty that if the implication has been proven automatically, the proof is correct with respect to the rewrite rules specified in the \textbf{implication-prover.maude} file.
+If the implication has been proven automatically, the proof is correct with respect to the rewrite rules specified in the \textbf{implication-prover.maude} file.
 The approach however has an exponential running time since it searches exhaustively throughout the state space for a solution.
@@
 In the future, one might consider using Maude internal strategies \cite{manual} to control the rewriting and searching in the implication proving process, to make it follow heuristics and thus be more effective.
-\paragraph{Inductive predicates} - the prover currently supports defining inductive predicates only by modifying the underlying Maude code.
+\paragraph{Inductive predicates} - the prover currently supports defining inductive predicates only by modifying the underlying Maude code (Listing \ref{indPred}).
 We have defined a single predicate, used in the Relational Separation Logic paper \cite{relational} :
-\begin{lstlisting}[caption=Predicate syntax definition]
+\begin{lstlisting}[caption=Predicate syntax definition,label=indPred]
 op List : Id -> Relation . 
 \end{lstlisting}
-In terms of the semantics of the \texttt{List} predicate, we have added rules to the \textbf{implication-prover.maude} file, to be considered when rewriting implications.
-\begin{lstlisting}[caption=Example of rule interpreting the List predicate during implication proving]
+In terms of the semantics of the \texttt{List} predicate, we have added rules to the \textbf{implication-prover.maude} file, to be considered when rewriting implications (Listing \ref{indPredSem}).
+\begin{lstlisting}[caption=Example of rule interpreting the List predicate during implication proving,label=indPredSem]
 rl [ (X:Id |-> E:AExp) * ((X:Id plus 1) |-> Y:Id) ; (X:Id |-> E:AExp) * ((X:Id plus 1) |-> Y:Id) ] * List(Y:Id) => List(X) .
 \end{lstlisting}
-\paragraph{Cyclist}\cite{cyclist} \cite{cyclistSite} is an automatic entailment prover for Separation Logic which we planned to integrate with our prover for Separation Logic implications and eventually extend to Relational Separation Logic, since it provides a generic framework.
+\paragraph{Cyclist}\cite{cyclist} \cite{cyclistSite} is an automatic entailment prover for Separation Logic which we plan to integrate with our prover for Separation Logic implications and eventually extend to Relational Separation Logic, since it provides a generic framework.
 Since Maude does not easily support external commands, the idea would be to modify Maude's C++ code and add a hook for the \texttt{[special]} operator attribute which would invoke that hook, which will call the external command for Cyclist.
-We have however focused on other aspects of our prover, and left this feature for the future.
 \subsection{User Interface}
-Since our project aims to simplify the demonstrations of Separation Logic / Relational Separation Logic formulae, using an interactive prover, the user interface plays a major role in the success of the project - the easier it is to use and understand, the more chances of success it has.
+Since our project aims to enable proofs of Separation Logic / Relational Separation Logic formulae, using an interactive prover, the user interface plays a major role in the success of the project - the easier it is to use and understand, the more chances of success it has.
 This idea has been presented in \cite{primer}, when discussing key elements of tools related to program verification.
@@
 
-Maude provides a simple, yet powerful system for controlling the output formatting of the CLI through which we aim to make the demonstrations more readable and user-friendly. \\
+Maude provides a simple, yet powerful system for controlling the output formatting of the CLI through which we aim to make the proofs more readable and user-friendly. \\
 
-The Maude features we used for this prover's user interface are :
+The Maude features we used for this prover's user interface are:
 \begin{itemize}
-	\item The \texttt{format} attribute of operators, which allows the programmer to control the style of the output when a term which makes use of the respective operator is printed to the console.
-It allows specifying modifiers for each possible white space in an operator, modifiers which will remain active until reset or until overriden.
+	\item The \texttt{format} attribute of operators, which allows the programmer to control the style of the output when a term that makes use of the respective operator is printed to the console.
+It allows specifying modifiers for each possible white space in an operator, modifiers that will remain active until reset or until overriden.
 More information on the \texttt{format} attribute can be found in the Maude Manual \cite{manual}.
@@
 	A sample output of the prover is presented in Figure \ref{fig:CLIScreenShot}, showcasing the manipulation of white spaces (newlines, indentation and spaces), usage of colours to distinguish between different elements - Relations are coloured in green, while the analysed code has it's keyword highlighted using cyan.
-The separator between the two pieces of code is also coloured in red.
+The separator between the two pieces of code is also coloured in red;
 	\begin{figure}[h]
@@
 
-For a more advanced user interface or to expose the prover's functionalities through a programming interface, a wrapper written in more feature-rich language through which to control the Maude environment is probably the best choice.
-The concept is exemplified by the Maude plug-in for Eclipse, \cite{maudeEclipsePLugin} which enables writing of Maude code inside the Eclipse IDE, and the plug-in communicates with the underlying Maude environment.
+For a more advanced user interface or to expose the  functionalities of the prover through a programming interface, a wrapper written in more feature-rich language through which to control the Maude environment is probably the best choice.
+The concept is exemplified by the Maude plug-in for Eclipse (see \cite{maudeEclipsePLugin}) which enables writing of Maude code inside the Eclipse IDE, and the plug-in communicates with the underlying Maude environment.
 The project also includes a generic plug-in which allows any Java program to communicate with Maude.
-\section*{Conclusions}
+\section*{Conclusions and Future Work}
 The development of the Relational Separation Logic prover helped us get a deeper understating of it, along with an introduction to other theoretical concepts used in program analysis and programming language semantics, such as Separation Logic and Rewriting Logic.
@@
 Overall, this whole project has been an interesting introduction to both  theoretical concepts regarding program analysis and new, different technologies. 
-The mix of the two resulted in the built prover, which could be improved in the future, both from an implementation standpoint (features discussed throughout the chapters) and by refining the theoretical concepts on which it is based (concurrency extensions for logics) to easily accommodate real-world usage.
+\\
+
+Future directions of developing this project include support for concurrent programs and reducing the amount of required user input by automation.
+Immediate improvements which can be implemented for the prover include:
+\begin{itemize}
+	\item The ability to trace back the progress of a proof, and retry from intermediary states.
+This can be achieved by replacing the \textbf{GoalStack} with a directed graph structure in which nodes are \textbf{Goals} and arcs represent dependencies between the \textbf{Goals}.
+	\item Implement a symbolic execution system for relations and assertions in order to be able to handle more complex proofs.
+The foundations of such a system are present in the current implementation, which interprets the equality between variables.
+For example, arithmetic expressions are a valid candidate for this system: in the current implementation, the expression \texttt{x plus (1 plus 2) } is different from the \texttt{x plus 3}.
+	\item Improvements to the automatic proof of implications, with two of the options discussed in the Subsection \ref{autoImpl}
+\end{itemize}
 

### 2018-06-30 paper/paper_after_guide.tex
proof-read the paper after modifications

@@
 \begin{abstract}
-	Lucrarea de față descrie procesul de dezvoltare al unui utilitar interactiv utilizat în analiza formală a programelor, folosindu-se de Logica Separatoare Relațională \cite{relational} și Logica Separatoare \cite{primer} \cite{SeparationLogic}, utilizând Maude \cite{maudesite} drept cadru de dezvoltare.
-Componenta interactivă se îmbină cu o componentă automatizată, prin care părți din demonstrație vor fi realizate automat.
-Lucrarea este orientata pe rezolvarea problemei prin intermediul funcționalităților oferite de Maude și va include secvențe de cod ce vor ilustra conceptele cheie legate de modelarea si aplicarea fundamentelor teoretice utilizate pe parcursul proiectului.
+	Lucrarea de față descrie procesul de dezvoltare al unui utilitar interactiv utilizat în analiza formală a echivalenței programelor, folosindu-se de Logica Separatoare Relațională \cite{relational} și Logica Separatoare \cite{primer} \cite{SeparationLogic}, utilizând Maude \cite{maudesite} drept cadru de dezvoltare.
+Componenta interactivă se îmbină cu o componentă automatizată, prin care, părți din demonstrație vor fi realizate automat.
+Lucrarea este orientată pe rezolvarea problemei prin intermediul funcționalităților oferite de Maude și va include secvențe de cod ce vor ilustra conceptele cheie legate de modelarea și aplicarea fundamentelor teoretice utilizate pe parcursul proiectului.
 \end{abstract}
@@
 
-The tool is an implementation of Hoare Logic, which allows formal reasoning about a program along with two of its extensions, namely the Separation Logic and Relational Separation Logic \cite{relational}.
+The tool is an implementation of Hoare Logic, which allows formal reasoning about a program, along with two of its extensions, namely the Separation Logic and Relational Separation Logic \cite{relational}.
 The two extensions simplify the Hoare Logic proofs, mainly using the "*" connector, allowing for local reasoning about the effects of statements in a program.
-I have the tool implemented in Maude, a high performance logical framework with powerful metalanguage applications that facilitate the implementation of executable environments for logics.\\
+I have implemented the tool in Maude, a high performance logical framework with powerful metalanguage applications that facilitate the implementation of executable environments for logics.\\
 
@@
 \section{Contributions}
-Personal contributions:
+Personal contributions to:
 \begin{itemize}
@@
 \end{itemize}
-Throughout the development of the prover, I have learned how to use a different, unfamiliar technology, that is a good fit for  modelling theoretical concepts which were also new to me.
+Throughout the development of the prover, I have learned how to use a different, unfamiliar technology, that is a good fit for  modelling theoretical concepts, which were also new to me.
 This learning by applying process properly introduced me to both the technology and the logics involved in formally verifying program equivalence.
@@
 
-The problem this project aims to solve is reducing the gap between theoretical and practical aspects of formal proofs for program equivalence by creating an executable environment for Relational Separation Logic in which the user can prove the equivalence of programs.
+The problem this project aims to solve is reducing the gap between theoretical and practical aspects of formal proofs for program equivalence, by creating an executable environment for Relational Separation Logic in which the user can prove the equivalence of programs.
 Through the creation of such a tool, the theoretical concepts become more accessible, easier to apply and understand.
@@
 \begin{itemize}
-	\item Losing as little generality as possible when modelling the theoretical concepts in a programming language;
+	\item Modelling the theoretical concepts in a programming language;
 	\item Approaching computationally-hard problems required for Relational Separation Logic proofs;
-	\item Understanding the complexities of Relational Separation Logic and create a user experience which facilitate the application of the logic.
+	\item Understanding the complexities of Relational Separation Logic and creating an user experience that facilitates the application of the logic.
 \end{itemize}
@@
 \begin{itemize}
-	\item \cite{primer} - for a good introduction and some interesting usages ;
+	\item \cite{primer} - for a good introduction and some interesting usages;
 	\item \cite{SeparationLogic} - for a more in depth explanation, including the mathematical fundaments of the logic.
@@
 \paragraph{}
-{
-	The semantics of the previously are standard, but a few clarifications are necessary to point out how our language constructs interact with the storage model, as well as a few differences from regular programming languages:
+	The semantics of the operators are standard, but a few clarifications are necessary to point out how our language constructs interact with the storage model, as well as a few differences from regular programming languages:
 	\begin{itemize}
 		\item{Verbosity of operators - most operators are replaced by their literal names (\(+\) becomes \(\mathtt{plus}\) etc.).
-I have opted for this approach to avoid syntactic complication when implementing the language in Maude, because most of the operators are already defined in Maude for its built-in types, and overloading them could cause conflicts since we are basing our own defined types on Maude's primitives.}
+I have opted for this approach to avoid syntactic complication when implementing the language in Maude, because most of the operators are already defined in Maude for its built-in types, and overloading them could cause conflicts since we are basing our own defined types on the primitives of Maude.}
 		\subitem{\( B\ \mathtt{ge}\ B\) translates to the usual \(\geq\) operator}
@@
 		\subitem{\(B\ \texttt{<=>}\ B\) denotes equivalence between boolean expressions}
-		\subitem{The rest of the operators are self-explanatory}
+		\subitem{The rest of the operators are self-explanatory.}
 		\item{Memory allocation / deallocation: }
@@
 	\end{itemize}
-	\paragraph{Maude Modelling of the Language}
+	\paragraph{Maude Modelling of the Language:}
 	We define sorts corresponding to language elements and their associated operators:
@@
 \begin{flushleft}
-	The Separation Logic rule of \textsf{Consequence}
+	The Separation Logic rule of \textsf{Consequence}:
 \end{flushleft}
@@
 \begin{flushleft}
-	The Relational Separation Logic rule of \textsf{Consequence}
+	The Relational Separation Logic rule of \textsf{Consequence}:
 \end{flushleft}
@@
 \\
-
 The \texttt{---} operator is used to separate the two snippets of code mentioned in the \textbf{Hoare Quadruple}.
@@
 As with \texttt{Assertion}, it is a super sort of the \texttt{BExp} sort of our language.
-Because both the \texttt{Relation} and \texttt{Assertion} are super sorts of the same sort, Maude will display a few warnings which are not affecting functionality, but in the future, creating a separate \texttt{BExp} sort for both the \texttt{Assertion} and \texttt{Relation} sorts would be a better option.
+Because both the \texttt{Relation} and \texttt{Assertion} are super sorts of the same sort, Maude will display a few warnings which are not affecting functionality, but in the future, creating a separate \texttt{BExp} sort for both the \texttt{Assertion} and \texttt{Relation} sorts would be a better option;
 	\item \texttt{HoareQuadruple} denotes the concept with the same name, in the context of Relational Separation Logic .\\
-	Listing \ref{HQ} language constructs relevant for Relational Separation Logic.
+	Listing \ref{HQ} presents language constructs relevant for Relational Separation Logic.
 	\begin{figure}[h]
@@
 
-We will make a distinction between \textbf{Loop state}, which is specific to Maude and the \textbf{Prover state}, which is specific to our use-case, and holds the necessary data related to the state of the proof we are currently working on.
+We will make a distinction between \textbf{Loop state}, which is specific to Maude, and the \textbf{Prover state}, which is specific to our use-case, and holds the necessary data related to the state of the proof we are currently working on.
 The \textbf{Prover state} is encapsulated within \textbf{Loop state} (see Figure \ref{fig:states}).
@@
 The current goal is the last element popped from the stack and new elements are generated and pushed by the application of proof rules to the current goal;}
-	\item{\texttt{Proven Goals} - list of goals that have already been proven, or axioms. Each goal will be first checked to see if it matches any goal in this list to prevent repeating the same proofs;}
+	\item{\texttt{Proven Goals} - list of goals that have already been proven, or axioms. Each goal will first be checked to see if it matches any goal in this list to prevent repeating the same proofs;}
 	\item{\texttt{Staging Output} - contains the output generated by the current action, before being passed to the Loop state.
@@
 	\item User input is placed in the \(\mathtt{INPUT}\) member of the loop state;
-	\item Maude engine applies all the possible rewritings, resulting in a new loop state. All the logic of the prover is implemented here, in the form of rewriting rules which modify the prover state;
-	\item The member \(\mathtt{OUTPUT}\) of the new loop state is taken and displayed at the console.
+	\item Maude applies all the possible rewritings, resulting in a new loop state. All the logic of the prover is implemented here, in the form of rewriting rules which modify the prover state;
+	\item The \(\mathtt{OUTPUT}\) member of the loop state is taken and displayed at the console.
 \end{enumerate}
@@
 The most important parts of the execution of the prover are controlled through the first member of a prover state, \texttt{Action}, which specifies the next step in the processing of the current goal.
-There are two types of actions, \texttt{System Actions}, colored in the figure in purple and \texttt{User Actions}, colored in light-yellow.
+There are two types of actions: \texttt{System Actions} and \texttt{User Actions}.
 The diagram showing how the prover works is presented in Figure \ref{fig:ProverDiagram}.
@@
 			\item The rewrite rule is applied to a \textbf{Prover state} that has the Action field equal to \texttt{applyConsequence R1 --- S1}, where \texttt{R1} and \texttt{S1} are parameters to be passed to the proof rule;
-			\item The Consequence rule is applied at a meta level, using the \texttt{metaXapply} operator [line 11] from the \texttt{META-LEVEL} module.
+			\item The Consequence rule is applied at the meta level, using the \texttt{metaXapply} operator (line 11) from the \texttt{META-LEVEL} module.
 To this operator we also pass the values of the parameters (in their meta representation) with which to bind variables appearing in the \texttt{Consequence} rule;
-			\item The result is then checked for errors to see if there were some errors when applying the \texttt{metaXapply} operator (line 8) or if the term returned is not actually of the required type (line 3);
+			\item The result is then checked for errors to see if the \texttt{metaXapply} operator has not been applied correctly (line 8), or if the term returned is not actually of the required type (line 3);
 			\item If the result corresponds to what the prover was expecting, we modify the state by adding the newly generated goals to the \texttt{GoalStack}, by moving down the meta-hierarchy - parsing meta-representation of terms;
-			\item The last thing to note is an example of how the rules generate output independent of other applications.
+			\item The last thing to note is an example of how the rules generate output independently of others.
 In the last field of the \texttt{Prover State}, as \texttt{StagingOutput}, there will be a list of quoted identifiers which will eventually get moved to the loop state and then outputted to the user.
@@
 This section describes the functional parts of the prover which have been automated to make it more user-friendly and even prove sub-goals of the main demonstration by itself.
-\subsubsection{Variable substitution}
+\subsubsection{Variable Substitution}
 In both sections describing automated processes we will interpret the equality operator between variables and replace, textually, one variable with the other in \texttt{Assertions}, \texttt{Relations} and \texttt{Commands}.
@@
 
-	However, Maude does not allow for variables to appear for the first time on the right hand side of a rewrite rule which needs to be used without meta-level computations (problem present when modelling the Separation Logic as well).
+	However, Maude does not allow for variables to appear for the first time on the right hand side of a rewrite rule which needs to be used without meta-level computations (problem present when modelling Separation Logic as well).
 We had to find a workaround for this problem and the solution we came up with was to write the axiom in its meta-representation, and then use the \texttt{downTerm} operator to bring it down in the meta-hierarchy (Listing \ref{axiom}).
@@
 ; 'begin '\n > .\end{lstlisting}
-Before attempting to match terms we also interpret the equality between variables using the \texttt{replace} operator (Listing \ref{replaceSymb}) introduced previously to reduce the \texttt{Goal} to a simpler form, which might match to an axiom (Listing \ref{rewriteBeforeMatch}).
+Before attempting to match terms we also interpret the equality between variables using the \texttt{replace} operator (Listing \ref{replaceSymb}) introduced previously, to reduce the \texttt{Goal} to a simpler form, which might match to an axiom (Listing \ref{rewriteBeforeMatch}).
 	\begin{lstlisting}[caption=Equation reducing the goal before attempting to match it,label=rewriteBeforeMatch]
@@
 \label{autoImpl}
-Automatic proof of implications is one of the most challenging aspects of this paper and this section will present our incipient approach to this problem.
+Automatic proof of implications is one of the most challenging aspects of this project and this section will present our incipient approach to this problem.
 
@@
 
-The second parameter controls the depth up to which the search goes.
+The second parameter in Listing \ref{eqImplicationProving} - line 1, controls the depth up to which the search goes.
 The prover will try automatically to search a solution within a depth of 3 rewrites, but the user can manually specify searching for a solution using the \texttt{auto x} command, where \texttt{x} is the depth up to which Maude should try to search the solution (our experiments show that searches up to a depth around 12 should finish use a reasonable amount of resources and finish in under 10 minutes - this observation of course depends on the implication and the number of possible rewrites starting from it).
@@
 
-Almost all the implications in Appendix \ref{proofExample} can be automatically proven, the exceptions being the ones for which the running time of the prover is too high, since they require a depth higher than 15 - those are manually admitted using the \texttt{ok} command.
+Almost all the implications in Appendix \ref{proofExample} can be automatically proven, the exceptions being the ones for which the compute resources required by the prover are too high, since they require a depth higher than 15 - those are manually admitted using the \texttt{ok} command.
 \\
@@
 \subsection{User Interface}
-Since our project aims to enable proofs of Separation Logic / Relational Separation Logic formulae, using an interactive prover, the user interface plays a major role in the success of the project - the easier it is to use and understand, the more chances of success it has.
+Since our project aims to enable proofs of Separation Logic / Relational Separation Logic formulae using an interactive prover, the user interface plays a major role in the success of the project - the easier it is to use and understand, the more chances of success it has.
 This idea has been presented in \cite{primer}, when discussing key elements of tools related to program verification.
@@
 
-	A sample output of the prover is presented in Figure \ref{fig:CLIScreenShot}, showcasing the manipulation of white spaces (newlines, indentation and spaces), usage of colours to distinguish between different elements - Relations are coloured in green, while the analysed code has it's keyword highlighted using cyan.
+	A sample output of the prover is presented in Figure \ref{fig:CLIScreenShot}, showcasing the manipulation of white spaces (newlines, indentation and spaces), usage of colours to distinguish between different elements - Relations are coloured in green, while the analysed code has its keywords highlighted using cyan.
 The separator between the two pieces of code is also coloured in red;
@@
 \section*{Conclusions and Future Work}
-The development of the Relational Separation Logic prover helped us get a deeper understating of it, along with an introduction to other theoretical concepts used in program analysis and programming language semantics, such as Separation Logic and Rewriting Logic.
+The development of the Relational Separation Logic prover helped me get a deeper understating of it, along with an introduction to other theoretical concepts used in program analysis and programming language semantics, such as Separation Logic and Rewriting Logic.
 \\
@@
 While the two Separation Logics used throughout the paper are powerful tools for analyzing the behavior of program and are relatively easy to understand, it takes time to become familiar and use them at their full potential.
-\\
-
-The logics are better suited for studying small snippets of code and not entire programs, because the demonstrations can get cumbersome and end up spending a lot of time on focusing on irrelevant parts of the program instead of its key sections.
+In my opinion, the logics are better suited for studying small snippets of code and not entire programs, because the demonstrations can get cumbersome and end up spending a lot of time on focusing on irrelevant parts of the program instead of its key sections.
 \\
@@
 
-While being a powerful and interesting language to work with, being fairly specialized and not very widespread, guidance and help are limited to the primer \cite{maudeprimer} and the manual \cite{manual}.
+While being a powerful and interesting language to work with, being fairly specialized and not very widespread, guidance and help are limited to the manual \cite{manual} and primer \cite{maudeprimer}.
 This obstacle resulted in significant time spent on searching for solutions to otherwise trivial problems, especially when starting using the language, because the source of the problem is usually unclear to a beginner.
@@
 The foundations of such a system are present in the current implementation, which interprets the equality between variables.
-For example, arithmetic expressions are a valid candidate for this system: in the current implementation, the expression \texttt{x plus (1 plus 2) } is different from the \texttt{x plus 3}.
+For example, arithmetic expressions are a valid candidate for this system: in the current implementation, the expression \texttt{x plus (1 plus 2)} is different from the \texttt{x plus 3}.
 	\item Improvements to the automatic proof of implications, with two of the options discussed in the Subsection \ref{autoImpl}
@@
 	This appendix contains all the necessary commands to be run in a Maude console in order to run an example demonstration using the prover.
+The proven example is detailed in the \cite{relational} paper.
 \begin{lstlisting}

### 2018-06-30 paper/paper_after_guide.tex
fixed capitalisation of chapter titles

@@
 \section{Contributions}
-Personal contributions to:
 \begin{itemize}
@@
 
-\section{Previous work}
+\section{Previous Work}
 Previous work related to the topic has been done mostly in terms of Separation Logic based tools, with Relational Separation Logic not being treated as much. \\
@@
 \begin{appendices}
-	\section{Example of proof using the prover}
+	\section{Example of Proof Using the Prover}
 	\label{proofExample}

### 2018-07-02 paper/paper_after_guide.tex
replaced black background screenshot with white bg one
printed version of the paper

@@
 \begin{center}
-\afterpage{\blankpage}
 \textbf{
@@
 
-The problem this project aims to solve is reducing the gap between theoretical and practical aspects of formal proofs for program equivalence, by creating an executable environment for Relational Separation Logic in which the user can prove the equivalence of programs.
-Through the creation of such a tool, the theoretical concepts become more accessible, easier to apply and understand.
+The problem this project aims to solve is program equivalence, by reducing the gap between theoretical and practical aspects of formal proofs for it.
+The project creates an executable environment for Relational Separation Logic in which the user can prove the equivalence of programs.
+Through the creation of this tool, the theoretical concepts become more accessible, easier to apply and understand.
 Making formal verification methods more accessible leads to an overall increase in the quality of software, by replacing the existing methods of verifying equivalence, that are often prone to errors, with more robust ones.\\
@@
 	\item {Hoare Triple} - corresponding to Separation Logic;
-	\item {Implication between relations and assertions}.
+	\item {Implication between relations and between assertions}.
 \end{itemize} 
@@
 	\begin{figure}[h]
-		\includegraphics[width=\linewidth]{pictures/CLI.png}
+		\includegraphics[width=\linewidth]{pictures/bg_white.png}
 		\caption{Formatted output of the prover}
